---
title: "PLS Model Fitting of Cognitive Abilities ~ Soc-Dem-Life-Dev for baseline and follow-up"
author: "Yue Wang, Narun Pat"
date:  "`r format(Sys.time(), '%d %b, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: united
    number_sections: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

options(scipen = 999)
```

# Set the working environment

## Reset workspace and load libraries  
This analysis uses ABCD Release 5.1.

This script is modified based on the social economics status and developmental analysis with elastic net version 2.0.

```{r , results='hide', message=FALSE, warning=FALSE}
rm(list=ls())
gc()
```

```{r , results='hide', message=FALSE, warning=FALSE}
library(tidyverse)
library(qgraph)
library(pander)
library(summarytools)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(tidymodels)
library(knitr)
library(extrafont)
## for poisson class of elastic net
library(poissonreg)
library("sva")
### plotting libraries
library(ggtext)
library(ggpubr)
library(cowplot)
library(ggthemes)
### package for pls analysis (all packages are necessary for the model to run)
library("pls")
library("mixOmics")
library(plsmod)

```


## Setting up paths

Using ABCD 4.0 

```{r, cache=FALSE, include=FALSE}

#ABCD3Fold <- '/Volumes/wd/ABCD3/'
#ABCD3Fold <-"~/OneDrive - University of Otago/ABCD3/"

#ABCD4Fold <-"/media/Data/ABCD/ABCD4/"
ABCD4Fold <-"/Volumes/Data/ABCD/ABCD4/"


#ABCD4Fold <- "//np-qnapa/Data/ABCD/ABCD4/"
#setwd(paste0(ABCD3Fold, "Analysis/CognitionP"))
dataFold <- paste0(ABCD4Fold, "ABCD4SQL/")

#ABCD3Fold <-"/media/Data/ABCD/ABCD3/"
ABCD3Fold <-"/Volumes/Data/ABCD/ABCD3/"


#utilFold <- paste0(ABCD3Fold, "Analysis/utilFunc/")

#scriptfold = "/media/Data/Yue script/"
scriptfold = "/Volumes/Data/Yue script/"


datafolder_5.1 = '/Volumes/sci-psy-narun/abcd-data-release-5.1/core/'
outputfolder_5.1 = "/Volumes/sci-psy-narun/Yue/ABCD_5.1_data_precessing/processed_data/"
dicfolder_5.1 = '/Volumes/sci-psy-narun/abcd-data-release-5.1/dictionary/'
featurefolder = "/Volumes/sci-psy-narun/Yue/ABCD_5.1_data_precessing/processed_data/"
commonfolder = "/Volumes/sci-psy-narun/Yue/Common_psy_ses_brain_gene_5.1/"
utilFold = "/Volumes/Data/ABCD/ABCD3/Analysis/utilFunc/"
imagingfolder_5.1  = paste0(datafolder_5.1, "imaging/")


source(paste0(scriptfold,"stacking_gfactor_modelling/r_functions_5.1.R"))

```

set up parallel

```{r}
# parallel for ubuntu
#doParallel::registerDoParallel(cores=30)  

### parallel library for mac
theme_set(theme_bw() + theme(panel.grid = element_blank()))
## parallel processing number of cores register
all_cores <- parallel::detectCores(logical = FALSE) - 5

doParallel::registerDoParallel(cores = all_cores)

## this one works for ubuntu but slow
#library(doFuture)
#registerDoFuture()
#plan(multicore(workers = 30))

### parallel for windows

#library(doFuture)
#registerDoFuture()
#plan(multisession(workers = 30))
```

# Load up data files

## Family relationship


1 = Male ;2 = Female  ;3 = Intersex-Male ; 4 = Intersex-Female o; 999 = Don't know ; 777 = Refuse to answer 

```{r, cache = FALSE, warning=FALSE}

acspsw03 <- read.csv("/Volumes/sci-psy-narun/abcd-data-release-5.1/core/abcd-general/abcd_y_lt.csv", na = c("", "NA", "999", "777"))
names(acspsw03) <-toupper(colnames(acspsw03))
acspsw03_select <- acspsw03 %>% filter(EVENTNAME %in% c("baseline_year_1_arm_1","2_year_follow_up_y_arm_1" ))

### write NAs of the followup family ids to be the family IDs at baseline
acspsw03_baseline <- acspsw03_select %>% filter(EVENTNAME == "baseline_year_1_arm_1" )
acspsw03_followup <- acspsw03_select %>% filter(EVENTNAME == "2_year_follow_up_y_arm_1" )

fam_basline <- acspsw03_baseline %>% dplyr::select(all_of(c("REL_FAMILY_ID","SRC_SUBJECT_ID")))

acspsw03_followup <- acspsw03_followup %>%dplyr::select(-"REL_FAMILY_ID") %>% 
                                          left_join(fam_basline, by = "SRC_SUBJECT_ID")

acspsw03_select <- bind_rows(acspsw03_baseline,acspsw03_followup)

demo <- read.csv("/Volumes/sci-psy-narun/abcd-data-release-5.1/core/abcd-general/abcd_p_demo.csv", na = c("", "NA", "999", "777"))
names(demo) <-toupper(colnames(demo))
demo_select <- demo %>% filter(EVENTNAME %in% c("baseline_year_1_arm_1","2_year_follow_up_y_arm_1" ))




ACS <- left_join(demo_select,acspsw03_select,by =c("SRC_SUBJECT_ID","EVENTNAME"))

# guardian-report relationship
# Relationship of the participant in his or her family
# 0 = single; 1 = sibling; 2 = twin; 3 = triplet
# ACS %>% count(REL_RELATIONSHIP)

ACSselected <- ACS %>% 
  dplyr::select(all_of(c("SRC_SUBJECT_ID", "EVENTNAME", "DEMO_SEX_V2", "INTERVIEW_AGE", "RACE_ETHNICITY", 
                              "REL_FAMILY_ID", "ACS_RAKED_PROPENSITY_SCORE","SITE_ID_L"))) %>%
  mutate(RACE_ETHNICITY = recode_factor(as.factor(RACE_ETHNICITY),
                `1` = "White", `2` = "Black", `3` = "Hispanic", `4` = "Asian", `5` = "Other",
                .default = "White")) %>%
  mutate(DEMO_SEX_V2 = as.factor(DEMO_SEX_V2)) %>%
  mutate(DEMO_SEX_V2 = recode_factor(as.factor(DEMO_SEX_V2),
                `1` = "Male", `2` = "Female", `3` = "Intersex-Male", `4` = "Intersex-Female",
                .default = "White")) %>%
  mutate(REL_FAMILY_ID = as.factor(REL_FAMILY_ID))

ACSselected %>%
 filter(EVENTNAME =="baseline_year_1_arm_1") %>%
 skimr::skim()


ACSselected_baseline <- ACSselected %>% filter(EVENTNAME =="baseline_year_1_arm_1") 
ACS_sex_race <- ACSselected_baseline %>% dplyr::select(SRC_SUBJECT_ID,DEMO_SEX_V2,RACE_ETHNICITY)

ACSselected_followup <- ACSselected %>% filter(EVENTNAME =="2_year_follow_up_y_arm_1") %>% 
                                        dplyr::select(- all_of(c( "DEMO_SEX_V2" ,"RACE_ETHNICITY"  )))

ACSselected_followup <- left_join(ACSselected_followup,ACS_sex_race,by = "SRC_SUBJECT_ID") 
```

vision index

```{r, cache=FALSE}

vision_idx <- tibble::as_tibble(read.csv(paste0(datafolder_5.1, "neurocognition/nc_y_svs.csv"),header = TRUE)) 
names(vision_idx) <-toupper(colnames(vision_idx))

vision_idx <- vision_idx%>% 
  mutate(visionProb = ifelse(SNELLEN_VA_Y == 0 | SNELLEN_VA_Y == 1 | VIS_FLG == 2, 1, 0))


vision_removed <- vision_idx %>% filter(SNELLEN_VA_Y == 0 | SNELLEN_VA_Y == 1 | VIS_FLG == 2)

removed_subj <- vision_removed$SRC_SUBJECT_ID

length(removed_subj)
```

## Setting up vector of names

```{r}

TaskDVs1Batch = c("NIHTBX_PICVOCAB_UNCORRECTED", 
                  "NIHTBX_READING_UNCORRECTED",
              "NIHTBX_FLANKER_UNCORRECTED",
              "NIHTBX_PATTERN_UNCORRECTED",
              "NIHTBX_PICTURE_UNCORRECTED",
               "PEA_RAVLT_LD_TRIAL_VII_TC")


subj_info <-  c("SRC_SUBJECT_ID","EVENTNAME","SITE_ID_L")   




```

Loading up pre-computed gfactor

```{r,eval=TRUE,echo=FALSE}
gfactor_list <- readRDS(paste0(scriptfold,'genetics_psychopathology_common_scan_all_scripts/gfactor_scale_seperate_5.1', '.RData'))
```


```{r}

baseline_train_gfactor <- purrr::map(gfactor_list,"output_train_baseline")
baseline_test_gfactor <- purrr::map(gfactor_list,"output_test_baseline")
followup_train_gfactor <- purrr::map(gfactor_list,"output_train_followup")
followup_test_gfactor <- purrr::map(gfactor_list,"output_test_followup")


```



## Physical

basically only sleep related are good

not very relevant: 
ABCD Sum Scores Traumatic Brain Injury	abcd_tbi01
ABCD Longitudinal Summary Scores Traumatic Brain Injury	abcd_lsstbi01
ABCD Sum Scores Parent Sports and Activities Involvement  	abcd__spacss01
ABCD Longitudinal Summary Scores Sports Activity	abcd_lsssa01
ABCD Sum Scores Parent Medical History	abcd_medhxss01
ABCD Longitudinal Summary Scores Medical History	abcd_lssmh01
ABCD Sum Scores Developmental History	abcd_devhxss01

this is mainly about puberty:
ABCD Sum Scores Physical Health Youth	abcd_ssphy01

sleep scores:
ABCD Parent Sleep Disturbance Scale for Children 	abcd_sds01
Diet only at one year follow up:
ABCD Child Nutrition Assessment	abcd_cna01
sum sleep score + diet
ABCD Sum Scores Physical Health Parent	abcd_ssphp01 

```{r, cache = FALSE, message= FALSE}
#ABCD Parent Sleep Disturbance Scale for Children
#SLEEPDISTURB1_P
#How many hours of sleep does your child get on most nights? ¬øCu√°ntas horas duerme su ni√±o(a) la mayor√≠a de las noches?
#1 = 9-11 hours/ 9 a 11 horas; 2 = 8-9 hours /8 a 9 horas; 3 = 7-8 hours /7 a 8 horas; 4 = 5-7 hours /5 a 7 horas; 5 = Less than 5 hours/ Menos de 5 horas// Consider each question pertaining to the PAST 6 MONTHS of the child's life
#SLEEPDISTURB2_P
#How long after going to bed does your child usually fall asleep? Despu√©s de acostarse ¬øgeneralmente cu√°nto tiempo tarda su ni√±o(a) en quedarse dormido(a)?
#1 = Less than 15 minutes /Menos de 15 minutos; 2 = 15-30 minutes 15 a 30 minutos; 3 = 30-45 minutes /30 a 45 minutos; 4 = 45-60 minutes /45 a 60 minutos; 5 = More than 60 minutes /M√°s de 60 minutos//Consider each question pertaining to the PAST 6 MONTHS of the child's life

sleepDis <-as_tibble(read_csv(paste0(datafolder_5.1,"physical-health/ph_p_sds.csv"))) 
names(sleepDis) <-toupper(colnames(sleepDis))

sleepDis <-sleepDis%>%
    distinct(.,.keep_all = TRUE)%>% #for some reason there is a duplicate based on these two variables
  filter(EVENTNAME %in% c("baseline_year_1_arm_1","2_year_follow_up_y_arm_1" )) 

# sleepDis %>% filter(EVENTNAME =="baseline_year_1_arm_1") %>% 
#   distinct(select(.,-ABCD_SDS01_ID, -DATASET_ID),.keep_all = TRUE) %>% 
#   arrange(SRC_SUBJECT_ID)

sleepDis %>%  filter(EVENTNAME =="baseline_year_1_arm_1") %>%
  dplyr::select(SLEEPDISTURB1_P,SLEEPDISTURB2_P) %>%
  skimr::skim()

sleepDis %>%  filter(EVENTNAME =="2_year_follow_up_y_arm_1") %>%
  dplyr::select(SLEEPDISTURB1_P,SLEEPDISTURB2_P) %>%
  skimr::skim()
# sds_p_ss_dims
# Disorders of Initiating and Maintaining Sleep (DIMS) SUM:  sleepdisturb1_p +  sleepdisturb2_p + sleepdisturb3_p + sleepdisturb4_p + sleepdisturb5_p + sleepdisturb10_p + sleepdisturb11_p;  Validation: All items must be answered
# 
# sds_p_ss_sbd
# Sleep Breathing disorders (SBD):  SUM sleepdisturb13_p +  sleepdisturb14_p + sleepdisturb15_p; Validation: All items must be answered
# 
# sds_p_ss_da
# Disorder of Arousal (DA) SUM: sleepdisturb17_p +  sleepdisturb20_p + sleepdisturb21_p;  Validation: All items must be answered
# 
# sds_p_ss_swtd
# Sleep-Wake transition Disorders (SWTD) SUM: sleepdisturb6_p + sleepdisturb7_p + sleepdisturb8_p + sleepdisturb12_p +  sleepdisturb18_p + sleepdisturb19_p; Validation: All items must be answered
# 
# sds_p_ss_does
# Disorders of Excessive Somnolence (DOES) SUM:  sleepdisturb22_p + sleepdisturb23_p +  sleepdisturb24_p +  sleepdisturb25_p + sleepdisturb26_p; Validation: All items must be answered
# 
# sds_p_ss_shy
# Sleep Hyperhydrosis (SHY) SUM: sleepdisturb9_p + sleepdisturb16_p; Validation: All items must be answered
# 
# sds_p_ss_total
# Total Score (Sum of 6 Factors): sds_p_ss_dims + sds_p_ss_sbd + sds_p_ss_da + sds_p_ss_swtd + sds_p_ss_does + sds_p_ss_shy; Validation: All items must be answered

sleepSum <- sleepDis %>%
  dplyr::select(SRC_SUBJECT_ID, EVENTNAME, SLEEPDISTURB1_P, SLEEPDISTURB2_P,
         SDS_P_SS_DIMS, SDS_P_SS_SBD, SDS_P_SS_DA, SDS_P_SS_SWTD, SDS_P_SS_DOES, SDS_P_SS_SHY, SDS_P_SS_TOTAL) %>%
  rename(sleep_hours = SLEEPDISTURB1_P) %>%
  rename(sleep_disturb = SLEEPDISTURB2_P) %>%
  rename(sleep_initiate_maintain = SDS_P_SS_DIMS) %>%
  rename(sleep_breath = SDS_P_SS_SBD) %>%
  rename(sleep_arousal = SDS_P_SS_DA) %>%
  rename(sleep_transition = SDS_P_SS_SWTD) %>%
  rename(sleep_somnolence = SDS_P_SS_DOES) %>%
  rename(sleep_hyperhydrosis = SDS_P_SS_SHY) %>%
  rename(sleep_total = SDS_P_SS_TOTAL) 

sleepSum %>% filter(EVENTNAME =="baseline_year_1_arm_1") %>%
  dplyr::select(-SRC_SUBJECT_ID,-EVENTNAME) %>%
   skimr::skim()

sleepSum %>% filter(EVENTNAME =="2_year_follow_up_y_arm_1") %>%
  dplyr::select(-SRC_SUBJECT_ID,-EVENTNAME) %>%
   skimr::skim()
```

## behavioral

### screen time

ABCD Youth Screen Time Survey	abcd_stq01

Youth Screen Time Survey
This measure includes customized questions about the overall amount of time that the youth spends using visual media, on a typical weekday and weekend day. Media activities assessed include: (1) Watching TV shows or movies; (2) Watching videos (such as YouTube); (3) Playing video games on a computer, console, phone or other device; (4) Texting on a cell phone, tablet, or computer; (5) Visiting social networking sites like Facebook, Twitter, Instagram; (6) Video chat.  Seven response options were: none, < 30 minutes, 30 minutes, 1 hour, 2 hours, 3 hours, and 4+ hours.


```{r, cache = FALSE, message= FALSE}


youthScreen_1 <-as_tibble(read_csv(paste0(datafolder_5.1,"novel-technologies/nt_p_stq.csv"))) 
names(youthScreen_1) <-toupper(colnames(youthScreen_1))

youthScreen_2 <-as_tibble(read_csv(paste0(datafolder_5.1,"novel-technologies/nt_y_st.csv"))) 
names(youthScreen_2) <-toupper(colnames(youthScreen_2))


youthScreen <- full_join(youthScreen_1,youthScreen_2, by = c("SRC_SUBJECT_ID","EVENTNAME")) %>% 
                filter(EVENTNAME %in% c("baseline_year_1_arm_1","2_year_follow_up_y_arm_1" )) 

#On a typical weekend/weekday, how many hours do you
#0 = None; .25 = < 30 minutes; 0.5 = 30 minutes; 1 = 1 hour; 2 = 2 hours; 3 = 3 hours; 4 = 4+ hours //Example: 1½ hours would be coded as 1 hour, rather than 2 hours.	
#How often do you play mature-rated video games (e.g., Call of Duty, Grand Theft Auto, Assassin's Creed, etc.)?
#How often do you watch R-rated movies?

youthScreenAdded <- youthScreen %>% 
  mutate(wkdySum_Screen = rowSums(dplyr::select(.,ends_with("WKDY_Y")))) %>% 
  mutate(wkndSum_Screen = rowSums(dplyr::select(.,ends_with("WKND_Y")))) %>%
  rename(matureGames_Screen = SCREEN13_Y) %>%
  rename(matureMovies_Screen = SCREEN14_Y) 

youthScreenSum <- youthScreenAdded %>%
  dplyr::select(SRC_SUBJECT_ID,EVENTNAME, ends_with("_Screen"))

youthScreenSum %>% filter(EVENTNAME =="baseline_year_1_arm_1") %>%
  dplyr::select(-SRC_SUBJECT_ID,-EVENTNAME) %>%
  skimr::skim()

youthScreenSum %>% filter(EVENTNAME =="2_year_follow_up_y_arm_1") %>%
  dplyr::select(-SRC_SUBJECT_ID,-EVENTNAME) %>%
  skimr::skim()
```

### maternal substance use

```{r}
#ABCD Developmental History Questionnaire
DevHis <-as_tibble(read_csv(paste0(datafolder_5.1,"physical-health/ph_p_dhx.csv"))) 
names(DevHis) <-toupper(colnames(DevHis))
DevHis <- DevHis %>%  filter(EVENTNAME %in% c("baseline_year_1_arm_1","2_year_follow_up_y_arm_1" )) 

#glimpse(DevHis)


DevHis %>% filter(EVENTNAME =="baseline_year_1_arm_1") %>%
  dplyr::select(starts_with("DEVHX_8")) %>%
  skimr::skim()

DevHis %>% filter(EVENTNAME =="2_year_follow_up_y_arm_1") %>%
  dplyr::select(starts_with("DEVHX_8")) %>%
  skimr::skim()


#devhx_8_tobacco
#Before knowing of pregnancy. Tobacco? How many times per day?/ ?Cuantas veces al d?a?

#devhx_9_tobacco
#Knowing of pregnancy. Tobacco? How many times per day?/ ?Cuantas veces al d?a?

#devhx_8_alcohol
#Before knowing of pregnancy. Alcohol? /?Alcohol?

#devhx_9_alcohol
#Knowing of pregnancy. Alcohol? /?Alcohol?

#devhx_8_marijuana
#Before knowing of pregnancy. Marijuana? /?Marihuana?

#devhx_9_marijuana
#Knowing of pregnancy. Marijuana? /?Marihuana?

# change name and replace 999 with na

momSubstanceUse <- DevHis %>% 
  mutate_if(is.numeric, ~na_if(., 999)) %>% 
  mutate(tobacco_before_preg = as.factor(DEVHX_8_TOBACCO)) %>% 
  mutate(tobacco_after_preg = as.factor(DEVHX_9_TOBACCO)) %>% 
  mutate(alcohol_before_preg = as.factor(DEVHX_8_ALCOHOL)) %>% 
  mutate(alcohol_after_preg = as.factor(DEVHX_9_ALCOHOL)) %>% 
  mutate(marijuana_before_preg = as.factor(DEVHX_8_MARIJUANA)) %>% 
  mutate(marijuana_after_preg = as.factor(DEVHX_9_MARIJUANA)) %>%
  dplyr::select(SRC_SUBJECT_ID,EVENTNAME, ends_with("_preg")) %>%
  droplevels()

momSubstanceUse %>% filter(EVENTNAME =="baseline_year_1_arm_1") %>%
  dplyr::select(-SRC_SUBJECT_ID,-EVENTNAME) %>%
  skimr::skim()

momSubstanceUse %>% filter(EVENTNAME =="2_year_follow_up_y_arm_1") %>%
  dplyr::select(-SRC_SUBJECT_ID,-EVENTNAME) %>%
  skimr::skim()
```

### developmental adversity

```{r}
DevHis %>% filter(EVENTNAME =="baseline_year_1_arm_1") %>%
  dplyr::select(starts_with(c("BIRTH_WEIGHT","DEVHX_10","DEVHX_12","DEVHX_13","DEVHX_14"))) %>%
  skimr::skim()

DevHis %>% filter(EVENTNAME =="2_year_follow_up_y_arm_1") %>%
  dplyr::select(starts_with(c("BIRTH_WEIGHT","DEVHX_10","DEVHX_12","DEVHX_13","DEVHX_14"))) %>%
  skimr::skim()
#devhx_12a_p
#Was the child born prematurely? /?Naci? el ni?o o la ni?a antes de tiempo?
adversitySum <- DevHis %>% 
  mutate_if(is.numeric, ~na_if(., 999))  %>%
  mutate(deveplopment_prematurity = as.factor(DEVHX_12A_P)) %>%
  mutate(deveplopment_birth_complications = rowSums(dplyr::select(.,starts_with("DEVHX_14")))) %>%
  #mutate(deveplopment_birth_kg = BIRTH_WEIGHT_LBS*0.453592) %>% #all na???
  mutate(deveplopment_pregnancy_complications = rowSums(dplyr::select(.,DEVHX_10A3_P:DEVHX_10L3_P))) %>%
  dplyr::select(SRC_SUBJECT_ID,EVENTNAME, starts_with("deveplopment_")) 

adversitySum %>% filter(EVENTNAME =="baseline_year_1_arm_1") %>%
  dplyr::select(-SRC_SUBJECT_ID,-EVENTNAME) %>%
  skimr::skim()

adversitySum %>% filter(EVENTNAME =="2_year_follow_up_y_arm_1") %>%
  dplyr::select(-SRC_SUBJECT_ID,-EVENTNAME) %>%
  skimr::skim()
```


### brain truma
most events are quite rare.

```{r, cache = FALSE}

brainTruma <-as_tibble(read_csv(paste0(datafolder_5.1,"physical-health/ph_p_otbi.csv"))) 
names(brainTruma) <-toupper(colnames(brainTruma))
brainTruma <- brainTruma %>%  filter(EVENTNAME %in% c("baseline_year_1_arm_1","2_year_follow_up_y_arm_1" )) 

brainTruma %>% filter(EVENTNAME =="baseline_year_1_arm_1") %>%
 skimr::skim()
brainTruma %>% filter(EVENTNAME =="2_year_follow_up_y_arm_1") %>%
 skimr::skim()
```

## culture 

### bilingual
https://www.nature.com/articles/s41562-019-0609-3
https://github.com/anthonystevendick/bilingual_abcd/blob/master/bilingual_analysis.r
accult_q1_y	
How well do you speak English?	
1 = Poor; 2 = Fair; 3 = Good; 4 = Excellent	
accult_q2_y	
Besides English, do you speak or understand another language or dialect? If child asks about languages learned in school, the RA should state: That's OK, as long as it is a language or dialect that you speak or understand.	
1 = Poor Mal; 2 = Fair Regular; 3 = Good Bien; 4 = Excellent Excelente; 777 = Refused Niego contestar; 999 = Don't Know No se	
accult_q4_y	
What language do you speak with most of your friends?	
1 = (Other language) all the time; 2 = (Other language) most of the time; 3 = (Other language) and English equally; 4 = English most of the time; 5 = English all the time	
accult_q5_y
What language do you speak with most of your family?
1 = (Other language) all the time; 2 = (Other language) most of the time; 3 = (Other language) and English equally; 4 = English most of the time; 5 = English all the time	

```{r, cache = FALSE}
bilingual <-as_tibble(read_csv(paste0(datafolder_5.1,"culture-environment/ce_y_acc.csv"))) 
names(bilingual) <-toupper(colnames(bilingual))
bilingual <- bilingual %>%  filter(EVENTNAME %in% c("baseline_year_1_arm_1","2_year_follow_up_y_arm_1" )) 

#%>% filter(EVENTNAME =="baseline_year_1_arm_1")

#bilingual_status
# #recode the accult_q2_y variable into a binary "Bilingual Status", 0 = not bilingual; 1 = bilingual
# 
# bilingual_status <- biLingual$ACCULT_Q2_Y
# sum(is.na(bilingual_status))

#bilingual_degree
# #dimension a 'bilingual degree' variable, where 1 = participant said they were bilingual, and they speak the other language with friends all the time, most of the time,
# #or equally, OR they speak the other language with family all the time, most of the time, or equally.
# 
# bilingual_degree <- ifelse(bilingual_status == 0, 0, ifelse(bilingual_status == 1 & (as.numeric(accult_q4_y) <= 3 | as.numeric(accult_q5_y) <= 3), 1, NA))
# count(bilingual_degree) #check the data
# sum(is.na(bilingual_degree))
#### here I change it such that 0 = non-bilingual, 1 = bilingual who use (Other language) < English, 2 = bilingual who use (Other language) >= English 

#bilingual_use
# 
# #dimension a continuous 'bilingual use' variable, and reverse-score so that if participants speak the other language with friends all the time, most of the time...,
# #they will receive high scores on this measure (range 0-8, with 8 indicating a high-degree of other language use)
# 
# bilingual_use<-10-(as.numeric(abcd_subset$accult_q4_y)+as.numeric(abcd_subset$accult_q5_y))
# sum(is.na(bilingual_use))
####  here I change it such that 0 = non-bilingual, 1 = bilingual who use (Other language) < English, 2 = bilingual who use (Other language) >= English  


bilingualAdded <- bilingual %>% 
  mutate(bilingual_status = factor(ifelse(ACCULT_Q2_Y==777,NA,ACCULT_Q2_Y))) %>%
  mutate(bilingual_degree = factor(ifelse(bilingual_status == 0, 0, 
                                    ifelse(bilingual_status == 1 & (as.numeric(ACCULT_Q4_Y) <= 3 | as.numeric(ACCULT_Q5_Y) <= 3), 1,
                                           ifelse(bilingual_status == 1 & (as.numeric(ACCULT_Q4_Y) > 3 | as.numeric(ACCULT_Q5_Y) > 3), 2,NA))))) %>%
      mutate(bilingual_use = ifelse(bilingual_status == 0, 0,
                                  11-(as.numeric(ACCULT_Q4_Y)+as.numeric(ACCULT_Q5_Y))))

bilingualSum <- bilingualAdded %>%
  dplyr::select(SRC_SUBJECT_ID,EVENTNAME, starts_with("bilingual_"))

bilingualSum %>%  filter(EVENTNAME =="baseline_year_1_arm_1") %>%
  dplyr::select(-SRC_SUBJECT_ID,-EVENTNAME) %>%
  skimr::skim()

bilingualSum %>%  filter(EVENTNAME =="2_year_follow_up_y_arm_1") %>%
  dplyr::select(-SRC_SUBJECT_ID,-EVENTNAME) %>%
  skimr::skim()
```

## social demographics

race/ethnicity is from ACS
family income
family type 
household size
parents' work status # demo_prnt_empl_v2 [a bit too much to include]
parents' education
sumEcon_insecurities

### ABCD Parent Demographics Survey


The following chunk of codes show that in ABCD 5.1 data tables some variables do not have measurements at the followup time points. However, some of the measurement with "_l" adding to those variables only have measurements at followup. So, in the analyses for the followup. 

The variables includes:

"marital"    
"educationAvg"                        
"combinedIncome"
"econ_insecurities_sum" 

In parents' education we replace demo_prnt_ed_v2 with demo_prnt_ed_v2_2yr_l

```{r}
demo <- read.csv("/Volumes/sci-psy-narun/abcd-data-release-5.1/core/abcd-general/abcd_p_demo.csv", na = c("", "NA", "999", "777"))
names(demo) <-toupper(colnames(demo))
demo_fam_select <- demo %>% 
  dplyr::select("SRC_SUBJECT_ID","EVENTNAME",starts_with("DEMO_FAM_"),
                starts_with("DEMO_COMB_INCOME_"),starts_with("DEMO_PRNT_ED_"),starts_with("DEMO_ROSTER_")) %>% 
  arrange(EVENTNAME) 

unique(demo_fam_select$EVENTNAME)

naniar::vis_miss(demo_fam_select,warn_large_data = FALSE)

demo_baseline <- demo_fam_select %>% 
  filter(EVENTNAME == "baseline_year_1_arm_1") %>% 
  dplyr::select("SRC_SUBJECT_ID","EVENTNAME",starts_with("DEMO_FAM_"),starts_with("DEMO_COMB_INCOME_"),starts_with("DEMO_PRNT_ED_"),starts_with("DEMO_ROSTER_"))
demo_followup <- demo_fam_select %>% 
  filter(EVENTNAME == "2_year_follow_up_y_arm_1") %>%
  dplyr::select("SRC_SUBJECT_ID","EVENTNAME",starts_with("DEMO_FAM_"),starts_with("DEMO_COMB_INCOME_"),starts_with("DEMO_PRNT_ED_"),starts_with("DEMO_ROSTER_"))

naniar::vis_miss(demo_baseline,warn_large_data = FALSE)
naniar::vis_miss(demo_followup,warn_large_data = FALSE)



```



```{r, cache = FALSE}

demograp <- read.csv("/Volumes/sci-psy-narun/abcd-data-release-5.1/core/abcd-general/abcd_p_demo.csv")
names(demograp) <-toupper(colnames(demograp))
demograp <- demograp %>% filter(EVENTNAME %in% c("baseline_year_1_arm_1","2_year_follow_up_y_arm_1" ))

demograp %>% filter(EVENTNAME =="baseline_year_1_arm_1") %>%
   skimr::skim()

demograp %>% filter(EVENTNAME =="2_year_follow_up_y_arm_1") %>%
   skimr::skim()

#demo_prnt_marital_v2 
#marital 
#Are you now married, widowed, divorced, separated, never married or living with a partner? ¬øUsted actualmente est√° casado(a), viudo(a), divorciado(a), separado(a), nunca se ha casado(a) o vive con una pareja?
#1 = Married Casado(a) ; 2 = Widowed Viudo(a) ; 3 = Divorced Divorciado(a) ; 4 = Separated Separado(a) ; 5 = Never married Nunca me he casado ; 6 = Living with partner Vivo con una pareja ; 777 = Refused to answer Prefiero no responder

#demo_prnt_ed_v2
#What is the highest grade or level of school you have completed or the highest degree you have received? ¬øCu√°l es su m√°ximo nivel de estudios completados o el m√°ximo t√≠tulo que ha recibido?
#0 = Never attended/Kindergarten only Nunca asist√É¬≠/Kinder solamente ; 1 = 1st grade 1.er grado ; 2 = 2nd grade 2.√Ç¬∫ grado ; 3 = 3rd grade 3.er grado ; 4 = 4th grade 4.√Ç¬∫ grado ; 5 = 5th grade 5.√Ç¬∫ grado ; 6 = 6th grade 6.√Ç¬∫ grado ; 7 = 7th grade 7.√Ç¬∫ grado ; 8 = 8th grade 8.√Ç¬∫ grado ; 9 = 9th grade 9.√Ç¬∫ grado ; 10 = 10th grade 10.√Ç¬∫ grado ; 11 = 11th grade 11.√Ç¬∫ grado ; 12 = 12th grade; 13 = High school graduate Preparatoria terminada ; 14 = GED or equivalent Diploma General de Equivalencia (GED) o equivalente ; 15 = Some college; 16 = Associate degree: Occupational; 17 = Associate degree: Academic Program T√É¬≠tulo de asociado: programa acad√É¬©mico ; 18 = Bachelor's degree (ex. BA; 19 = Master's degree (ex. MA; 20 = Professional School degree (ex. MD; 21 = Doctoral degree (ex. PhD; 777 = Refused to answer Prefiero no responder // The following questions are about your partner. Your "partner" refers to any significant figure in your life that helps you in raising your child or has helped you for more than 2 years. This person should be involved 40% or more of the daily activities your child does. For example, your partner could be your spouse. However, your partner could also be your boyfriend/girlfriend or relative.

#demo_comb_income_v2
#What is your TOTAL COMBINED FAMILY INCOME for the past 12 months? This should include income (before taxes and deductions) from all sources, wages, rent from properties, social security, disability and/or veteran's benefits, unemployment benefits, workman's compensation, help from relative (include child payments and alimony), and so on. ¬øCu√°l de estas categor√≠as es la que mejor describe su INGRESO FAMILIAR TOTAL COMBINADO de los √∫ltimos 12 meses? Este debe incluir los ingresos (antes de impuestos y deducciones) provenientes de todas las fuentes, salarios, renta de propiedades, seguro social, pagos por incapacidad o subsidios para veteranos, subsidios por desempleo, compensaci√≥n por accidentes de trabajo, ayuda de familiares (incluya pensiones alimenticias para hijos y c√≥nyuges divorciados), etc.
#1= Less than $5,000; 2=$5,000 through $11,999; 3=$12,000 through $15,999; 4=$16,000 through $24,999; 5=$25,000 through $34,999; 6=$35,000 through $49,999; 7=$50,000 through $74,999; 8= $75,000 through $99,999; 9=$100,000 through $199,999; 10=$200,000 and greater. 999 = Don't know No lo s√É¬© ; 777 = Refuse to answer No deseo responder  | If Separated/Divorced, please average the two household incomes. Si es Separado(a) / Divorciado(a), por favor promedie los dos ingresos familiares

#demo_roster_v2
#How many people are living at your address? INCLUDE everyone who is living or staying at your address for more than 2 months. ¬øCu√°ntas personas est√°n viviendo o qued√°ndose en su domicilio? INCLUYA a todas las personas que lleven viviendo o qued√°ndose en su domicilio durante m√°s de 2 meses.

#demo_fam_exp1_v2
#demo_fam_exp2_v2
#demo_fam_exp3_v2
#demo_fam_exp4_v2
#demo_fam_exp5_v2
#demo_fam_exp6_v2
#demo_fam_exp7_v2
# In the past 12 months, has there been a time when you and your immediate family experienced any of the following: Needed food but couldn't afford to buy it or couldn't afford to go out to get it? ¬øNecesitaban comida pero no les alcanzaba el dinero para comprarla o para salir a comprarla?
# 0 = No No; 1 = Yes S√É¬≠; 777 = Refuse to answer Niego contestar

### deal with data in baseline

demo_vec_names <-toupper(c("demo_fam_exp1_v2","demo_fam_exp2_v2","demo_fam_exp3_v2","demo_fam_exp4_v2","demo_fam_exp5_v2","demo_fam_exp6_v2","demo_fam_exp7_v2"))


demograpSum_baseline <- demograp %>% filter(EVENTNAME == "baseline_year_1_arm_1")%>% 
  dplyr::select(SRC_SUBJECT_ID,EVENTNAME,DEMO_PRNT_MARITAL_V2,DEMO_PRNT_ED_V2,DEMO_PRTNR_ED_V2,DEMO_COMB_INCOME_V2,DEMO_ROSTER_V2, starts_with("DEMO_FAM_")) %>%
  mutate(marital = recode_factor(as.factor( DEMO_PRNT_MARITAL_V2 ),
                `1` = "married", `2` = "widowed", `3` = "divorced", 
                `4` = "separated", `5` = "neverMarried", `6` = "livingWithPartner",
                `777` = NA_character_, `999` = NA_character_,
                .default = "married")) %>%
  mutate(education1stPar = ifelse( DEMO_PRNT_ED_V2 %in% c(777,999) , NA, DEMO_PRNT_ED_V2) ) %>%
  mutate(education2ndPar = ifelse( DEMO_PRTNR_ED_V2 %in% c(777,999) , NA, DEMO_PRTNR_ED_V2) ) %>%
  mutate(educationAvg = rowMeans(cbind(education1stPar,education2ndPar),na.rm=T)) %>%
  mutate(combinedIncome = ifelse( DEMO_COMB_INCOME_V2 %in% c(777,999) , NA, DEMO_COMB_INCOME_V2) ) %>%
  mutate(householdSize= ifelse( DEMO_ROSTER_V2 %in% c(777,999) | DEMO_ROSTER_V2 > 20 , NA, DEMO_ROSTER_V2) ) %>% # trim people who live with > 20 ppl (2 people in total) 
  mutate(across((starts_with("DEMO_FAM_")), ~ na_if(., 777)),
        (across((starts_with("DEMO_FAM_")), ~ na_if(., 999)))) %>%
  mutate(econ_insecurities_sum = rowSums(dplyr::select(.,all_of(demo_vec_names)),na.rm=F)) %>% 
  dplyr::select(-starts_with("DEMO_"))
  
demograpSum_baseline  %>% filter(EVENTNAME =="baseline_year_1_arm_1") %>%
  skimr::skim()

demo_vec_followup <-toupper(c("demo_fam_exp1_v2_l","demo_fam_exp2_v2_l","demo_fam_exp3_v2_l","demo_fam_exp4_v2_l","demo_fam_exp5_v2_l","demo_fam_exp6_v2_l","demo_fam_exp7_v2_l"))


demograpSum_followup <- demograp %>%  filter(EVENTNAME == "2_year_follow_up_y_arm_1")%>%
  dplyr::select(SRC_SUBJECT_ID,EVENTNAME,DEMO_PRNT_MARITAL_V2_L,DEMO_PRNT_ED_V2_L,DEMO_PRTNR_ED_V2_L,DEMO_COMB_INCOME_V2_L,DEMO_ROSTER_V2_L,DEMO_PRNT_ED_V2_2YR_L,DEMO_PRTNR_ED_V2_2YR_L, starts_with("DEMO_FAM_")) %>%
  mutate(marital = recode_factor(as.factor( DEMO_PRNT_MARITAL_V2_L ),
                `1` = "married", `2` = "widowed", `3` = "divorced", 
                `4` = "separated", `5` = "neverMarried", `6` = "livingWithPartner",
                `777` = NA_character_, `999` = NA_character_,
                .default = "married")) %>%
  mutate(education1stPar = ifelse( DEMO_PRNT_ED_V2_2YR_L %in% c(777,999) , NA, DEMO_PRNT_ED_V2_2YR_L) ) %>%
  mutate(education2ndPar = ifelse( DEMO_PRTNR_ED_V2_2YR_L %in% c(777,999) , NA, DEMO_PRTNR_ED_V2_2YR_L) ) %>%
  mutate(educationAvg = rowMeans(cbind(education1stPar,education2ndPar),na.rm=T)) %>%
  mutate(combinedIncome = ifelse( DEMO_COMB_INCOME_V2_L %in% c(777,999) , NA, DEMO_COMB_INCOME_V2_L) ) %>%
  mutate(householdSize= ifelse( DEMO_ROSTER_V2_L %in% c(777,999) | DEMO_ROSTER_V2_L > 20 , NA, DEMO_ROSTER_V2_L) ) %>% # trim people who live with > 20 ppl (2 people in total) 
  mutate(across((starts_with("DEMO_FAM_")), ~ na_if(., 777)),
        (across((starts_with("DEMO_FAM_")), ~ na_if(., 999)))) %>%
  mutate(econ_insecurities_sum = rowSums(dplyr::select(.,all_of(demo_vec_followup)),na.rm=F)) %>% 
  dplyr::select(-starts_with("DEMO_"))

  

  demograpSum_followup  %>% filter(EVENTNAME =="2_year_follow_up_y_arm_1") %>%
  skimr::skim()  
  
  demograp_sex_info <-demograp %>% dplyr::select(SRC_SUBJECT_ID,DEMO_SEX_V2) %>% drop_na()
  demograp_sex_info %>% count(DEMO_SEX_V2)
  
  demograp_sex_info %>% filter(SRC_SUBJECT_ID %in% demograpSum_followup$SRC_SUBJECT_ID) %>% count(DEMO_SEX_V2)
  
demograpSum <- bind_rows(demograpSum_baseline,demograpSum_followup)   
  
```

### more Social Demographics from Residential History Derived Scores

"RESHIST_ADDR1_ADI_WSUM"
Residential history derived - Area Deprivation Index: scaled weighted sum based on Kind et al., Annals of Internal Medicine, 2014 1
"RESHIST_ADDR1_GRNDTOT"
the grand total Uniform Crime Reports, 
"RESHIST_ADDR1_LEADRISK"
the estimated lead risk in census tract of primary residential address

```{r, cache = FALSE}

 RHDS_list <- list.files(path = paste0(datafolder_5.1,"linked-external-data/"), 
                       pattern = ".csv$", full.names = TRUE)

RHDS_file_list <- purrr::map(RHDS_list, read_csv)
RHDS <- plyr::join_all(RHDS_file_list, by = c( "src_subject_id","eventname"))
names(RHDS) <-toupper(colnames(RHDS))


# RHDS %>% filter(EVENTNAME =="baseline_year_1_arm_1") %>% select(RESHIST_ADDR1_GRNDTOT) %>%
#   #select(-1:-8) %>%
#   summarytools::dfSummary(
#                         style = 'grid', graph.magnif = 0.75,
#                         valid.col = FALSE, tmp.img.dir = "/tmp")

# Uniform Crime Reports seem to have some high values. quartic transformation will be applied.
hist(RHDS$RESHIST_ADDR1_GRNDTOT, breaks = 100)
hist((RHDS$RESHIST_ADDR1_GRNDTOT)^(1/4), breaks = 100)

ResidHistDer <- RHDS %>% 
  dplyr::select(SRC_SUBJECT_ID,EVENTNAME,
         RESHIST_ADDR1_ADI_WSUM, RESHIST_ADDR1_GRNDTOT, RESHIST_ADDR1_LEADRISK) %>%
  rename(area_deprivation_index = RESHIST_ADDR1_ADI_WSUM) %>%
  mutate(quartic_uniform_crime_reports = (RESHIST_ADDR1_GRNDTOT)^(1/4)) %>% 
  dplyr::select(-RESHIST_ADDR1_GRNDTOT) %>%
  rename(lead_risk = RESHIST_ADDR1_LEADRISK) %>%  
  filter(EVENTNAME %in% c("baseline_year_1_arm_1","2_year_follow_up_y_arm_1" )) 
  
ResidHistDer %>%  filter(EVENTNAME =="baseline_year_1_arm_1") %>%
  skimr::skim()

ResidHistDer %>%  filter(EVENTNAME =="2_year_follow_up_y_arm_1") %>%
  skimr::skim()
```
## Proximal Environment
From Zhang et al. Translational Psychiatry (2020) https://doi.org/10.1038/s41398-020-0761-6
The “Safety from Crime” items from the PhenX Toolkit was used to assess neighborhood safety and crime reports. Additionally, children reported their schoolrisk and protective factors via a 12-item Inventory for School Risk and Protective Factors of the PhenX toolkit.

### ABCD Neighborhood Safety/Crime Survey Modified from PhenX (NSC)  
from parents and children
 
```{r, cache = FALSE}

NeighboSafety_parent <-as_tibble(read_csv(paste0(datafolder_5.1,"culture-environment/ce_p_nsc.csv"))) 
names(NeighboSafety_parent) <-toupper(colnames(NeighboSafety_parent))
NeighboSafety_parent <- NeighboSafety_parent %>%  
  filter(EVENTNAME %in% c("baseline_year_1_arm_1","2_year_follow_up_y_arm_1" )) %>% 
  mutate(neighbo_safety_parent_sum = rowSums(dplyr::select(.,"NEIGHBORHOOD1R_P","NEIGHBORHOOD2R_P","NEIGHBORHOOD3R_P"),na.rm=F)) %>%
  dplyr::select(SRC_SUBJECT_ID,EVENTNAME, neighbo_safety_parent_sum)

# I feel safe walking in my neighborhood, day or night. Me siento seguro(a) caminando por mi vecindario, de d√≠a o de noche.
# Violence is not a problem in my neighborhood./ La violencia no es un problema en mi vecindario.
# My neighborhood is safe from crime. Mi vecindario est√° a salvo de la delincuencia.
#1 = Strongly Disagree /Muy en desacuerdo; 2 = Disagree /En desacuerdo; 3 = Neutral (neither agree nor disagree)/ Neutral (ni de acuerdo ni en desacuerdo); 4 = Agree /De acuerdo; 5 = Strongly Agree/ Muy de acuerdo//The following questions are about your neighborhood. Your neighborhood is the area within about a 20-minute walk (or about a mile) from your home. For each of the statements please indicate whether you strongly agree, agree, neither agree nor disagree, disagree, or strongly disagree


NeighboSafety_children <-as_tibble(read_csv(paste0(datafolder_5.1,"culture-environment/ce_y_nsc.csv"))) 
names(NeighboSafety_children) <-toupper(colnames(NeighboSafety_children))
NeighboSafety_children <- NeighboSafety_children %>%  
  filter(EVENTNAME %in% c("baseline_year_1_arm_1","2_year_follow_up_y_arm_1" )) %>% 
  rename(neighbo_safety_child_sum = NEIGHBORHOOD_CRIME_Y) %>%
  dplyr::select(SRC_SUBJECT_ID,EVENTNAME, neighbo_safety_child_sum)

#My neighborhood is safe from crime.

NeighboSafety <- plyr::join_all(list(NeighboSafety_parent, NeighboSafety_children), by=c('SRC_SUBJECT_ID','EVENTNAME'), type='full')

NeighboSafety  %>%  filter(EVENTNAME =="baseline_year_1_arm_1") %>%
  skimr::skim()

NeighboSafety  %>%  filter(EVENTNAME =="2_year_follow_up_y_arm_1") %>%
  skimr::skim()

```

### School Risk and Protective Factors Survey

```{r, cache = FALSE}

SchRisk <-as_tibble(read_csv(paste0(datafolder_5.1,"culture-environment/ce_y_srpf.csv"))) 
names(SchRisk) <-toupper(colnames(SchRisk))
SchRisk <- SchRisk %>%  
  filter(EVENTNAME %in% c("baseline_year_1_arm_1","2_year_follow_up_y_arm_1" ))

school_risk_sum <- SchRisk %>% 
  mutate(sumSchool_environment = rowSums(dplyr::select(., "SCHOOL_2_Y", "SCHOOL_3_Y", "SCHOOL_4_Y", "SCHOOL_5_Y", "SCHOOL_6_Y", "SCHOOL_7_Y"))) %>%
  mutate(sumSchool_involvement = rowSums(dplyr::select(., "SCHOOL_8_Y", "SCHOOL_9_Y", "SCHOOL_10_Y", "SCHOOL_12_Y"))) %>%
  mutate(sumSchool_disengagement = rowSums(dplyr::select(., "SCHOOL_15_Y", "SCHOOL_17_Y"))) %>%
  dplyr::select(SRC_SUBJECT_ID,EVENTNAME, starts_with("sumSchool"))

school_risk_sum %>%  filter(EVENTNAME =="baseline_year_1_arm_1") %>%
   skimr::skim()

school_risk_sum %>%  filter(EVENTNAME =="2_year_follow_up_y_arm_1") %>%
   skimr::skim()

```

## Social Interaction
From Zhang et al. Translational Psychiatry (2020) https://doi.org/10.1038/s41398-020-0761-6
The child-reported parental monitoring and acceptance, as well as the child- and parent-reported prosocial tendency and family conflicts were included to measure social interactions. Parent monitoring was accessed by a 5-item summary score of the Parental Monitoring Scale24. Parent acceptance was evaluated by the Acceptance Scale, a subscale of the Child Report of Behavior Inventory (CRPBI)25. Prosocial behavior (e.g., being nice, helping, caring) was assessed using the Prosocial Behavior Scale, a subscale from the “Strengths and Difficulties Questionnaire” (SDQ)26. Both parents and youth reported on the youth’s prosocial behavior (e.g., being considerate of other people’s feelings, often offering to help others). In order to assess the family conflicts, the ABCD protocol utilized a 9-item Family Conflict subscale of the Moos Family Environment Scale (FES) for the baseline protocol27.

### ABCD Parental Monitoring Survey

```{r, cache = FALSE}
ParMonSur <-as_tibble(read_csv(paste0(datafolder_5.1,"culture-environment/ce_y_pm.csv"))) 
names(ParMonSur) <-toupper(colnames(ParMonSur))
ParMonSur <- ParMonSur %>%  
  filter(EVENTNAME %in% c("baseline_year_1_arm_1","2_year_follow_up_y_arm_1" ))


# How often do your parents/guardians know where you are?
# How often do your parents know who you are with when you are not at school and away from home?
# If you are at home when your parents or guardians are not, how often do you know how to get in touch with them?
# How often do you talk to your mom/dad or guardian about your plans for the coming day, such as your plans about what will happen at school or what you are going to do with friends?
# In an average week, how many times do you and your parents/guardians, eat dinner together?
#1 = Never; 2 = Almost Never; 3 = Sometimes; 4 = Often; 5 = Always or Almost Always

ParentMonitoring <- ParMonSur %>% 
  mutate(parent_monitor_mean = rowMeans(dplyr::select(., starts_with("PARENT_MONITOR_")))) %>%
  dplyr::select(SRC_SUBJECT_ID,EVENTNAME, parent_monitor_mean)

ParentMonitoring %>%  filter(EVENTNAME =="baseline_year_1_arm_1") %>%
      skimr::skim()

ParentMonitoring %>%  filter(EVENTNAME =="2_year_follow_up_y_arm_1") %>%
      skimr::skim()
```

### ABCD Family Conflict
ABCD Parents Reported Parent Family Environment Scale-Family Conflict Subscale Modified from PhenX (FES), version 2 - short name: fes02
ABCD Youth Reported Parent Family Environment Scale-Family Conflict Subscale Modified from PhenX (FES), version 2 - short name: fes01

```{r, cache = FALSE}
FamilyConflict_Parents <-as_tibble(read_csv(paste0(datafolder_5.1,"culture-environment/ce_p_fes.csv"))) 
names(FamilyConflict_Parents) <-toupper(colnames(FamilyConflict_Parents))
FamilyConflict_Parents <- FamilyConflict_Parents %>%  
  filter(EVENTNAME %in% c("baseline_year_1_arm_1","2_year_follow_up_y_arm_1" )) %>% 
    distinct(.,.keep_all = TRUE) #for some reason there is a duplicate based on these two variables

# We fight a lot in our family. /Peleamos mucho en nuestra familia.
# Family members rarely become openly angry. /Los miembros de la familia raramente se enojan abiertamente.
# Family members sometimes get so angry they throw things./ Los miembros de la familia algunas veces se enojan tanto que avientan cosas.
# Family members hardly ever lose their tempers. /Los miembros de la familia dificilmente pierden su temperamento.
# Family members often criticize each other. /Los miembros de la familia con frecuencia se critican unos a otros.
# Family members sometimes hit each other./ Los miembros de la familia algunas veces se golpean unos a otros.
# If there is a disagreement in our family, we try hard to smooth things over and keep the peace. /Si hay un desacuerdo en nuestra familia, hacemos todo lo posible por resolverlo y conservar la paz.
# Family members often try to one-up or outdo each other./ Los miembros de la familia con frecuencia tratan de superar a los dem√°s.
# In our family, we believe you don't ever get anywhere by raising your voice. /En nuestra familia, creemos que no se llega a nada levantando la voz.
# 1 = True /Verdadera; 0 = False/ Falsa or 0 = True /Verdadera; 1 = False/ Falsa  

FamilyConflict_parents_sum <- FamilyConflict_Parents  %>% 
  mutate(fam_conflict_parent = rowSums(dplyr::select(., FAM_ENVIRO1_P:FAM_ENVIRO9R_P ), na.rm = F)) %>%           
  dplyr::select(SRC_SUBJECT_ID,EVENTNAME, fam_conflict_parent)

# FamilyConflict_parents_sum  %>%  filter(EVENTNAME =="baseline_year_1_arm_1") %>%
#    summarytools::dfSummary(
#                          style = 'grid', graph.magnif = 0.75, 
#                          valid.col = FALSE, tmp.img.dir = "/tmp")

FamilyConflict_Children <-as_tibble(read.csv(paste0(dataFold,"ABCD_FES01_DATA_TABLE.csv"))) 

# We fight a lot in our family.
# Family members rarely become openly angry.
# Family members sometimes get so angry they throw things.
# Family members hardly ever lose their tempers.
# Family members often criticize each other.
# Family members sometimes hit each other.
# If there's a disagreement in our family, we try hard to smooth things over and keep the peace.
# Family members often try to one-up or outdo each other.
# In our family, we believe you don't ever get anywhere by raising your voice.

FamilyConflict_children_sum <- FamilyConflict_Children   %>% 
  mutate(fam_conflict_children = rowSums(dplyr::select(., FES_YOUTH_Q1:FES_YOUTH_Q9 ), na.rm = F)) %>%           
  dplyr::select(SRC_SUBJECT_ID,EVENTNAME, fam_conflict_children)

# FamilyConflict_children_sum %>%  filter(EVENTNAME =="baseline_year_1_arm_1") %>%
#    summarytools::dfSummary(
#                          style = 'grid', graph.magnif = 0.75, 
#                          valid.col = FALSE, tmp.img.dir = "/tmp")

FamilyConflict_sum <- plyr::join_all(list(FamilyConflict_parents_sum , FamilyConflict_children_sum), 
                                by=c('SRC_SUBJECT_ID','EVENTNAME'), type='full')

FamilyConflict_sum  %>%  filter(EVENTNAME =="baseline_year_1_arm_1") %>%
    skimr::skim()

# FamilyConflict_Parents %>%  filter(EVENTNAME =="baseline_year_1_arm_1") %>% arrange(SRC_SUBJECT_ID)
# FamilyConflict_Children %>%  filter(EVENTNAME =="baseline_year_1_arm_1") %>% arrange(SRC_SUBJECT_ID)
# FamilyConflict_sum  %>%  filter(EVENTNAME =="baseline_year_1_arm_1") %>% arrange(SRC_SUBJECT_ID) 

FamilyConflict_sum  %>%  filter(EVENTNAME =="2_year_follow_up_y_arm_1") %>%
    skimr::skim()
```

### Prosocial Tendency
Parent Prosocial Behavior Survey
Youth Prosocial Behavior Survey
```{r, cache = FALSE}
#Parent Prosocial Behavior Survey

ParPS <-as_tibble(read_csv(paste0(datafolder_5.1,"culture-environment/ce_y_psb.csv"))) 
names(ParPS) <-toupper(colnames(ParPS))
ParPS <- ParPS %>%  
  filter(EVENTNAME %in% c("baseline_year_1_arm_1","2_year_follow_up_y_arm_1" )) 

#Youth Prosocial Behavior Survey
YouthPS <-as_tibble(read_csv(paste0(datafolder_5.1,"culture-environment/ce_p_psb.csv"))) 
names(YouthPS) <-toupper(colnames(YouthPS))
YouthPS <- YouthPS %>%  
  filter(EVENTNAME %in% c("baseline_year_1_arm_1","2_year_follow_up_y_arm_1" )) 

prosocial_sum <- plyr::join_all(list(ParPS , YouthPS), 
                                by=c('SRC_SUBJECT_ID','EVENTNAME'), type='full') %>%
 mutate(prosocial_parent_mean = rowMeans(dplyr::select(., "PROSOCIAL_Q1_P", "PROSOCIAL_Q2_P", "PROSOCIAL_Q3_P"))) %>%
 mutate(prosocial_youth_mean = rowMeans(dplyr::select(., "PROSOCIAL_Q1_Y", "PROSOCIAL_Q2_Y", "PROSOCIAL_Q3_Y"))) %>%
 dplyr::select(SRC_SUBJECT_ID,EVENTNAME, prosocial_parent_mean,prosocial_youth_mean)  

prosocial_sum %>%  filter(EVENTNAME =="baseline_year_1_arm_1") %>%
skimr::skim()


prosocial_sum %>%  filter(EVENTNAME =="2_year_follow_up_y_arm_1") %>%
skimr::skim()

```

## Parent Sports and Activities

### ABCD Sum Scores Parent Sports and Activities Involvement  
multiplying hours x days x 4 weeks x months x years /24 to get days
this method leads to high zeros. this might be because of the 999 -> 0??



In ABCD 5.1 data table "ph_p_saiq",  variables with the name for example: sai_ss_sboard_perwk_p only has baseline measurements and sai_ss_sboard_perwk_p_l only has followup measurements. So in the following analyses, for the baseline data we use the variable with the name sai_ss_sboard_perwk_p and the followup sai_ss_sboard_perwk_p_l.

"phys_ind_daypweek_sum"
"phys_team_daypweek_sum"   
"art_daypweek_sum" 

ABCD 5.1 does not provide measurements for the followup with the variable sai_ss_dance_nyr_p. So at the 2 years followup, we add the one year followup and 2 years followup to the baseline results to get the accumulated results. For the variables that describes the sum of days in weeks we add the baseline, one year followup and two years followup as the new data points.


```{r, cache = FALSE, warning= FALSE}

sport_act <-as_tibble(read_csv(paste0(datafolder_5.1,"physical-health/ph_p_saiq.csv"))) 
names(sport_act) <-toupper(colnames(sport_act))
sport_act <- sport_act %>%  
  filter(EVENTNAME %in% c("baseline_year_1_arm_1", "1_year_follow_up_y_arm_1" ,"2_year_follow_up_y_arm_1" )) 




sport_act_multiplied_sum_baseline <- sport_act %>% filter(EVENTNAME =="baseline_year_1_arm_1") %>%
  # change 999 to 0. don't know seems to infer that the child doesn't do that activiy
  mutate_at(vars(starts_with("SAI_SS_")), ~ replace(., which(.==999), 0)) %>%
  # 0 = 0; 1 = 1; 2 = 2; 3 = 3; 4 = 4; 5 = 5; 6 = 6; 7 = 7; 8 = Once every 2 weeks; 9 = One day every month; 10 = Less than one day per month/; 999 = Don't know | When ballet/dance was not endorsed, values for the follow-up questions are missing. Here, missing values for  the  "... how many...?" follow-up questions have been replaced with "0". 
  #change this so that 0 = nothing, .125 = Less than one day per month, .25 = One day every month, .5 =Once every 2 weeks, 1 = 1 day per week and so on
  mutate_at(.vars = vars(ends_with("_PERWK_P")),
            .funs = funs(case_when(. == 10 ~ .125,
                                   . == 9 ~ .25,
                                   . == 8 ~ .5,
                                   TRUE ~ as.numeric(.)))) %>%
  # mutate_at(.vars = vars(ends_with("_PERWK_P")),
  #           .funs = funs(case_when(. == 10 ~ 1,
  #                                  . == 9 ~ 2,
  #                                  . == 8 ~ 3,
  #                                  . == 1 ~ 4,
  #                                  . == 2 ~ 5,
  #                                  . == 3 ~ 6,
  #                                  . == 4 ~ 7,
  #                                  . == 5 ~ 8,
  #                                  . == 6 ~ 9,
  #                                  . == 7 ~ 10,
  #                                  TRUE ~ as.numeric(.)))) %>%
  #0 = 0; 1 = less than 30 minutes; 2 = 30; 3 = 45; 4 = 60 (1 hr); 5 = 90 (1.5 hrs); 6 = 120 (2 hrs); 7 = 150 (2.5 hrs); 8 = 180 (3 hrs); 9 = greater than 3 hours; 999 = Don't know | When ballet/dance was not endorsed, values for the follow-up questions are missing. Here, missing values for  the  "... how many...?" follow-up questions have been replaced with "0".  
  #change to hours unit. assumes less than 30 minutes to be .25 hour(15 mins) and > 3 hrs to be 4 hours
 mutate_at(.vars = vars(ends_with("_TSPENT_P")),
            .funs = funs(case_when(. == 1 ~ .25,
                                   . == 2 ~ .5,
                                   . == 3 ~ .75,
                                   . == 4 ~ 1,
                                   . == 5 ~ 1.5,
                                   . == 6 ~ 2,
                                   . == 7 ~ 2.5,
                                   . == 8 ~ 3,
                                   . == 9 ~ 4,
                                   TRUE ~ as.numeric(.)))) %>%
  #hours x days x 4 weeks x months x years /24 to get days
  mutate(dance_days = SAI_SS_DANCE_TSPENT_P*SAI_SS_DANCE_PERWK_P*4*SAI_SS_DANCE_NMONTH_P*SAI_SS_DANCE_NYR_P/24) %>%
  mutate(base_days = SAI_SS_BASE_TSPENT_P*SAI_SS_BASE_PERWK_P*4*SAI_SS_BASE_NMONTH_P*SAI_SS_BASE_NYR_P/24) %>%
  mutate(basket_days = SAI_SS_BASKET_TSPENT_P*SAI_SS_BASKET_PERWK_P*4*SAI_SS_BASKET_NMONTH_P*SAI_SS_BASKET_NYR_P/24) %>%
  mutate(climb_days = SAI_SS_CLIMB_TSPENT_P*SAI_SS_CLIMB_PERWK_P*4*SAI_SS_CLIMB_NMONTH_P*SAI_SS_CLIMB_NYR_P/24) %>%
  mutate(fball_days = SAI_SS_FBALL_TSPENT_P*SAI_SS_FBALL_PERWK_P*4*SAI_SS_FBALL_NMONTH_P*SAI_SS_FBALL_NYR_P/24) %>%
  mutate(fhock_days = SAI_SS_FHOCK_TSPENT_P*SAI_SS_FHOCK_PERWK_P*4*SAI_SS_FHOCK_NMONTH_P*SAI_SS_FHOCK_NYR_P/24) %>%
  mutate(gym_days = SAI_SS_GYM_TSPENT_P*SAI_SS_GYM_PERWK_P*4*SAI_SS_GYM_NMONTH_P*SAI_SS_GYM_NYR_P/24) %>%
  mutate(ihock_days = SAI_SS_IHOCK_TSPENT_P*SAI_SS_IHOCK_PERWK_P*4*SAI_SS_IHOCK_NMONTH_P*SAI_SS_IHOCK_NYR_P/24) %>%
  mutate(polo_days = SAI_SS_POLO_TSPENT_P*SAI_SS_POLO_PERWK_P*4*SAI_SS_POLO_NMONTH_P*SAI_SS_POLO_NYR_P/24) %>%
  mutate(iskate_days = SAI_SS_ISKATE_TSPENT_P*SAI_SS_ISKATE_PERWK_P*4*SAI_SS_ISKATE_NMONTH_P*SAI_SS_ISKATE_NYR_P/24) %>%
  mutate(m_arts_days = SAI_SS_M_ARTS_TSPENT_P*SAI_SS_M_ARTS_PERWK_P*4*SAI_SS_M_ARTS_NMONTH_P*SAI_SS_M_ARTS_NYR_P/24) %>%
  mutate(lax_days = SAI_SS_LAX_TSPENT_P*SAI_SS_LAX_PERWK_P*4*SAI_SS_LAX_NMONTH_P*SAI_SS_LAX_NYR_P/24) %>%
  mutate(rugby_days = SAI_SS_RUGBY_TSPENT_P*SAI_SS_RUGBY_PERWK_P*4*SAI_SS_RUGBY_NMONTH_P*SAI_SS_RUGBY_NYR_P/24) %>%
  mutate(skate_days = SAI_SS_SKATE_TSPENT_P*SAI_SS_SKATE_PERWK_P*4*SAI_SS_SKATE_NMONTH_P*SAI_SS_SKATE_NYR_P/24) %>%
  mutate(sboard_days = SAI_SS_SBOARD_TSPENT_P*SAI_SS_SBOARD_PERWK_P*4*SAI_SS_SBOARD_NMONTH_P*SAI_SS_SBOARD_NYR_P/24) %>%
  mutate(soc_days = SAI_SS_SOC_TSPENT_P*SAI_SS_SOC_PERWK_P*4*SAI_SS_SOC_NMONTH_P*SAI_SS_SOC_NYR_P/24) %>%
  mutate(surf_days = SAI_SS_SURF_TSPENT_P*SAI_SS_SURF_PERWK_P*4*SAI_SS_SURF_NMONTH_P*SAI_SS_SURF_NYR_P/24) %>%
  mutate(wpolo_days = SAI_SS_WPOLO_TSPENT_P*SAI_SS_WPOLO_PERWK_P*4*SAI_SS_WPOLO_NMONTH_P*SAI_SS_WPOLO_NYR_P/24) %>%
  mutate(tennis_days = SAI_SS_TENNIS_TSPENT_P*SAI_SS_TENNIS_PERWK_P*4*SAI_SS_TENNIS_NMONTH_P*SAI_SS_TENNIS_NYR_P/24) %>%
  mutate(run_days = SAI_SS_RUN_TSPENT_P*SAI_SS_RUN_PERWK_P*4*SAI_SS_RUN_NMONTH_P*SAI_SS_RUN_NYR_P/24) %>%
  mutate(mma_days = SAI_SS_MMA_TSPENT_P*SAI_SS_MMA_PERWK_P*4*SAI_SS_MMA_NMONTH_P*SAI_SS_MMA_NYR_P/24) %>%
  mutate(vball_days = SAI_SS_VBALL_TSPENT_P*SAI_SS_VBALL_PERWK_P*4*SAI_SS_VBALL_NMONTH_P*SAI_SS_VBALL_NYR_P/24) %>%
  mutate(yoga_days = SAI_SS_YOGA_TSPENT_P*SAI_SS_YOGA_PERWK_P*4*SAI_SS_YOGA_NMONTH_P*SAI_SS_YOGA_NYR_P/24) %>%
  mutate(music_days = SAI_SS_MUSIC_TSPENT_P*SAI_SS_MUSIC_PERWK_P*4*SAI_SS_MUSIC_NMONTH_P*SAI_SS_MUSIC_NYR_P/24) %>%
  mutate(art_days = SAI_SS_ART_TSPENT_P*SAI_SS_ART_PERWK_P*4*SAI_SS_ART_NMONTH_P*SAI_SS_ART_NYR_P/24) %>%
  mutate(drama_days = SAI_SS_DRAMA_TSPENT_P*SAI_SS_DRAMA_PERWK_P*4*SAI_SS_DRAMA_NMONTH_P*SAI_SS_DRAMA_NYR_P/24) %>%
  mutate(craft_days = SAI_SS_CRAFTS_TSPENT_P*SAI_SS_CRAFTS_PERWK_P*4*SAI_SS_CRAFTS_NMONTH_P*SAI_SS_CRAFTS_NYR_P/24) %>%
  mutate(chess_days = SAI_SS_CHESS_TSPENT_P*SAI_SS_CHESS_PERWK_P*4*SAI_SS_CHESS_NMONTH_P*SAI_SS_CHESS_NYR_P/24) %>%
  mutate(collect_days = SAI_SS_COLLECT_TSPENT_P*SAI_SS_COLLECT_PERWK_P*4*SAI_SS_COLLECT_NMONTH_P*SAI_SS_COLLECT_NYR_P/24) %>%
# didn't include listening to music or reading since they are in the different scale
# summary based on kerlic's child dev paper
  mutate(phys_ind_days_sum = sboard_days + climb_days + gym_days + iskate_days + m_arts_days + skate_days + dance_days + surf_days + tennis_days + run_days + mma_days + yoga_days) %>%
  mutate(phys_team_days_sum = base_days + basket_days + fhock_days + fball_days + ihock_days + polo_days + lax_days + rugby_days + soc_days + wpolo_days +vball_days) %>%
  mutate(art_days_sum = collect_days + music_days + art_days + drama_days + craft_days + chess_days) %>%
  mutate(sport_act_all_days_sum = phys_ind_days_sum + phys_team_days_sum + art_days_sum) %>%
  mutate(phys_ind_daypweek_sum = SAI_SS_SBOARD_PERWK_P + SAI_SS_CLIMB_PERWK_P + SAI_SS_GYM_PERWK_P + SAI_SS_ISKATE_PERWK_P + SAI_SS_M_ARTS_PERWK_P + SAI_SS_SKATE_PERWK_P + SAI_SS_DANCE_PERWK_P + SAI_SS_SURF_PERWK_P + SAI_SS_TENNIS_PERWK_P + SAI_SS_RUN_PERWK_P + SAI_SS_MMA_PERWK_P + SAI_SS_YOGA_PERWK_P) %>%
  mutate(phys_team_daypweek_sum = SAI_SS_BASE_PERWK_P + SAI_SS_BASKET_PERWK_P + SAI_SS_FHOCK_PERWK_P + SAI_SS_FBALL_PERWK_P + SAI_SS_IHOCK_PERWK_P + SAI_SS_POLO_PERWK_P + SAI_SS_LAX_PERWK_P + SAI_SS_RUGBY_PERWK_P + SAI_SS_SOC_PERWK_P + SAI_SS_WPOLO_PERWK_P +SAI_SS_VBALL_PERWK_P) %>%
  mutate(art_daypweek_sum = SAI_SS_COLLECT_PERWK_P + SAI_SS_MUSIC_PERWK_P + SAI_SS_ART_PERWK_P + SAI_SS_DRAMA_PERWK_P + SAI_SS_CRAFTS_PERWK_P + SAI_SS_CHESS_PERWK_P) %>%
  mutate(sport_act_all_daypweek_sum = phys_ind_daypweek_sum + phys_team_daypweek_sum + art_daypweek_sum)

sport_act_multiplied_sum_baseline %>%  filter(EVENTNAME =="baseline_year_1_arm_1") %>%
  skimr::skim()


baseline_days <- sport_act_multiplied_sum_baseline %>% dplyr::select("SRC_SUBJECT_ID",ends_with("days"), ends_with("_daypweek_sum"))

baseline_names_vec <- baseline_days %>% colnames()

names(baseline_days) <- paste0(baseline_names_vec,"_baseline")

baseline_days <- baseline_days %>% mutate(SRC_SUBJECT_ID=SRC_SUBJECT_ID_baseline) %>% 
                 dplyr::select(-"SRC_SUBJECT_ID_baseline" )





sport_act_multiplied_sum_one_followup <- sport_act %>% filter(EVENTNAME =="1_year_follow_up_y_arm_1") 

sport_act_multiplied_sum_one_followup <- sport_act_multiplied_sum_one_followup %>% 
                                         left_join(baseline_days, by = "SRC_SUBJECT_ID")

sport_act_multiplied_sum_one_followup <- sport_act_multiplied_sum_one_followup%>%
  # change 999 to 0. don't know seems to infer that the child doesn't do that activiy
  mutate_at(vars(starts_with("SAI_SS_")), ~ replace(., which(.==999), 0)) %>%
  # 0 = 0; 1 = 1; 2 = 2; 3 = 3; 4 = 4; 5 = 5; 6 = 6; 7 = 7; 8 = Once every 2 weeks; 9 = One day every month; 10 = Less than one day per month/; 999 = Don't know | When ballet/dance was not endorsed, values for the follow-up questions are missing. Here, missing values for  the  "... how many...?" follow-up questions have been replaced with "0". 
  #change this so that 0 = nothing, .125 = Less than one day per month, .25 = One day every month, .5 =Once every 2 weeks, 1 = 1 day per week and so on
  mutate_at(.vars = vars(ends_with("_PERWK_P_L")),
            .funs = funs(case_when(. == 10 ~ .125,
                                   . == 9 ~ .25,
                                   . == 8 ~ .5,
                                   TRUE ~ as.numeric(.)))) %>%
  # mutate_at(.vars = vars(ends_with("_PERWK_P")),
  #           .funs = funs(case_when(. == 10 ~ 1,
  #                                  . == 9 ~ 2,
  #                                  . == 8 ~ 3,
  #                                  . == 1 ~ 4,
  #                                  . == 2 ~ 5,
  #                                  . == 3 ~ 6,
  #                                  . == 4 ~ 7,
  #                                  . == 5 ~ 8,
  #                                  . == 6 ~ 9,
  #                                  . == 7 ~ 10,
  #                                  TRUE ~ as.numeric(.)))) %>%
  #0 = 0; 1 = less than 30 minutes; 2 = 30; 3 = 45; 4 = 60 (1 hr); 5 = 90 (1.5 hrs); 6 = 120 (2 hrs); 7 = 150 (2.5 hrs); 8 = 180 (3 hrs); 9 = greater than 3 hours; 999 = Don't know | When ballet/dance was not endorsed, values for the follow-up questions are missing. Here, missing values for  the  "... how many...?" follow-up questions have been replaced with "0".  
  #change to hours unit. assumes less than 30 minutes to be .25 hour(15 mins) and > 3 hrs to be 4 hours
 mutate_at(.vars = vars(ends_with("_TSPENT_P_L")),
            .funs = funs(case_when(. == 1 ~ .25,
                                   . == 2 ~ .5,
                                   . == 3 ~ .75,
                                   . == 4 ~ 1,
                                   . == 5 ~ 1.5,
                                   . == 6 ~ 2,
                                   . == 7 ~ 2.5,
                                   . == 8 ~ 3,
                                   . == 9 ~ 4,
                                   TRUE ~ as.numeric(.)))) %>%
  #hours x days x 4 weeks x months x years /24 to get days
  mutate(dance_days = SAI_SS_DANCE_TSPENT_P_L*SAI_SS_DANCE_PERWK_P_L*4*SAI_SS_DANCE_NMONTH_P_L/24+dance_days_baseline) %>%
  mutate(base_days = SAI_SS_BASE_TSPENT_P_L*SAI_SS_BASE_PERWK_P_L*4*SAI_SS_BASE_NMONTH_P_L/24+base_days_baseline) %>%
  mutate(basket_days = SAI_SS_BASKET_TSPENT_P_L*SAI_SS_BASKET_PERWK_P_L*4*SAI_SS_BASKET_NMONTH_P_L/24+basket_days_baseline) %>%
  mutate(climb_days = SAI_SS_CLIMB_TSPENT_P_L*SAI_SS_CLIMB_PERWK_P_L*4*SAI_SS_CLIMB_NMONTH_P_L/24+climb_days_baseline) %>%
  mutate(fball_days = SAI_SS_FBALL_TSPENT_P_L*SAI_SS_FBALL_PERWK_P_L*4*SAI_SS_FBALL_NMONTH_P_L/24+fball_days_baseline) %>%
  mutate(fhock_days = SAI_SS_FHOCK_TSPENT_P_L*SAI_SS_FHOCK_PERWK_P_L*4*SAI_SS_FHOCK_NMONTH_P_L/24+fhock_days_baseline) %>%
  mutate(gym_days = SAI_SS_GYM_TSPENT_P_L*SAI_SS_GYM_PERWK_P_L*4*SAI_SS_GYM_NMONTH_P_L/24+gym_days_baseline) %>%
  mutate(ihock_days = SAI_SS_IHOCK_TSPENT_P_L*SAI_SS_IHOCK_PERWK_P_L*4*SAI_SS_IHOCK_NMONTH_P_L/24+ihock_days_baseline) %>%
  mutate(polo_days = SAI_SS_POLO_TSPENT_P_L*SAI_SS_POLO_PERWK_P_L*4*SAI_SS_POLO_NMONTH_P_L/24+polo_days_baseline) %>%
  mutate(iskate_days = SAI_SS_ISKATE_TSPENT_P_L*SAI_SS_ISKATE_PERWK_P_L*4*SAI_SS_ISKATE_NMONTH_P_L/24+iskate_days_baseline) %>%
  mutate(m_arts_days = SAI_SS_M_ARTS_TSPENT_P_L*SAI_SS_M_ARTS_PERWK_P_L*4*SAI_SS_M_ARTS_NMONTH_P_L/24+m_arts_days_baseline) %>%
  mutate(lax_days = SAI_SS_LAX_TSPENT_P_L*SAI_SS_LAX_PERWK_P_L*4*SAI_SS_LAX_NMONTH_P_L/24+lax_days_baseline) %>%
  mutate(rugby_days = SAI_SS_RUGBY_TSPENT_P_L*SAI_SS_RUGBY_PERWK_P_L*4*SAI_SS_RUGBY_NMONTH_P_L/24+rugby_days_baseline) %>%
  mutate(skate_days = SAI_SS_SKATE_TSPENT_P_L*SAI_SS_SKATE_PERWK_P_L*4*SAI_SS_SKATE_NMONTH_P_L/24+skate_days_baseline) %>%
  mutate(sboard_days = SAI_SS_SBOARD_TSPENT_P_L*SAI_SS_SBOARD_PERWK_P_L*4*SAI_SS_SBOARD_NMONTH_P_L/24+sboard_days_baseline) %>%
  mutate(soc_days = SAI_SS_SOC_TSPENT_P_L*SAI_SS_SOC_PERWK_P_L*4*SAI_SS_SOC_NMONTH_P_L/24+soc_days_baseline) %>%
  mutate(surf_days = SAI_SS_SURF_TSPENT_P_L*SAI_SS_SURF_PERWK_P_L*4*SAI_SS_SURF_NMONTH_P_L/24+surf_days_baseline) %>%
  mutate(wpolo_days = SAI_SS_WPOLO_TSPENT_P_L*SAI_SS_WPOLO_PERWK_P_L*4*SAI_SS_WPOLO_NMONTH_P_L/24+wpolo_days_baseline) %>%
  mutate(tennis_days = SAI_SS_TENNIS_TSPENT_P_L*SAI_SS_TENNIS_PERWK_P_L*4*SAI_SS_TENNIS_NMONTH_P_L/24+tennis_days_baseline) %>%
  mutate(run_days = SAI_SS_RUN_TSPENT_P_L*SAI_SS_RUN_PERWK_P_L*4*SAI_SS_RUN_NMONTH_P_L/24+run_days_baseline) %>%
  mutate(mma_days = SAI_SS_MMA_TSPENT_P_L*SAI_SS_MMA_PERWK_P_L*4*SAI_SS_MMA_NMONTH_P_L/24+mma_days_baseline) %>%
  mutate(vball_days = SAI_SS_VBALL_TSPENT_P_L*SAI_SS_VBALL_PERWK_P_L*4*SAI_SS_VBALL_NMONTH_P_L/24+vball_days_baseline) %>%
  mutate(yoga_days = SAI_SS_YOGA_TSPENT_P_L*SAI_SS_YOGA_PERWK_P_L*4*SAI_SS_YOGA_NMONTH_P_L/24+yoga_days_baseline) %>%
  mutate(music_days = SAI_SS_MUSIC_TSPENT_P_L*SAI_SS_MUSIC_PERWK_P_L*4*SAI_SS_MUSIC_NMONTH_P_L/24+music_days_baseline) %>%
  mutate(art_days = SAI_SS_ART_TSPENT_P_L*SAI_SS_ART_PERWK_P_L*4*SAI_SS_ART_NMONTH_P_L/24+art_days_baseline) %>%
  mutate(drama_days = SAI_SS_DRAMA_TSPENT_P_L*SAI_SS_DRAMA_PERWK_P_L*4*SAI_SS_DRAMA_NMONTH_P_L/24+drama_days_baseline) %>%
  mutate(craft_days = SAI_SS_CRAFTS_TSPENT_P_L*SAI_SS_CRAFTS_PERWK_P_L*4*SAI_SS_CRAFTS_NMONTH_P_L/24+craft_days_baseline) %>%
  mutate(chess_days = SAI_SS_CHESS_TSPENT_P_L*SAI_SS_CHESS_PERWK_P_L*4*SAI_SS_CHESS_NMONTH_P_L/24+chess_days_baseline) %>%
  mutate(collect_days = SAI_SS_COLLECT_TSPENT_P_L*SAI_SS_COLLECT_PERWK_P_L*4*SAI_SS_COLLECT_NMONTH_P_L/24+collect_days_baseline) %>%
# didn't include listening to music or reading since they are in the different scale
# summary based on kerlic's child dev paper
  mutate(phys_ind_days_sum = sboard_days + climb_days + gym_days + iskate_days + m_arts_days + skate_days + dance_days + surf_days + tennis_days + run_days + mma_days + yoga_days) %>%
  mutate(phys_team_days_sum = base_days + basket_days + fhock_days + fball_days + ihock_days + polo_days + lax_days + rugby_days + soc_days + wpolo_days +vball_days) %>%
  mutate(art_days_sum = collect_days + music_days + art_days + drama_days + craft_days + chess_days) %>%
  mutate(sport_act_all_days_sum = phys_ind_days_sum + phys_team_days_sum + art_days_sum) %>%
  mutate(phys_ind_daypweek_sum = SAI_SS_SBOARD_PERWK_P_L + SAI_SS_CLIMB_PERWK_P_L + SAI_SS_GYM_PERWK_P_L + SAI_SS_ISKATE_PERWK_P_L + SAI_SS_M_ARTS_PERWK_P_L + SAI_SS_SKATE_PERWK_P_L + SAI_SS_DANCE_PERWK_P_L + SAI_SS_SURF_PERWK_P_L + SAI_SS_TENNIS_PERWK_P_L + SAI_SS_RUN_PERWK_P_L + SAI_SS_MMA_PERWK_P_L + SAI_SS_YOGA_PERWK_P_L+phys_ind_daypweek_sum_baseline) %>%
  mutate(phys_team_daypweek_sum = SAI_SS_BASE_PERWK_P_L + SAI_SS_BASKET_PERWK_P_L + SAI_SS_FHOCK_PERWK_P_L + SAI_SS_FBALL_PERWK_P_L + SAI_SS_IHOCK_PERWK_P_L + SAI_SS_POLO_PERWK_P_L + SAI_SS_LAX_PERWK_P_L + SAI_SS_RUGBY_PERWK_P_L + SAI_SS_SOC_PERWK_P_L + SAI_SS_WPOLO_PERWK_P_L +SAI_SS_VBALL_PERWK_P_L+phys_team_daypweek_sum_baseline) %>%
  mutate(art_daypweek_sum = SAI_SS_COLLECT_PERWK_P_L + SAI_SS_MUSIC_PERWK_P_L + SAI_SS_ART_PERWK_P_L + SAI_SS_DRAMA_PERWK_P_L + SAI_SS_CRAFTS_PERWK_P_L + SAI_SS_CHESS_PERWK_P_L+art_daypweek_sum_baseline) %>%
  mutate(sport_act_all_daypweek_sum = phys_ind_daypweek_sum + phys_team_daypweek_sum + art_daypweek_sum) %>% 
 dplyr::select(-ends_with("_baseline"))



one_followup_days <- sport_act_multiplied_sum_one_followup %>% dplyr::select("SRC_SUBJECT_ID",ends_with("days"), ends_with("_daypweek_sum"))

one_followup_names_vec <- one_followup_days %>% colnames()

names(one_followup_days) <- paste0(one_followup_names_vec,"_one_followup")

one_followup_days <- one_followup_days %>% mutate(SRC_SUBJECT_ID=SRC_SUBJECT_ID_one_followup) %>% 
                 dplyr::select(-"SRC_SUBJECT_ID_one_followup" )





sport_act_multiplied_sum_two_followup <- sport_act %>% filter(EVENTNAME =="2_year_follow_up_y_arm_1") 

sport_act_multiplied_sum_two_followup <- sport_act_multiplied_sum_two_followup %>% 
                                         left_join(one_followup_days, by = "SRC_SUBJECT_ID")

sport_act_multiplied_sum_two_followup <- sport_act_multiplied_sum_two_followup%>%
  # change 999 to 0. don't know seems to infer that the child doesn't do that activiy
  mutate_at(vars(starts_with("SAI_SS_")), ~ replace(., which(.==999), 0)) %>%
  # 0 = 0; 1 = 1; 2 = 2; 3 = 3; 4 = 4; 5 = 5; 6 = 6; 7 = 7; 8 = Once every 2 weeks; 9 = One day every month; 10 = Less than one day per month/; 999 = Don't know | When ballet/dance was not endorsed, values for the follow-up questions are missing. Here, missing values for  the  "... how many...?" follow-up questions have been replaced with "0". 
  #change this so that 0 = nothing, .125 = Less than one day per month, .25 = One day every month, .5 =Once every 2 weeks, 1 = 1 day per week and so on
  mutate_at(.vars = vars(ends_with("_PERWK_P_L")),
            .funs = funs(case_when(. == 10 ~ .125,
                                   . == 9 ~ .25,
                                   . == 8 ~ .5,
                                   TRUE ~ as.numeric(.)))) %>%
  # mutate_at(.vars = vars(ends_with("_PERWK_P")),
  #           .funs = funs(case_when(. == 10 ~ 1,
  #                                  . == 9 ~ 2,
  #                                  . == 8 ~ 3,
  #                                  . == 1 ~ 4,
  #                                  . == 2 ~ 5,
  #                                  . == 3 ~ 6,
  #                                  . == 4 ~ 7,
  #                                  . == 5 ~ 8,
  #                                  . == 6 ~ 9,
  #                                  . == 7 ~ 10,
  #                                  TRUE ~ as.numeric(.)))) %>%
  #0 = 0; 1 = less than 30 minutes; 2 = 30; 3 = 45; 4 = 60 (1 hr); 5 = 90 (1.5 hrs); 6 = 120 (2 hrs); 7 = 150 (2.5 hrs); 8 = 180 (3 hrs); 9 = greater than 3 hours; 999 = Don't know | When ballet/dance was not endorsed, values for the follow-up questions are missing. Here, missing values for  the  "... how many...?" follow-up questions have been replaced with "0".  
  #change to hours unit. assumes less than 30 minutes to be .25 hour(15 mins) and > 3 hrs to be 4 hours
 mutate_at(.vars = vars(ends_with("_TSPENT_P_L")),
            .funs = funs(case_when(. == 1 ~ .25,
                                   . == 2 ~ .5,
                                   . == 3 ~ .75,
                                   . == 4 ~ 1,
                                   . == 5 ~ 1.5,
                                   . == 6 ~ 2,
                                   . == 7 ~ 2.5,
                                   . == 8 ~ 3,
                                   . == 9 ~ 4,
                                   TRUE ~ as.numeric(.)))) %>%
  #hours x days x 4 weeks x months x years /24 to get days
  mutate(dance_days = SAI_SS_DANCE_TSPENT_P_L*SAI_SS_DANCE_PERWK_P_L*4*SAI_SS_DANCE_NMONTH_P_L/24+dance_days_one_followup) %>%
  mutate(base_days = SAI_SS_BASE_TSPENT_P_L*SAI_SS_BASE_PERWK_P_L*4*SAI_SS_BASE_NMONTH_P_L/24+base_days_one_followup) %>%
  mutate(basket_days = SAI_SS_BASKET_TSPENT_P_L*SAI_SS_BASKET_PERWK_P_L*4*SAI_SS_BASKET_NMONTH_P_L/24+basket_days_one_followup) %>%
  mutate(climb_days = SAI_SS_CLIMB_TSPENT_P_L*SAI_SS_CLIMB_PERWK_P_L*4*SAI_SS_CLIMB_NMONTH_P_L/24+climb_days_one_followup) %>%
  mutate(fball_days = SAI_SS_FBALL_TSPENT_P_L*SAI_SS_FBALL_PERWK_P_L*4*SAI_SS_FBALL_NMONTH_P_L/24+fball_days_one_followup) %>%
  mutate(fhock_days = SAI_SS_FHOCK_TSPENT_P_L*SAI_SS_FHOCK_PERWK_P_L*4*SAI_SS_FHOCK_NMONTH_P_L/24+fhock_days_one_followup) %>%
  mutate(gym_days = SAI_SS_GYM_TSPENT_P_L*SAI_SS_GYM_PERWK_P_L*4*SAI_SS_GYM_NMONTH_P_L/24+gym_days_one_followup) %>%
  mutate(ihock_days = SAI_SS_IHOCK_TSPENT_P_L*SAI_SS_IHOCK_PERWK_P_L*4*SAI_SS_IHOCK_NMONTH_P_L/24+ihock_days_one_followup) %>%
  mutate(polo_days = SAI_SS_POLO_TSPENT_P_L*SAI_SS_POLO_PERWK_P_L*4*SAI_SS_POLO_NMONTH_P_L/24+polo_days_one_followup) %>%
  mutate(iskate_days = SAI_SS_ISKATE_TSPENT_P_L*SAI_SS_ISKATE_PERWK_P_L*4*SAI_SS_ISKATE_NMONTH_P_L/24+iskate_days_one_followup) %>%
  mutate(m_arts_days = SAI_SS_M_ARTS_TSPENT_P_L*SAI_SS_M_ARTS_PERWK_P_L*4*SAI_SS_M_ARTS_NMONTH_P_L/24+m_arts_days_one_followup) %>%
  mutate(lax_days = SAI_SS_LAX_TSPENT_P_L*SAI_SS_LAX_PERWK_P_L*4*SAI_SS_LAX_NMONTH_P_L/24+lax_days_one_followup) %>%
  mutate(rugby_days = SAI_SS_RUGBY_TSPENT_P_L*SAI_SS_RUGBY_PERWK_P_L*4*SAI_SS_RUGBY_NMONTH_P_L/24+rugby_days_one_followup) %>%
  mutate(skate_days = SAI_SS_SKATE_TSPENT_P_L*SAI_SS_SKATE_PERWK_P_L*4*SAI_SS_SKATE_NMONTH_P_L/24+skate_days_one_followup) %>%
  mutate(sboard_days = SAI_SS_SBOARD_TSPENT_P_L*SAI_SS_SBOARD_PERWK_P_L*4*SAI_SS_SBOARD_NMONTH_P_L/24+sboard_days_one_followup) %>%
  mutate(soc_days = SAI_SS_SOC_TSPENT_P_L*SAI_SS_SOC_PERWK_P_L*4*SAI_SS_SOC_NMONTH_P_L/24+soc_days_one_followup) %>%
  mutate(surf_days = SAI_SS_SURF_TSPENT_P_L*SAI_SS_SURF_PERWK_P_L*4*SAI_SS_SURF_NMONTH_P_L/24+surf_days_one_followup) %>%
  mutate(wpolo_days = SAI_SS_WPOLO_TSPENT_P_L*SAI_SS_WPOLO_PERWK_P_L*4*SAI_SS_WPOLO_NMONTH_P_L/24+wpolo_days_one_followup) %>%
  mutate(tennis_days = SAI_SS_TENNIS_TSPENT_P_L*SAI_SS_TENNIS_PERWK_P_L*4*SAI_SS_TENNIS_NMONTH_P_L/24+tennis_days_one_followup) %>%
  mutate(run_days = SAI_SS_RUN_TSPENT_P_L*SAI_SS_RUN_PERWK_P_L*4*SAI_SS_RUN_NMONTH_P_L/24+run_days_one_followup) %>%
  mutate(mma_days = SAI_SS_MMA_TSPENT_P_L*SAI_SS_MMA_PERWK_P_L*4*SAI_SS_MMA_NMONTH_P_L/24+mma_days_one_followup) %>%
  mutate(vball_days = SAI_SS_VBALL_TSPENT_P_L*SAI_SS_VBALL_PERWK_P_L*4*SAI_SS_VBALL_NMONTH_P_L/24+vball_days_one_followup) %>%
  mutate(yoga_days = SAI_SS_YOGA_TSPENT_P_L*SAI_SS_YOGA_PERWK_P_L*4*SAI_SS_YOGA_NMONTH_P_L/24+yoga_days_one_followup) %>%
  mutate(music_days = SAI_SS_MUSIC_TSPENT_P_L*SAI_SS_MUSIC_PERWK_P_L*4*SAI_SS_MUSIC_NMONTH_P_L/24+music_days_one_followup) %>%
  mutate(art_days = SAI_SS_ART_TSPENT_P_L*SAI_SS_ART_PERWK_P_L*4*SAI_SS_ART_NMONTH_P_L/24+art_days_one_followup) %>%
  mutate(drama_days = SAI_SS_DRAMA_TSPENT_P_L*SAI_SS_DRAMA_PERWK_P_L*4*SAI_SS_DRAMA_NMONTH_P_L/24+drama_days_one_followup) %>%
  mutate(craft_days = SAI_SS_CRAFTS_TSPENT_P_L*SAI_SS_CRAFTS_PERWK_P_L*4*SAI_SS_CRAFTS_NMONTH_P_L/24+craft_days_one_followup) %>%
  mutate(chess_days = SAI_SS_CHESS_TSPENT_P_L*SAI_SS_CHESS_PERWK_P_L*4*SAI_SS_CHESS_NMONTH_P_L/24+chess_days_one_followup) %>%
  mutate(collect_days = SAI_SS_COLLECT_TSPENT_P_L*SAI_SS_COLLECT_PERWK_P_L*4*SAI_SS_COLLECT_NMONTH_P_L/24+collect_days_one_followup) %>%
# didn't include listening to music or reading since they are in the different scale
# summary based on kerlic's child dev paper
  mutate(phys_ind_days_sum = sboard_days + climb_days + gym_days + iskate_days + m_arts_days + skate_days + dance_days + surf_days + tennis_days + run_days + mma_days + yoga_days) %>%
  mutate(phys_team_days_sum = base_days + basket_days + fhock_days + fball_days + ihock_days + polo_days + lax_days + rugby_days + soc_days + wpolo_days +vball_days) %>%
  mutate(art_days_sum = collect_days + music_days + art_days + drama_days + craft_days + chess_days) %>%
  mutate(sport_act_all_days_sum = phys_ind_days_sum + phys_team_days_sum + art_days_sum) %>%
  mutate(phys_ind_daypweek_sum = SAI_SS_SBOARD_PERWK_P_L + SAI_SS_CLIMB_PERWK_P_L + SAI_SS_GYM_PERWK_P_L + SAI_SS_ISKATE_PERWK_P_L + SAI_SS_M_ARTS_PERWK_P_L + SAI_SS_SKATE_PERWK_P_L + SAI_SS_DANCE_PERWK_P_L + SAI_SS_SURF_PERWK_P_L + SAI_SS_TENNIS_PERWK_P_L + SAI_SS_RUN_PERWK_P_L + SAI_SS_MMA_PERWK_P_L + SAI_SS_YOGA_PERWK_P_L+phys_ind_daypweek_sum_one_followup) %>%
  mutate(phys_team_daypweek_sum = SAI_SS_BASE_PERWK_P_L + SAI_SS_BASKET_PERWK_P_L + SAI_SS_FHOCK_PERWK_P_L + SAI_SS_FBALL_PERWK_P_L + SAI_SS_IHOCK_PERWK_P_L + SAI_SS_POLO_PERWK_P_L + SAI_SS_LAX_PERWK_P_L + SAI_SS_RUGBY_PERWK_P_L + SAI_SS_SOC_PERWK_P_L + SAI_SS_WPOLO_PERWK_P_L +SAI_SS_VBALL_PERWK_P_L+phys_team_daypweek_sum_one_followup) %>%
  mutate(art_daypweek_sum = SAI_SS_COLLECT_PERWK_P_L + SAI_SS_MUSIC_PERWK_P_L + SAI_SS_ART_PERWK_P_L + SAI_SS_DRAMA_PERWK_P_L + SAI_SS_CRAFTS_PERWK_P_L + SAI_SS_CHESS_PERWK_P_L+art_daypweek_sum_one_followup) %>%
  mutate(sport_act_all_daypweek_sum = phys_ind_daypweek_sum + phys_team_daypweek_sum + art_daypweek_sum) %>% 
 dplyr::select(-ends_with("_one_followup"))



sport_act_multiplied_sum_two_followup %>%  filter(EVENTNAME =="2_year_follow_up_y_arm_1") %>%
  skimr::skim()


sport_act_multiplied_sum <- bind_rows(sport_act_multiplied_sum_baseline,sport_act_multiplied_sum_two_followup)
```

### ABCD Sum Scores Parent Sports and Activities Involvement  
method used by Kerlic et al. They focus only on days per week. The data were converted differently.

```{r, cache = FALSE}

sport_act_kerlic_sum_baseline <- sport_act %>% filter(EVENTNAME =="baseline_year_1_arm_1") %>%
  # change 999 to 0. don't know seems to infer that the child doesn't do that activiy
  mutate_at(vars(starts_with("SAI_SS_")), ~ replace(., which(.==999), 0)) %>% 
  # 0 = 0; 1 = 1; 2 = 2; 3 = 3; 4 = 4; 5 = 5; 6 = 6; 7 = 7; 8 = Once every 2 weeks; 9 = One day every month; 10 = Less than one day per month/; 999 = Don't know | When ballet/dance was not endorsed, values for the follow-up questions are missing. Here, missing values for  the  "... how many...?" follow-up questions have been replaced with "0". 
  #change this so that 0 = nothing, .125 = Less than one day per month, .25 = One day every month, .5 =Once every 2 weeks, 1 = 1 day per week and so on
  mutate_at(.vars = vars(ends_with("_PERWK_P")),
            .funs = funs(case_when(. == 10 ~ 1,
                                   . == 9 ~ 2,
                                   . == 8 ~ 3,
                                   . == 1 ~ 4,
                                   . == 2 ~ 5,
                                   . == 3 ~ 6,
                                   . == 4 ~ 7,
                                   . == 5 ~ 8,
                                   . == 6 ~ 9,
                                   . == 7 ~ 10,
                                   TRUE ~ as.numeric(.)))) %>%
  mutate(phys_ind_daypweek_sum = SAI_SS_SBOARD_PERWK_P + SAI_SS_CLIMB_PERWK_P + SAI_SS_GYM_PERWK_P + SAI_SS_ISKATE_PERWK_P + SAI_SS_M_ARTS_PERWK_P + SAI_SS_SKATE_PERWK_P + SAI_SS_DANCE_PERWK_P + SAI_SS_SURF_PERWK_P + SAI_SS_TENNIS_PERWK_P + SAI_SS_RUN_PERWK_P + SAI_SS_MMA_PERWK_P + SAI_SS_YOGA_PERWK_P) %>%
  mutate(phys_team_daypweek_sum = SAI_SS_BASE_PERWK_P + SAI_SS_BASKET_PERWK_P + SAI_SS_FHOCK_PERWK_P + SAI_SS_FBALL_PERWK_P + SAI_SS_IHOCK_PERWK_P + SAI_SS_POLO_PERWK_P + SAI_SS_LAX_PERWK_P + SAI_SS_RUGBY_PERWK_P + SAI_SS_SOC_PERWK_P + SAI_SS_WPOLO_PERWK_P +SAI_SS_VBALL_PERWK_P) %>%
  mutate(art_daypweek_sum = SAI_SS_COLLECT_PERWK_P + SAI_SS_MUSIC_PERWK_P + SAI_SS_ART_PERWK_P + SAI_SS_DRAMA_PERWK_P + SAI_SS_CRAFTS_PERWK_P + SAI_SS_CHESS_PERWK_P) %>%
  mutate(sport_act_all_daypweek_sum = phys_ind_daypweek_sum + phys_team_daypweek_sum + art_daypweek_sum) %>%
  dplyr::select(	SRC_SUBJECT_ID, EVENTNAME, ends_with("_daypweek_sum"))


sport_act_kerlic_sum_baseline %>%  filter(EVENTNAME =="baseline_year_1_arm_1") %>%
   dplyr::select(-SRC_SUBJECT_ID, -EVENTNAME, ends_with('_daypweek_sum')) %>%
     skimr::skim()


baseline_sum_days <- sport_act_kerlic_sum_baseline %>% dplyr::select("SRC_SUBJECT_ID", ends_with("_daypweek_sum"))

baseline_sum_names_vec <- baseline_sum_days %>% colnames()

names(baseline_sum_days) <- paste0(baseline_sum_names_vec,"_baseline")

baseline_sum_days <- baseline_sum_days %>% mutate(SRC_SUBJECT_ID=SRC_SUBJECT_ID_baseline) %>% 
                 dplyr::select(-"SRC_SUBJECT_ID_baseline" )


sport_act_kerlic_sum_one_followup <- sport_act %>% filter(EVENTNAME =="1_year_follow_up_y_arm_1") 

sport_act_kerlic_sum_one_followup <- sport_act_kerlic_sum_one_followup %>% 
                                         left_join(baseline_sum_days, by = "SRC_SUBJECT_ID")

sport_act_kerlic_sum_one_followup <- sport_act_kerlic_sum_one_followup %>%
  # change 999 to 0. don't know seems to infer that the child doesn't do that activiy
  mutate_at(vars(starts_with("SAI_SS_")), ~ replace(., which(.==999), 0)) %>% 
  # 0 = 0; 1 = 1; 2 = 2; 3 = 3; 4 = 4; 5 = 5; 6 = 6; 7 = 7; 8 = Once every 2 weeks; 9 = One day every month; 10 = Less than one day per month/; 999 = Don't know | When ballet/dance was not endorsed, values for the follow-up questions are missing. Here, missing values for  the  "... how many...?" follow-up questions have been replaced with "0". 
  #change this so that 0 = nothing, .125 = Less than one day per month, .25 = One day every month, .5 =Once every 2 weeks, 1 = 1 day per week and so on
  mutate_at(.vars = vars(ends_with("_PERWK_P_L")),
            .funs = funs(case_when(. == 10 ~ 1,
                                   . == 9 ~ 2,
                                   . == 8 ~ 3,
                                   . == 1 ~ 4,
                                   . == 2 ~ 5,
                                   . == 3 ~ 6,
                                   . == 4 ~ 7,
                                   . == 5 ~ 8,
                                   . == 6 ~ 9,
                                   . == 7 ~ 10,
                                   TRUE ~ as.numeric(.)))) %>%
  mutate(phys_ind_daypweek_sum = SAI_SS_SBOARD_PERWK_P_L + SAI_SS_CLIMB_PERWK_P_L + SAI_SS_GYM_PERWK_P_L + SAI_SS_ISKATE_PERWK_P_L + SAI_SS_M_ARTS_PERWK_P_L + SAI_SS_SKATE_PERWK_P_L + SAI_SS_DANCE_PERWK_P_L + SAI_SS_SURF_PERWK_P_L + SAI_SS_TENNIS_PERWK_P_L + SAI_SS_RUN_PERWK_P_L + SAI_SS_MMA_PERWK_P_L + SAI_SS_YOGA_PERWK_P_L+phys_ind_daypweek_sum_baseline) %>%
  mutate(phys_team_daypweek_sum = SAI_SS_BASE_PERWK_P_L + SAI_SS_BASKET_PERWK_P_L + SAI_SS_FHOCK_PERWK_P_L + SAI_SS_FBALL_PERWK_P_L + SAI_SS_IHOCK_PERWK_P_L + SAI_SS_POLO_PERWK_P_L + SAI_SS_LAX_PERWK_P_L + SAI_SS_RUGBY_PERWK_P_L + SAI_SS_SOC_PERWK_P_L + SAI_SS_WPOLO_PERWK_P_L +SAI_SS_VBALL_PERWK_P_L+phys_team_daypweek_sum_baseline) %>%
  mutate(art_daypweek_sum = SAI_SS_COLLECT_PERWK_P_L + SAI_SS_MUSIC_PERWK_P_L + SAI_SS_ART_PERWK_P_L + SAI_SS_DRAMA_PERWK_P_L + SAI_SS_CRAFTS_PERWK_P_L + SAI_SS_CHESS_PERWK_P_L+art_daypweek_sum_baseline) %>%
  mutate(sport_act_all_daypweek_sum = phys_ind_daypweek_sum + phys_team_daypweek_sum + art_daypweek_sum) %>%
  dplyr::select(	SRC_SUBJECT_ID, EVENTNAME, ends_with("_daypweek_sum"))


one_followup_sum_days <- sport_act_kerlic_sum_one_followup %>% dplyr::select("SRC_SUBJECT_ID", ends_with("_daypweek_sum"))

one_followup_sum_names_vec <- one_followup_sum_days %>% colnames()

names(one_followup_sum_days) <- paste0(one_followup_sum_names_vec,"_one_followup")

one_followup_sum_days <- one_followup_sum_days %>% mutate(SRC_SUBJECT_ID=SRC_SUBJECT_ID_one_followup) %>% 
                 dplyr::select(-"SRC_SUBJECT_ID_one_followup" )


sport_act_kerlic_sum_two_followup <- sport_act %>% filter(EVENTNAME =="2_year_follow_up_y_arm_1") 

sport_act_kerlic_sum_two_followup <- sport_act_kerlic_sum_two_followup %>% 
                                         left_join(one_followup_sum_days, by = "SRC_SUBJECT_ID")




sport_act_kerlic_sum_two_followup <- sport_act_kerlic_sum_two_followup %>%
  # change 999 to 0. don't know seems to infer that the child doesn't do that activiy
  mutate_at(vars(starts_with("SAI_SS_")), ~ replace(., which(.==999), 0)) %>% 
  # 0 = 0; 1 = 1; 2 = 2; 3 = 3; 4 = 4; 5 = 5; 6 = 6; 7 = 7; 8 = Once every 2 weeks; 9 = One day every month; 10 = Less than one day per month/; 999 = Don't know | When ballet/dance was not endorsed, values for the follow-up questions are missing. Here, missing values for  the  "... how many...?" follow-up questions have been replaced with "0". 
  #change this so that 0 = nothing, .125 = Less than one day per month, .25 = One day every month, .5 =Once every 2 weeks, 1 = 1 day per week and so on
  mutate_at(.vars = vars(ends_with("_PERWK_P_L")),
            .funs = funs(case_when(. == 10 ~ 1,
                                   . == 9 ~ 2,
                                   . == 8 ~ 3,
                                   . == 1 ~ 4,
                                   . == 2 ~ 5,
                                   . == 3 ~ 6,
                                   . == 4 ~ 7,
                                   . == 5 ~ 8,
                                   . == 6 ~ 9,
                                   . == 7 ~ 10,
                                   TRUE ~ as.numeric(.)))) %>%
  mutate(phys_ind_daypweek_sum = SAI_SS_SBOARD_PERWK_P_L + SAI_SS_CLIMB_PERWK_P_L + SAI_SS_GYM_PERWK_P_L + SAI_SS_ISKATE_PERWK_P_L + SAI_SS_M_ARTS_PERWK_P_L + SAI_SS_SKATE_PERWK_P_L + SAI_SS_DANCE_PERWK_P_L + SAI_SS_SURF_PERWK_P_L + SAI_SS_TENNIS_PERWK_P_L + SAI_SS_RUN_PERWK_P_L + SAI_SS_MMA_PERWK_P_L + SAI_SS_YOGA_PERWK_P_L+phys_ind_daypweek_sum_one_followup) %>%
  mutate(phys_team_daypweek_sum = SAI_SS_BASE_PERWK_P_L + SAI_SS_BASKET_PERWK_P_L + SAI_SS_FHOCK_PERWK_P_L + SAI_SS_FBALL_PERWK_P_L + SAI_SS_IHOCK_PERWK_P_L + SAI_SS_POLO_PERWK_P_L + SAI_SS_LAX_PERWK_P_L + SAI_SS_RUGBY_PERWK_P_L + SAI_SS_SOC_PERWK_P_L + SAI_SS_WPOLO_PERWK_P_L +SAI_SS_VBALL_PERWK_P_L+phys_team_daypweek_sum_one_followup) %>%
  mutate(art_daypweek_sum = SAI_SS_COLLECT_PERWK_P_L + SAI_SS_MUSIC_PERWK_P_L + SAI_SS_ART_PERWK_P_L + SAI_SS_DRAMA_PERWK_P_L + SAI_SS_CRAFTS_PERWK_P_L + SAI_SS_CHESS_PERWK_P_L+art_daypweek_sum_one_followup) %>%
  mutate(sport_act_all_daypweek_sum = phys_ind_daypweek_sum + phys_team_daypweek_sum + art_daypweek_sum) %>%
  dplyr::select(	SRC_SUBJECT_ID, EVENTNAME, ends_with("_daypweek_sum"))




sport_act_kerlic_sum_two_followup %>%  filter(EVENTNAME =="2_year_follow_up_y_arm_1") %>%
   dplyr::select(-SRC_SUBJECT_ID, -EVENTNAME, ends_with('_daypweek_sum')) %>%
     skimr::skim()

sport_act_kerlic_sum <- bind_rows(sport_act_kerlic_sum_baseline,sport_act_kerlic_sum_two_followup)

```



### physical activity
ABCD Youth Risk Behavior Survey Exercise Physical Activity 

```{r, cache = FALSE}

phyc_act <-as_tibble(read_csv(paste0(datafolder_5.1,"physical-health/ph_y_yrb.csv"))) 
names(phyc_act) <-toupper(colnames(phyc_act))
phyc_act <- phyc_act %>%  
  filter(EVENTNAME %in% c("baseline_year_1_arm_1","2_year_follow_up_y_arm_1" )) %>%
  rename(physc_act_days = PHYSICAL_ACTIVITY1_Y) %>%
  dplyr::select(SRC_SUBJECT_ID, EVENTNAME, physc_act_days)

#During the past 7 days, on how many days were you physically active for a total of at least 60 minutes per day? (Add up all the time you spent in any kind of physical activity that increased your heart rate and made you breathe hard some of the time)

phyc_act %>%  filter(EVENTNAME =="baseline_year_1_arm_1") %>%
   dplyr::select(-SRC_SUBJECT_ID, -EVENTNAME) %>%
   skimr::skim()


phyc_act %>%  filter(EVENTNAME =="2_year_follow_up_y_arm_1") %>%
   dplyr::select(-SRC_SUBJECT_ID, -EVENTNAME) %>%
   skimr::skim()
```

### BMI and Waist
ABCD Youth Anthropometrics Modified From PhenX 
values are questionable, even after deleting outliers. We ended up not using them.

NDAR_INV0P34UPZ9 height = 4
NDAR_INVZEKA1L7D height = 4.25 at baseline




```{r, cache = FALSE}
anthro <-as_tibble(read_csv(paste0(datafolder_5.1,"physical-health/ph_y_anthro.csv"))) 
names(anthro) <-toupper(colnames(anthro))
anthro <- anthro %>%  
  filter(EVENTNAME %in% c("baseline_year_1_arm_1","2_year_follow_up_y_arm_1" )) 

count(anthro,ANTHROWEIGHTCAST)
# remove those (82) with cast as BMI won't be accurate     
bmi_waist <- anthro %>% 
  # filter(ANTHROHEIGHTCALC > 30) %>% # remove those who are unusally short. Potentially error in data entering
  # filter(ANTHROWEIGHTCALC < 500) %>%
  # filter(!rstatix::is_outlier(ANTHROHEIGHTCALC) & !rstatix::is_outlier(ANTHROWEIGHTCALC)) %>%
  mutate(bmi = ifelse(ANTHROWEIGHTCAST == 0 | is.na(ANTHROWEIGHTCAST),
                      (ANTHROWEIGHTCALC/(ANTHROHEIGHTCALC^2))*703,NA)) %>%
  rename(waist = ANTHRO_WAIST_CM) %>%
  dplyr::select(SRC_SUBJECT_ID, EVENTNAME, bmi, waist, ANTHROWEIGHTCALC, ANTHROHEIGHTCALC)
  
# anthro %>% 
#   mutate(bmi = ifelse(ANTHROWEIGHTCAST == 0 | is.na(ANTHROWEIGHTCAST),
#                       (ANTHROWEIGHTCALC/(ANTHROHEIGHTCALC^2))*703,NA)) %>%
#   rename(waist = ANTHRO_WAIST_CM) %>%
#   arrange(desc(bmi)) %>% glimpse()

# bmi_waist %>% arrange(desc(bmi)) %>% glimpse()
# bmi_waist %>% arrange(bmi) %>% glimpse()
# 
# anthro %>% rstatix::identify_outliers(ANTHROHEIGHTCALC) %>%  arrange(ANTHROHEIGHTCALC) %>% View()
# anthro %>% rstatix::identify_outliers(ANTHROHEIGHTCALC) %>%  arrange(desc(ANTHROHEIGHTCALC)) %>% View()

# boxplot(anthro$ANTHROHEIGHTCALC)$out
# boxplot(anthro$ANTHROWEIGHTCALC)$out
# 
# boxplot(bmi_waist$ANTHROWEIGHTCALC)$out

bmi_waist %>%  filter(EVENTNAME =="baseline_year_1_arm_1") %>%
   dplyr::select(-SRC_SUBJECT_ID, -EVENTNAME) %>%
   skimr::skim()
bmi_waist %>%  filter(EVENTNAME =="2_year_follow_up_y_arm_1") %>%
   dplyr::select(-SRC_SUBJECT_ID, -EVENTNAME) %>%
   skimr::skim()
```


## Join data

Set the feature names

```{r}

Child_Sleep <- c("sleep_hours","sleep_disturb","sleep_initiate_maintain","sleep_breath","sleep_arousal","sleep_transition","sleep_somnolence","sleep_hyperhydrosis")

Physical_Activity <- c("phys_ind_daypweek_sum","phys_team_daypweek_sum","art_daypweek_sum","physc_act_days")

Child_Screen_Use <- c("matureGames_Screen","matureMovies_Screen","wkdySum_Screen","wkndSum_Screen")


Parent_Drug_Use <-c("tobacco_before_preg","tobacco_after_preg","alcohol_before_preg","alcohol_after_preg","marijuana_before_preg","marijuana_after_preg")


Child_Developmental_Adversity <- c("deveplopment_prematurity","deveplopment_birth_complications","deveplopment_pregnancy_complications")

Child_Socio_Demographics <- c("bilingual_use","marital","educationAvg","combinedIncome","householdSize","econ_insecurities_sum","area_deprivation_index","lead_risk","quartic_uniform_crime_reports","neighbo_safety_parent_sum","neighbo_safety_child_sum","sumSchool_environment","sumSchool_involvement","sumSchool_disengagement")

Social_Interaction<- c("parent_monitor_mean","fam_conflict_parent","fam_conflict_children","prosocial_parent_mean","prosocial_youth_mean")



features <- c(Child_Sleep,Physical_Activity,Child_Screen_Use,Parent_Drug_Use,Child_Developmental_Adversity,Child_Socio_Demographics,Social_Interaction)

```


```{r, cache=FALSE}
all_sum_vars <- plyr::join_all(list(ACSselected,sleepSum,youthScreenSum,
                      momSubstanceUse,adversitySum,bilingualSum,
                      demograpSum,ResidHistDer,NeighboSafety,
                      school_risk_sum,ParentMonitoring,FamilyConflict_sum,prosocial_sum,
                      sport_act_kerlic_sum,phyc_act,vision_idx), 
                 by=c('SRC_SUBJECT_ID','EVENTNAME'), type='full') %>%  
  filter(EVENTNAME %in% c("baseline_year_1_arm_1","2_year_follow_up_y_arm_1" )) 

all_sum_vars %>% count(EVENTNAME)

all_sum_vars <- all_sum_vars%>%
  #filter(visionProb != 1|is.na(visionProb)) %>% #remove subjects with eyesight problems 
    filter(!SRC_SUBJECT_ID %in% removed_subj) %>%
  dplyr::select(-visionProb)

all_sum_vars %>% count(EVENTNAME)

all_sum_vars %>%  filter(EVENTNAME =="baseline_year_1_arm_1") %>% dplyr::select(-1:-2) %>%
   skimr::skim()


all_sum_vars %>%  filter(EVENTNAME =="2_year_follow_up_y_arm_1") %>% dplyr::select(-1:-2) %>%
   skimr::skim()

```


## preprocess site
make sure that there are no members from the same family at different sites

```{r, cache = FALSE}
all_sum_vars_baseline <- all_sum_vars %>% filter(EVENTNAME =="baseline_year_1_arm_1") 

all_sum_vars_baseline %>% count(SITE_ID_L)

# check if there are members from the same family at different sites. There are 6 of them.
all_sum_vars_baseline %>%
  drop_na(SITE_ID_L) %>%
  filter(SITE_ID_L != "site22") %>%
  count(REL_FAMILY_ID, SITE_ID_L) %>%
  spread(SITE_ID_L, n, fill = 0) %>%
  dplyr::select(-REL_FAMILY_ID) %>% 
       as.matrix %>% 
       crossprod

#below will remove those
all_sum_vars_baseline_no_dup <- all_sum_vars_baseline %>%
  drop_na(SITE_ID_L) %>%
  filter(SITE_ID_L != "site22") %>%
  group_by(REL_FAMILY_ID) %>% 
  nest(SITE_ID_L, .key="SITE_ID_L") %>%
  mutate(dup = ifelse(length(c(unlist(SITE_ID_L)))==1,0,
                      ifelse(length(unique(c(unlist(SITE_ID_L)))) > 1,1,0))) %>%
  unnest(SITE_ID_L) %>%
  ungroup()

family_exclude <- unique(all_sum_vars_baseline_no_dup$REL_FAMILY_ID[which(all_sum_vars_baseline_no_dup$dup==1)])

all_sum_vars_no_dup <- all_sum_vars%>%
                 filter(!REL_FAMILY_ID %in% family_exclude)%>%
    drop_na(SITE_ID_L) %>%
  filter(SITE_ID_L != "site22")

all_sum_vars_no_dup %>% count(EVENTNAME)
### test whether the data set has all the features
setdiff(features,all_sum_vars_no_dup%>% colnames())

```


# Modeling for Socio-Demographic and Psychological Factors 

Samples:
REL_FAMILY_ID (9856 Levels)
SITE_ID_L (need to remove 22nd site. having too few subjects)
ALSO make sure about EVENTNAME

Target:
Factor analysis of psychopathology: pfactor

46 Features:
soc-demo-lifestyle-dev


Features by catergories:


Child Sleep (8):
sleep_hours
sleep_disturb
sleep_initiate_maintain
sleep_breath
sleep_arousal
sleep_transition
sleep_somnolence
sleep_hyperhydrosis

Physical Activity (4):
phys_ind_daypweek_sum
phys_team_daypweek_sum
art_daypweek_sum
physc_act_days

Child Screen Use (4):
matureGames_Screen
matureMovies_Screen
wkdySum_Screen
wkndSum_Screen

Parent Drug Use (6):
tobacco_before_preg
tobacco_after_preg
alcohol_before_preg
alcohol_after_preg
marijuana_before_preg
marijuana_after_preg

Child Developmental Adversity (3):
deveplopment_prematurity
deveplopment_birth_complications
deveplopment_pregnancy_complications

Child Socio-Demographics (14):
bilingual_use
marital
educationAvg
combinedIncome
householdSize
econ_insecurities_sum
area_deprivation_index
lead_risk
quartic_uniform_crime_reports
neighbo_safety_parent_sum
neighbo_safety_child_sum
sumSchool_environment
sumSchool_involvement
sumSchool_disengagement

Social Interaction (5):
parent_monitor_mean
fam_conflict_parent
fam_conflict_children
prosocial_parent_mean
prosocial_youth_mean



set up vector of names based on different catorgies of features

### process data for modelling

```{r}

all_features_no_dup <- all_sum_vars_no_dup %>% dplyr::select(all_of(subj_info),all_of(features))
## change the character variables and factors into numeric values

factor_features <- c("tobacco_before_preg","tobacco_after_preg","alcohol_before_preg"    ,"alcohol_after_preg","marijuana_before_preg","marijuana_after_preg","deveplopment_prematurity", "marital"  )

all_features_no_dup_num <- all_features_no_dup %>%
                mutate(marital = recode_factor(as.factor(marital),married=1,  widowed=2,divorced=3,separated=4,neverMarried=5,livingWithPartner=6,.default = 1))
#%>%
#  mutate_if(is.factor,as.numeric)
   

###check the NAs in both baseline and followup data sets
  all_features_no_dup_num_baseline <- all_features_no_dup_num%>%
    filter(EVENTNAME=="baseline_year_1_arm_1") 
  
naniar::vis_miss(all_features_no_dup_num_baseline)

 all_features_no_dup_num_followup <- all_features_no_dup_num%>%
    filter(EVENTNAME=="2_year_follow_up_y_arm_1") 
  
naniar::vis_miss(all_features_no_dup_num_followup)
```
Loading tables for plotting

```{r}
plotting_names <- read.csv(paste0(commonfolder,"NonBrainFeaturesRead.csv"))

## clean plotting names

plotting_names[72,1] <- "marital_X2"
plotting_names[73,1] <- "marital_X3"
plotting_names[74,1] <- "marital_X4"
plotting_names[75,1] <- "marital_X5"
plotting_names[76,1] <- "marital_X6"

names(plotting_names) <- c("feature_names","plotting_name")

```

## Clean up variables



### Replace the variables with baseline data in the followup

The following variables are only found in the baseline. Those variables are:

"wkdySum_Screen"  

"wkndSum_Screen"                      

"tobacco_before_preg"

"tobacco_after_preg"

"alcohol_before_preg"                 

"alcohol_after_preg"  

"marijuana_before_preg"

"marijuana_after_preg"                

"deveplopment_prematurity"            

"deveplopment_birth_complications"  

"deveplopment_pregnancy_complications"
 
 "householdSize"
 
 "area_deprivation_index"
 
 "lead_risk"
 
 "quartic_uniform_crime_reports"    

We use the exact replications in the followup analysis.

The following variables appear in both baseline and followup data:


 "sleep_hours"
 
 "sleep_disturb"
 
 "sleep_initiate_maintain"  
 
 "sleep_breath" 
 
 "sleep_arousal"
 
 "sleep_transition"
 
 "sleep_somnolence"         

 "sleep_hyperhydrosis"  

 "physc_act_days"

 "matureGames_Screen"

 "matureMovies_Screen"      

"bilingual_use"

"neighbo_safety_parent_sum"

"neighbo_safety_child_sum"

"sumSchool_environment"    

"sumSchool_involvement"

"sumSchool_disengagement"

"parent_monitor_mean"

"fam_conflict_parent"      

"fam_conflict_children"

"prosocial_parent_mean"

"prosocial_youth_mean"


Variable that has followup information but in other variables


"phys_ind_daypweek_sum"

"phys_team_daypweek_sum"   

"art_daypweek_sum" 

"marital"  

"educationAvg"                        

"combinedIncome"

"econ_insecurities_sum"       

```{r}
features_fix_na <- c("wkdySum_Screen"  ,"wkndSum_Screen","tobacco_before_preg","tobacco_after_preg","alcohol_before_preg","alcohol_after_preg","marijuana_before_preg","marijuana_after_preg","deveplopment_prematurity","deveplopment_birth_complications","deveplopment_pregnancy_complications","householdSize","area_deprivation_index","lead_risk","quartic_uniform_crime_reports"  )

all_features_no_dup_na_fix_baseline <- all_features_no_dup_num_baseline%>%
                                       dplyr::select(all_of(c("SRC_SUBJECT_ID","SITE_ID_L")),all_of(features_fix_na))

all_features_no_dup_na_fix_followup <- all_features_no_dup_num_followup %>% 
                                       dplyr::select(-all_of(features_fix_na))
all_features_no_dup_na_fixed_followup <- left_join(all_features_no_dup_na_fix_followup,
                                                   all_features_no_dup_na_fix_baseline,
                                                   by =c("SRC_SUBJECT_ID","SITE_ID_L"))

## plot the information of missingness after all the NAs are fixed
naniar::vis_miss(all_features_no_dup_na_fixed_followup)

all_features_no_dup_na_fixed <- bind_rows(all_features_no_dup_num_baseline,all_features_no_dup_na_fixed_followup)
```

```{r}
## select variables and keep the order

Child_Sleep <-c("sleep_hours","sleep_disturb","sleep_initiate_maintain","sleep_breath","sleep_arousal","sleep_transition","sleep_somnolence","sleep_hyperhydrosis")

Physical_Activity <-c("phys_ind_daypweek_sum","phys_team_daypweek_sum","art_daypweek_sum","physc_act_days")

Child_Screen_Use <-c("matureGames_Screen","matureMovies_Screen","wkdySum_Screen","wkndSum_Screen")

Parent_Drug_Use <-c("tobacco_before_preg","tobacco_after_preg","alcohol_before_preg","alcohol_after_preg","marijuana_before_preg",
"marijuana_after_preg")

Child_evelopmental_Adversity <-c("deveplopment_prematurity","deveplopment_birth_complications","deveplopment_pregnancy_complications")


Child_Socio_Demographics<-c("bilingual_use","marital","educationAvg","combinedIncome","householdSize","econ_insecurities_sum","area_deprivation_index","lead_risk","quartic_uniform_crime_reports","neighbo_safety_parent_sum","neighbo_safety_child_sum","sumSchool_environment","sumSchool_involvement","sumSchool_disengagement")

Social_Interaction <-c("parent_monitor_mean","fam_conflict_parent","fam_conflict_children","prosocial_parent_mean","prosocial_youth_mean")

table_features_no_dup <- all_features_no_dup_na_fixed %>% dplyr::select(all_of(subj_info),
                                                               all_of(Child_Socio_Demographics),
                                                               all_of(Social_Interaction),
                                                               all_of(Parent_Drug_Use),
                                                               all_of(Child_Sleep),
                                                               all_of(Physical_Activity),
                                                               all_of(Child_Screen_Use),
                                                               all_of(Child_evelopmental_Adversity))

## convert the plotting names
table_features <- c(Child_Socio_Demographics,Social_Interaction,Parent_Drug_Use,Child_Sleep,Physical_Activity,Child_Screen_Use,Child_evelopmental_Adversity)
## get the plotting names
plotting_names_ses <- plotting_names %>% filter(feature_names %in% table_features)

changed_plotting_names <- tibble(feature_names =c("marital","tobacco_before_preg","tobacco_after_preg","alcohol_before_preg","alcohol_after_preg","marijuana_before_preg","marijuana_after_preg","deveplopment_prematurity"),
                                 plotting_name = c("Parent Marital Status","Tobbaco Before Pregnant","Tabbaco After Pregnant","Alcohol Before Pregnant","Alcohol After Pregnant","Marijuana Before Pregant","Marijuana After Pregant","Developmental Prematurity"))

plotting_names_ses_all <- bind_rows(plotting_names_ses,changed_plotting_names)

table_features_names <- rep(NA,dim(plotting_names_ses_all)[1])

for(i in 1: dim(plotting_names_ses_all)[1]){
  table_features_names[i] <- plotting_names_ses_all$plotting_name[which(plotting_names_ses_all$feature_names==table_features[i])]
}

table_plotting_names <- tibble(feature_names = table_features,
                               plotting_names = table_features_names)

table_features_no_dup_baseline <- table_features_no_dup %>% 
                                  filter(EVENTNAME == "baseline_year_1_arm_1")%>%
                                  dplyr::select(-all_of(subj_info))

names(table_features_no_dup_baseline) <- table_plotting_names$plotting_names
### summary table for baseline

table_features_no_dup_baseline %>% 
summarytools::dfSummary(., 
          #plain.ascii  = FALSE, 
          style        = "grid", 
          graph.magnif = 0.75, 
          valid.col    = FALSE,
          tmp.img.dir  = "/tmp") %>% 
         print(., max.tbl.height = 300,
      method = "render")



table_features_no_dup_baseline%>%
  skimr::skim()

### fixing the followup table only keep the variables that are not all NA in the follow up

followup_names_keep <- plotting_names_ses_all %>% filter(!plotting_names_ses_all$feature_names %in% features_fix_na)

table_features_no_dup_followup <- table_features_no_dup %>% 
                                  filter(EVENTNAME == "2_year_follow_up_y_arm_1")%>%
                                  dplyr::select(-all_of(subj_info))%>%
                                  dplyr::select(-all_of(features_fix_na))
followup_features <- colnames(table_features_no_dup_followup)

followup_features_names <- rep(NA,dim(followup_names_keep)[1])

for(i in 1: dim(followup_names_keep)[1]){
  followup_features_names[i] <- followup_names_keep$plotting_name[which(followup_names_keep$feature_names==followup_features[i])]
}

followup_plotting_names <- tibble(feature_names = followup_features,
                               plotting_names = followup_features_names)

names(table_features_no_dup_followup) <- followup_plotting_names$plotting_names
### summary table for baseline

table_features_no_dup_followup %>% 
summarytools::dfSummary(., 
          #plain.ascii  = FALSE, 
          style        = "grid", 
          graph.magnif = 0.75, 
          valid.col    = FALSE,
          tmp.img.dir  = "/tmp") %>% 
         print(., max.tbl.height = 300,
      method = "render")


table_features_no_dup_followup%>%
  skimr::skim()


saveRDS(table_features_no_dup_baseline,paste0(scriptfold,'Common_psy_gene_brain_all/saved_outputs/scatter_plots/ses_table_features_no_dup_baseline_5.1', '.RData'))
saveRDS(table_features_no_dup_followup,paste0(scriptfold,'Common_psy_gene_brain_all/saved_outputs/scatter_plots/ses_table_features_no_dup_followup_5.1', '.RData'))

```

Making data splits by site.

```{r}

site_col <- all_features_no_dup_na_fixed  %>%
  distinct(SITE_ID_L) %>% 
  arrange(SITE_ID_L) 

site_list <- as.list(site_col$SITE_ID_L)

site_char <- as.character(unlist(site_col$SITE_ID_L))

split_list <- purrr::map(site_list, ~split_func(.x,data_input =all_features_no_dup_na_fixed ))


names(split_list) <- site_char

```



Join features and response across sites


```{r}

feature_resp_join <- function(site_input){
  features_list <- split_list[[site_input]]
  baseline_train_features <- training(features_list)%>%
                             filter(EVENTNAME == "baseline_year_1_arm_1")
  baseline_test_features <- testing(features_list)%>%
                             filter(EVENTNAME == "baseline_year_1_arm_1")
  followup_train_features <- training(features_list)%>%
                             filter(EVENTNAME == "2_year_follow_up_y_arm_1")
  followup_test_features <- testing(features_list)%>%
                             filter(EVENTNAME == "2_year_follow_up_y_arm_1")
  
  baseline_train <- baseline_train_gfactor[[site_input]]
  baseline_test <- baseline_test_gfactor[[site_input]]
  followup_train <- followup_train_gfactor[[site_input]]
  followup_test <- followup_test_gfactor[[site_input]]
  ## NAs are removed here
  baseline_train_all <- full_join(baseline_train_features,baseline_train,by = "SRC_SUBJECT_ID")%>%
                        drop_na("gfactor")
  baseline_test_all <- full_join(baseline_test_features,baseline_test,by = "SRC_SUBJECT_ID")%>%
                        drop_na("gfactor")
  followup_train_all <- full_join(followup_train_features,followup_train,by = "SRC_SUBJECT_ID")%>%
                        drop_na("gfactor")
  followup_test_all <- full_join(followup_test_features,followup_test,by = "SRC_SUBJECT_ID")%>%
                        drop_na("gfactor")
  
  baseline_train_select <- baseline_train_all%>%
                           dplyr::select(-all_of(subj_info))
  baseline_test_select <- baseline_test_all%>%
                           dplyr::select(-all_of(subj_info))
  followup_train_select <- followup_train_all%>%
                           dplyr::select(-all_of(subj_info))
  followup_test_select <- followup_test_all%>%
                           dplyr::select(-all_of(subj_info))
  
  
return(list(baseline_train = baseline_train_all,
            baseline_test=baseline_test_all,
            followup_train=followup_train_all,
            followup_test=followup_test_all,
            baseline_train_select = baseline_train_select,
            baseline_test_select=baseline_test_select,
            followup_train_select=followup_train_select,
            followup_test_select=followup_test_select))
}


gfactor_ses_split_list <- purrr::map(site_char,~feature_resp_join(site_input = .))

names(gfactor_ses_split_list) <- site_char


gfactor_ses_baseline_train <- purrr::map(gfactor_ses_split_list,"baseline_train")
gfactor_ses_baseline_test <- purrr::map(gfactor_ses_split_list,"baseline_test")
gfactor_ses_followup_train <- purrr::map(gfactor_ses_split_list,"followup_train")
gfactor_ses_followup_test <- purrr::map(gfactor_ses_split_list,"followup_test")


gfactor_ses_baseline_train_select <- purrr::map(gfactor_ses_split_list,"baseline_train_select")
gfactor_ses_baseline_test_select <- purrr::map(gfactor_ses_split_list,"baseline_test_select")
gfactor_ses_followup_train_select <- purrr::map(gfactor_ses_split_list,"followup_train_select")
gfactor_ses_followup_test_select <- purrr::map(gfactor_ses_split_list,"followup_test_select")

```


### Demographic tables between two groups 

NDAR_INV0P34UPZ9 height = 4
NDAR_INVZEKA1L7D height = 4.25 at baseline

```{r}



table_features_baseline_all <- table_features_no_dup %>% 
  mutate(marital= recode_factor(as.factor( marital ),
                `1` = "married", `2` = "widowed", `3` = "divorced", 
                `4` = "separated", `5` = "neverMarried", `6` = "livingWithPartner",
                `777` = NA_character_, `999` = NA_character_,
                .default = "married")) %>%
# mutate( householdSize = as.factor(householdSize)) %>% 
 #mutate(combinedIncome = as.factor(combinedIncome)) %>% 
                                  filter(EVENTNAME == "baseline_year_1_arm_1") 

table_features_baseline_all_subj <- table_features_baseline_all %>% 
                                           dplyr::select(all_of(subj_info))

table_features_baseline_all_no_subj <- table_features_baseline_all %>% 
                                           dplyr::select(-all_of(subj_info))


baseline_all_of_features <- colnames(table_features_baseline_all_no_subj)

baseline_all_of_features_names <- rep(NA,dim(plotting_names_ses_all)[1])

for(i in 1: dim(plotting_names_ses_all)[1]){
  baseline_all_of_features_names[i] <- plotting_names_ses_all$plotting_name[which(plotting_names_ses_all$feature_names==baseline_all_of_features[i])]
}

baseline_plotting_all_names <- tibble(feature_names = baseline_all_of_features,
                               plotting_names = baseline_all_of_features_names)

names(table_features_baseline_all_no_subj) <- baseline_plotting_all_names$plotting_names



table_features_baseline_all <- bind_cols(table_features_baseline_all_subj,
                                                        table_features_baseline_all_no_subj)



### divide the ses data into two groups


gfactor_ses_followup_test_select_tibble_all <- gfactor_ses_followup_test %>% do.call(rbind,.)


features_baseline_with_cog_score <- table_features_baseline_all %>% 
                                    filter( SRC_SUBJECT_ID %in% gfactor_ses_followup_test_select_tibble_all$SRC_SUBJECT_ID)

followup_no_cog_id <- demo_followup %>% filter( ! SRC_SUBJECT_ID %in%  gfactor_ses_followup_test_select_tibble_all$SRC_SUBJECT_ID)


features_baseline_no_cog_score <- table_features_baseline_all %>% 
                                    filter( SRC_SUBJECT_ID %in% followup_no_cog_id$SRC_SUBJECT_ID)

### get the basic demographic information
bmi_waist_baseline <- bmi_waist %>% filter(EVENTNAME == "baseline_year_1_arm_1") %>%dplyr::select(SRC_SUBJECT_ID,bmi)

names(bmi_waist_baseline) <- c("SRC_SUBJECT_ID","BMI" )

ACSselected_baseline_select <-ACSselected_baseline %>% dplyr::select( "SRC_SUBJECT_ID" ,"INTERVIEW_AGE", "DEMO_SEX_V2","RACE_ETHNICITY")

names(ACSselected_baseline_select)  <- c("SRC_SUBJECT_ID","Age" ,"Sex","Race")

features_baseline_with_cog_score_all <- plyr::join_all(list(features_baseline_with_cog_score,
                                                            bmi_waist_baseline,ACSselected_baseline_select),
                                                       by = "SRC_SUBJECT_ID", type = "left") %>% 
                                        filter(! SRC_SUBJECT_ID %in% c("NDAR_INV0P34UPZ9","NDAR_INVZEKA1L7D"))




features_baseline_no_cog_score_all <- plyr::join_all(list(features_baseline_no_cog_score,
                                                            bmi_waist_baseline,ACSselected_baseline_select),
                                                       by = "SRC_SUBJECT_ID", type = "left")%>% 
                                        filter(! SRC_SUBJECT_ID %in% c("NDAR_INV0P34UPZ9","NDAR_INVZEKA1L7D"))



feature_names_factor_test <- features_baseline_with_cog_score_all%>%dplyr::select(where(is.factor)) %>% colnames() %>% set_names()

feature_names_num_test <- features_baseline_with_cog_score_all%>% dplyr::select(-all_of(feature_names_factor_test)) %>%
                             dplyr::select(-all_of(subj_info)) %>%
                        colnames() %>% set_names()





robust_conti <- function(cog_input = features_baseline_with_cog_score_all,
                       no_cog_input = features_baseline_no_cog_score_all,
                       names_input = "Sleep Hyperhydrosis"  ){
  cog_tibble <- tibble(name = rep("cog",nrow(cog_input)),value = cog_input[[names_input]] %>% as.numeric())
  no_cog_tibble <- tibble(name = rep("no_cog",nrow(no_cog_input)),value = no_cog_input[[names_input]] %>% as.numeric())
  all_tibble <- bind_rows(cog_tibble,no_cog_tibble) %>% drop_na()
  test_results <- WRS2::yuen(value ~ name, data = all_tibble,tr = 0.2)
 p_val_str <- ifelse(test_results$p.value < 0.001, "<0.001", paste0("= ",round(test_results$p.value,3))) 
 
 output_str <- paste0("Yuen’s t(",round(test_results$df),") = " ,round(test_results$test,3), ", p ",p_val_str, ", Cohen’s d = ", round(test_results$effsize,3))
 return(output_str)
}

robust_conti_other <- function(cog_input = features_followup_with_cog_score_all,
                       no_cog_input = features_followup_no_cog_score_all,
                       names_input = feature_names_num_test[1]  ){
  cog_tibble <- tibble(name = rep("cog",nrow(cog_input)),value = cog_input[[names_input]] %>% as.numeric())
  no_cog_tibble <- tibble(name = rep("no_cog",nrow(no_cog_input)),value = no_cog_input[[names_input]] %>% as.numeric())
  all_tibble <- bind_rows(cog_tibble,no_cog_tibble) %>% drop_na()
  test_results <- WRS2::yuen(value ~ name, data = all_tibble,tr = 0.15)

 p_val_str <- ifelse(test_results$p.value < 0.001, "< 0.001", paste0("= ",round(test_results$p.value,3))) 
 
 output_str <- paste0("Yuen’s t(",round(test_results$df),") = " ,round(test_results$test,3), ", p ",p_val_str, ", Cohen’s d = ", round(test_results$effsize,3))
 return(output_str)
}

test_cate <- function(cog_input = features_baseline_with_cog_score_all,
                       no_cog_input = features_baseline_no_cog_score_all,
                       names_input = "Race" ){
  
 no_cog <- no_cog_input %>% dplyr::select(all_of(names_input)) %>% drop_na()
 names(no_cog) <- c("factor1")
  
  cog <- cog_input %>% dplyr::select(all_of(names_input)) %>% drop_na()
 names(cog) <- c("factor1")


no_cog_count <- no_cog %>% 
  group_by(factor1) %>%
  summarise(no_rows = length(factor1)) %>% 
  rename(count_no_cog = no_rows)


cog_count <- cog %>% 
  group_by(factor1) %>%
  summarise(no_rows = length(factor1)) %>% 
  rename(count_cog = no_rows)

count_all_data <- full_join(no_cog_count,cog_count, by = "factor1")%>% mutate_all(~replace(., is.na(.), 0))


test_output <- chisq.test(count_all_data$count_cog , count_all_data$count_no_cog)

 p_val_str <- ifelse(test_output$p.value < 0.001, "< 0.001", paste0("= ",round(test_output$p.value,3))) 

 output_string <- paste0("Chi_squared(",test_output$parameter,", N = ",nrow(no_cog)+nrow(cog),")", " = ", test_output$statistic, ", p ", p_val_str)

return(output_string)
}



robust_feature_names_num_test <- feature_names_num_test[-26]
robust_feature_names_num_test_other <- feature_names_num_test[26]


robust_conti_p_val_baseline <- robust_feature_names_num_test %>% purrr::map(.,~robust_conti(cog_input = features_baseline_with_cog_score_all,
                       no_cog_input = features_baseline_no_cog_score_all,
                       names_input = .))

print(robust_conti_p_val_baseline)


robust_conti_p_val_baseline_other <- robust_feature_names_num_test_other %>% 
  purrr::map(.,~robust_conti_other(cog_input = features_baseline_with_cog_score_all,
                       no_cog_input = features_baseline_no_cog_score_all,
                       names_input = .))

print(robust_conti_p_val_baseline_other)


factor_p_val_baseline <- feature_names_factor_test %>% purrr::map(.,~test_cate(cog_input = features_baseline_with_cog_score_all,
                       no_cog_input = features_baseline_no_cog_score_all,
                       names_input = .))

print(factor_p_val_baseline)
```

```{r,results='asis'}

features_baseline_with_cog_score_all %>%  dplyr::select(-all_of(subj_info)) %>% 
summarytools::dfSummary(., 
          #plain.ascii  = FALSE, 
          style        = "grid", 
          graph.magnif = 0.75, 
          valid.col    = FALSE,
          tmp.img.dir  = "/tmp")%>% 
         print(., max.tbl.height = 300,
      method = "render")



features_baseline_no_cog_score_all%>%  dplyr::select(-all_of(subj_info)) %>% 
summarytools::dfSummary(., 
          #plain.ascii  = FALSE, 
          style        = "grid", 
          graph.magnif = 0.75, 
          valid.col    = FALSE,
          tmp.img.dir  = "/tmp") %>% 
         print(., max.tbl.height = 300,
      method = "render")

```





```{r}



table_features_no_dup_followup_all <- table_features_no_dup %>% 
  mutate(marital= recode_factor(as.factor( marital ),
                `1` = "married", `2` = "widowed", `3` = "divorced", 
                `4` = "separated", `5` = "neverMarried", `6` = "livingWithPartner",
                `777` = NA_character_, `999` = NA_character_,
                .default = "married")) %>%
 mutate( householdSize = as.factor(householdSize)) %>% 
 mutate(combinedIncome = as.factor(combinedIncome)) %>% 
                                  filter(EVENTNAME == "2_year_follow_up_y_arm_1") 

table_features_no_dup_followup_all_subj <- table_features_no_dup_followup_all %>% 
                                           dplyr::select(all_of(subj_info))

table_features_no_dup_followup_all_no_subj <- table_features_no_dup_followup_all %>% 
                                           dplyr::select(-all_of(subj_info))


followup_all_of_features <- colnames(table_features_no_dup_followup_all_no_subj)

followup_all_of_features_names <- rep(NA,dim(plotting_names_ses_all)[1])

for(i in 1: dim(plotting_names_ses_all)[1]){
  followup_all_of_features_names[i] <- plotting_names_ses_all$plotting_name[which(plotting_names_ses_all$feature_names==followup_all_of_features[i])]
}

followup_plotting_all_names <- tibble(feature_names = followup_all_of_features,
                               plotting_names = followup_all_of_features_names)

names(table_features_no_dup_followup_all_no_subj) <- followup_plotting_all_names$plotting_names



table_features_no_dup_followup_all <- bind_cols(table_features_no_dup_followup_all_subj,
                                                        table_features_no_dup_followup_all_no_subj)



### divide the ses data into two groups


gfactor_ses_followup_test_select_tibble_all <- gfactor_ses_followup_test %>% do.call(rbind,.)


features_followup_with_cog_score <- table_features_no_dup_followup_all %>% 
                                    filter( SRC_SUBJECT_ID %in% gfactor_ses_followup_test_select_tibble_all$SRC_SUBJECT_ID)



features_followup_no_cog_score <- table_features_no_dup_followup_all %>% 
                                    filter(  SRC_SUBJECT_ID %in% followup_no_cog_id$SRC_SUBJECT_ID)

### get the basic demographic information
bmi_waist_followup <- bmi_waist %>% filter(EVENTNAME == "2_year_follow_up_y_arm_1") %>%dplyr::select(SRC_SUBJECT_ID,bmi)

names(bmi_waist_followup) <- c("SRC_SUBJECT_ID","BMI" )

ACSselected_followup_select <-ACSselected_followup %>% dplyr::select( "SRC_SUBJECT_ID" ,"INTERVIEW_AGE", "DEMO_SEX_V2","RACE_ETHNICITY")

names(ACSselected_followup_select)  <- c("SRC_SUBJECT_ID","Age" ,"Sex","Race")

features_followup_with_cog_score_all <- plyr::join_all(list(features_followup_with_cog_score,
                                                            bmi_waist_followup,ACSselected_followup_select),
                                                       by = "SRC_SUBJECT_ID", type = "left")




features_followup_no_cog_score_all <- plyr::join_all(list(features_followup_no_cog_score,
                                                            bmi_waist_followup,ACSselected_followup_select),
                                                       by = "SRC_SUBJECT_ID", type = "left")



feature_names_factor_test <- features_followup_with_cog_score_all%>%dplyr::select(where(is.factor)) %>% colnames() %>% set_names()

feature_names_num_test <- features_followup_with_cog_score_all%>% dplyr::select(-all_of(feature_names_factor_test)) %>%
                             dplyr::select(-all_of(subj_info)) %>%
                        colnames() %>% set_names()



test_conti <- function(cog_input = features_followup_with_cog_score_all,
                       no_cog_input = features_followup_no_cog_score_all,
                       names_input = feature_names_num_test[1]){
  cog_vec  <- cog_input[[names_input]]
  no_cog_vec <- no_cog_input[[names_input]]
  test_list <- t.test(cog_vec,no_cog_vec)
  return(test_list$p.value)
}

test_cate <- function(cog_input = features_followup_with_cog_score_all,
                       no_cog_input = features_followup_no_cog_score_all,
                       names_input = feature_names_factor_test[3]){
  
 no_cog <- no_cog_input %>% dplyr::select(all_of(names_input)) %>% drop_na()
 names(no_cog) <- c("factor1")
  
  cog <- cog_input %>% dplyr::select(all_of(names_input)) %>% drop_na()
 names(cog) <- c("factor1")


no_cog_count <- no_cog %>% 
  group_by(factor1) %>%
  summarise(no_rows = length(factor1)) %>% 
  rename(count_no_cog = no_rows)


cog_count <- cog %>% 
  group_by(factor1) %>%
  summarise(no_rows = length(factor1)) %>% 
  rename(count_cog = no_rows)

count_all_data <- full_join(no_cog_count,cog_count, by = "factor1")%>% mutate_all(~replace(., is.na(.), 0))


test_output <- chisq.test(count_all_data$count_cog , count_all_data$count_no_cog)
return(test_output$p.value)
}

conti_p_val_followup <- feature_names_num_test %>% purrr::map(.,~test_conti(cog_input = features_followup_with_cog_score_all,
                       no_cog_input = features_followup_no_cog_score_all,
                       names_input = .))
  
factor_p_val_followup <- feature_names_factor_test %>% purrr::map(.,~test_cate(cog_input = features_followup_with_cog_score_all,
                       no_cog_input = features_followup_no_cog_score_all,
                       names_input = .))


```

### scale the data set with dummy variables 

This function can be run by replacing select and map function in the r functions file. Or, run it without loading the PLS packages.

The process of data preparation is as follows

1. Use a recipe to change the dummy variables into the continuous variables. (In the mean time impute the NA with mode and then K-nearest-neightbours)
2. Scale the baseline train and test data separately. Then scale the followup train and test with the mean and standard deviation from baseline train and test respectively.



```{r, eval=FALSE}

processed_features_gfactor_ses_list <- purrr::pmap(list(gfactor_ses_baseline_train,
                                                        gfactor_ses_baseline_test,
                                                        gfactor_ses_followup_train,
                                                        gfactor_ses_followup_test),
                                                   ~data_processing_cross_sites_seperate_dummy(baseline_train=..1,
                                                 baseline_test=..2,
                                                 followup_train=..3,
                                                 followup_test=..4))

```

save and load the processed datasets

```{r,eval=FALSE,echo=FALSE}
saveRDS(processed_features_gfactor_ses_list,paste0(scriptfold,'Common_psy_gene_brain_all/saved_outputs/processed_features_gfactor_ses_list_5.1', '.RData'))
```

## loading the processed data output


```{r,eval=TRUE,echo=FALSE}
processed_features_gfactor_ses_list <- readRDS(paste0(scriptfold,'Common_psy_gene_brain_all/saved_outputs/processed_features_gfactor_ses_list_5.1', '.RData'))
```



### manually fixing variavbles with all zeros in the test datasets

Some of the factor features are all zero in the test sets. They are removed in the recipe because they have a standard deviation of 0. Then those variables are deleted. When fit the model in the test sets, this problem leads to the model fitting function failing to run.

As a part of the imputation that is never done by the recipe function. Those NAs in the data set are going to be replaced with 0.

We find out that 
1. observations in site 3 do not have crime report.
2. observations in site 7 do not have widowers.

```{r}
### find the features
train_colnames_site03 <- processed_features_gfactor_ses_list[["site03"]][["output_train_baseline"]]%>% colnames()
test_colnames_site03 <- processed_features_gfactor_ses_list[["site03"]][["output_test_baseline"]]%>% colnames()
site03_add <- setdiff(train_colnames_site03,test_colnames_site03)
site03_add
### check the original data sets

gfactor_ses_baseline_test$site03[[site03_add]]
### manually fix baseline and followup data

processed_features_gfactor_ses_list[["site03"]][["output_test_baseline"]] <- processed_features_gfactor_ses_list[["site03"]][["output_test_baseline"]]%>% mutate(quartic_uniform_crime_reports=0)


processed_features_gfactor_ses_list[["site03"]][["output_test_followup"]] <- processed_features_gfactor_ses_list[["site03"]][["output_test_followup"]]%>% mutate(quartic_uniform_crime_reports=0)

### do the same thing for site07, site20

### find the features
train_colnames_site07 <- processed_features_gfactor_ses_list[["site07"]][["output_train_baseline"]]%>% colnames()
test_colnames_site07 <- processed_features_gfactor_ses_list[["site07"]][["output_test_baseline"]]%>% colnames()
site07_add <- setdiff(train_colnames_site07,test_colnames_site07)
site07_add

### check the original data sets

which(gfactor_ses_baseline_test$site07[["marital"]]==2)


### manually fix baseline and followup data

processed_features_gfactor_ses_list[["site07"]][["output_test_baseline"]] <- processed_features_gfactor_ses_list[["site07"]][["output_test_baseline"]]%>% mutate(marital_X2=0)


processed_features_gfactor_ses_list[["site07"]][["output_test_followup"]] <- processed_features_gfactor_ses_list[["site07"]][["output_test_followup"]]%>% mutate(marital_X2=0)

```


extract the processed datasets

```{r}
processed_ses_baseline_train <- purrr::map(processed_features_gfactor_ses_list,"output_train_baseline")
processed_ses_baseline_test <- purrr::map(processed_features_gfactor_ses_list,"output_test_baseline")
processed_ses_followup_train <- purrr::map(processed_features_gfactor_ses_list,"output_train_followup")
processed_ses_followup_test <- purrr::map(processed_features_gfactor_ses_list,"output_test_followup")

processed_ses_baseline_train_select <- purrr::map(processed_ses_baseline_train,~dplyr::select(.,-all_of(subj_info)))
processed_ses_baseline_test_select <- purrr::map(processed_ses_baseline_test,~dplyr::select(.,-all_of(subj_info)))
processed_ses_followup_train_select <- purrr::map(processed_ses_followup_train,~dplyr::select(.,-all_of(subj_info)))
processed_ses_followup_test_select <- purrr::map(processed_ses_followup_test,~dplyr::select(.,-all_of(subj_info)))


```


# model fitting

## Baseline model fitting

```{r}

### fit the enet model
### baseline
dummy_features <- processed_ses_baseline_train_select[[1]] %>% dplyr::select(-"gfactor") %>% colnames()


ses_baseline_recipe_list <- purrr::map(.x = processed_ses_baseline_train_select,
                             ~recipe_prep(train_input=.x, features_input = dummy_features)) 

ses_pls_fit_baseline <-purrr::map(.x=ses_baseline_recipe_list,
                              ~pls_tune(recipe_input = .x,feature_input =dummy_features )) 

ses_pls_fit_baseline_wf <- purrr::map(ses_pls_fit_baseline,"pls_final_wf")


ses_pls_model_fit_baseline <- purrr::pmap(list(ses_baseline_recipe_list,
                                        ses_pls_fit_baseline_wf,
                                        processed_ses_baseline_test_select),~
                                                 model_final_fit(recipe_input = ..1, 
                                    wf_input = ..2,
                                    test_data = ..3)) 


ses_pls_pred_baseline <- purrr::map(ses_pls_model_fit_baseline,"model_predict")

ses_pls_model_fit_baseline_train <- purrr::pmap(list(ses_baseline_recipe_list,
                                        ses_pls_fit_baseline_wf,
                                        processed_ses_baseline_train_select),~
                                                 model_final_fit(recipe_input = ..1, 
                                    wf_input = ..2,
                                    test_data = ..3)) 

ses_pls_pred_baseline_train <- purrr::map(ses_pls_model_fit_baseline_train,"model_predict")


ses_baseline_metric <- purrr::map2(.x=ses_pls_pred_baseline,
     .y=processed_ses_baseline_test,~metric_compute_site(data_input =.x ,
                                           site_input = .y)) %>%
                      do.call(rbind,.) %>% 
                      drop_na(site)

      ses_baseline_metric%>% 
    kableExtra::kbl(caption = "metrics for all sites in baseline") %>%
    kableExtra::kable_classic(full_width = F, 
                             html_font = "Cambria")


ses_baseline_metric_avg <- average_metric_one_mod(metric_list =ses_baseline_metric)

avg_table_var_names <- c("correlation (sd)", "tradrsq (sd)","MAE (sd)","RMSE (sd)"  )


ses_baseline_metric_avg_table <- ses_baseline_metric_avg %>%
  mutate_if(is.numeric, round, digits=3)%>%
  mutate("correlation (sd)" = paste0(correlation," (",cor_sd,")"))%>%
  mutate("tradrsq (sd)" = paste0(tradrsq," (",rsq_sd,")"))%>%
  mutate("MAE (sd)" = paste0(MAE," (",mae_sd,")"))%>%
  mutate("RMSE (sd)" = paste0(RMSE," (",rmse_sd,")"))%>%
  select_if(is.character)
  
  ses_baseline_metric_avg_table%>%
    dplyr::select(all_of(avg_table_var_names))%>%
    kableExtra::kbl(caption = paste0("metrics for modalities averaged across sites in baseline")) %>%
    kableExtra::kable_classic(full_width = F, 
                             html_font = "Cambria")


```

## Followup model fitting

```{r}

### fit the enet model
### followup
ses_followup_recipe_list <- purrr::map(.x = processed_ses_followup_train_select,
                             ~recipe_prep(train_input=.x, features_input = dummy_features)) 

ses_pls_fit_followup <-purrr::map(.x=ses_followup_recipe_list,
                              ~pls_tune(recipe_input = .x,feature_input =dummy_features )) 

ses_pls_fit_followup_wf <- purrr::map(ses_pls_fit_followup,"pls_final_wf")


ses_pls_model_fit_followup <- pmap(list(ses_followup_recipe_list,
                                        ses_pls_fit_followup_wf,
                                        processed_ses_followup_test_select),~
                                                 model_final_fit(recipe_input = ..1, 
                                    wf_input = ..2,
                                    test_data = ..3)) 


ses_pls_pred_followup <- purrr::map(ses_pls_model_fit_followup,"model_predict")

ses_pls_model_fit_followup_train <- pmap(list(ses_followup_recipe_list,
                                        ses_pls_fit_followup_wf,
                                        processed_ses_followup_train_select),~
                                                 model_final_fit(recipe_input = ..1, 
                                    wf_input = ..2,
                                    test_data = ..3)) 

ses_pls_pred_followup_train <- purrr::map(ses_pls_model_fit_followup_train,"model_predict")


ses_followup_metric <- purrr::map2(.x=ses_pls_pred_followup,
     .y=processed_ses_followup_test,~metric_compute_site(data_input =.x ,
                                           site_input = .y)) %>%
                      do.call(rbind,.)%>% 
                      drop_na(site)

      ses_followup_metric%>% 
    kableExtra::kbl(caption = "metrics for all sites in followup") %>%
    kableExtra::kable_classic(full_width = F, 
                             html_font = "Cambria")


ses_followup_metric_avg <- average_metric_one_mod(metric_list =ses_followup_metric)

ses_followup_metric_avg_table <- ses_followup_metric_avg %>%
  mutate_if(is.numeric, round, digits=3)%>%
  mutate("correlation (sd)" = paste0(correlation," (",cor_sd,")"))%>%
  mutate("tradrsq (sd)" = paste0(tradrsq," (",rsq_sd,")"))%>%
  mutate("MAE (sd)" = paste0(MAE," (",mae_sd,")"))%>%
  mutate("RMSE (sd)" = paste0(RMSE," (",rmse_sd,")"))%>%
  select_if(is.character)
  
  ses_followup_metric_avg_table%>%
    dplyr::select(all_of(avg_table_var_names))%>%
    kableExtra::kbl(caption = paste0("metrics for modalities averaged across sites in followup")) %>%
    kableExtra::kable_classic(full_width = F, 
                             html_font = "Cambria")


```

## Plotting the trace of performance metric against the number of factors.

Baseline


```{r}

## get the model grid
ses_pls_grid_baseline  <- purrr::map(ses_pls_fit_baseline,"pls_grid")
ses_pls_param_baseline  <- purrr::map(ses_pls_fit_baseline,"best_pls_model")

factor_metric_plot <- function(grid_input, param_input){
  selected_comp <- param_input$num_comp
  
  comp_plot <-  grid_input %>% 
  collect_metrics() %>% 
  ggplot(aes(num_comp, mean, col = .metric)) +
  geom_point() +
  geom_line() +
  geom_vline(xintercept = selected_comp, size=1.5)+
  scale_x_continuous(n.breaks = 26) +
  labs(x = "Number of components",
       y = "Indicator",
       title = "Plot of RMSE vs number of components ",
       subtitle = paste0("Optimal number of components is ", selected_comp)) +
 facet_grid(.metric ~.) +
  theme_few() +
  theme(legend.position = "none")

  return(comp_plot)
}


comp_metric_plot_baseline <- purrr::map2(.x = ses_pls_grid_baseline,
                                         .y = ses_pls_param_baseline,
                                         ~factor_metric_plot(grid_input= .x ,
                                                             param_input = .y))

comp_metric_plot_baseline
```


Followup

```{r}


## get the model grid
ses_pls_grid_followup  <- purrr::map(ses_pls_fit_followup,"pls_grid")
ses_pls_param_followup  <- purrr::map(ses_pls_fit_followup,"best_pls_model")

comp_metric_plot_followup <- purrr::map2(.x = ses_pls_grid_followup,
                                         .y = ses_pls_param_followup,
                                         ~factor_metric_plot(grid_input= .x ,
                                                             param_input = .y))

comp_metric_plot_followup

```




# Feature importance for the whole data set


## Baseline

### Variable importance plot for pls models at baseline

Model across all sites.

```{r,fig.width=16,fig.height=12}
### combine the data set with the same train and test fold
data_all_site_baseline <- rbind(processed_ses_baseline_train_select[[1]],
                                processed_ses_baseline_test_select[[1]])
## retune the model
all_data_recipe_baseline <- recipe_prep_scale(train_input=data_all_site_baseline, 
                                        features_input = dummy_features)

all_data_fit_baseline <- pls_tune(recipe_input = all_data_recipe_baseline, 
                                        feature_input = dummy_features)

all_data_wf_baseline <- all_data_fit_baseline[["pls_final_wf"]]
## final fit the model
all_data_final_fit_baseline <- all_data_wf_baseline%>%
    parsnip::extract_spec_parsnip()%>%
    parsnip::fit(data = data_all_site_baseline, formula= as.formula("gfactor~."))
## get the coefficients
tidy_all_data_final_fit_baseline <- all_data_final_fit_baseline%>% 
  tidy()
### extract the number of components
all_data_param_baseline <-all_data_fit_baseline[["best_pls_model"]][["num_comp"]]
### extract the variance explained by each component

var_explained <- all_data_final_fit_baseline[["fit"]][["prop_expl_var"]][["X"]]

### plotting feature importance based on the model with all the data

comp_idx_vec <- c(1:all_data_param_baseline)

tidy_all_data_final_fit_baseline <- tidy_all_data_final_fit_baseline %>%
                                    rename(feature_names = term)
tidy_all_data_final_fit_baseline_with_name<- full_join(tidy_all_data_final_fit_baseline,
                                                       plotting_names, by = "feature_names")%>%
                                                filter(feature_names != "Y", # outcome variable col name
                                                       )%>% drop_na()
tidy_all_data_final_fit_baseline_list <- purrr::map(comp_idx_vec,
                                                    ~filter(tidy_all_data_final_fit_baseline_with_name,
                                                                         component == .)%>%
                                                          dplyr::select(all_of(c("plotting_name","value"))))

### get the variable order from the first component:

tidy_all_data_final_fit_baseline_reordered <- tidy_all_data_final_fit_baseline_list[[1]] %>% 
                                                                  arrange(value)

tidy_all_data_final_fit_baseline_reordered<- tidy_all_data_final_fit_baseline_reordered$plotting_name

## get the range for all of the plots

baseline_loading_table <- tidy_all_data_final_fit_baseline_list %>% do.call(rbind,.)



pls_vi_plot_with_label <- function(data_input=tidy_all_data_final_fit_baseline_list[[1]],
                                   var_input = var_explained[1],
                                   idx_input = comp_idx_vec[1],
                                   reorder_name = tidy_all_data_final_fit_baseline_reordered,
                                   range_input = baseline_loading_table){
  ### arrange the data from small to large
  data_input <- data_input %>%
                mutate(plotting_name = as.factor(plotting_name))%>%
                  mutate(plotting_name = factor(plotting_name,
                                                levels =reorder_name))
  
    range_value <- range(range_input$value)
  var_title_long <- paste0("component ", idx_input," var explained ",round(var_input,3)*100,"%")
 var_title_short <- paste0(round(var_input,3)*100,"%")
  var_title_medium <- paste0("comp ", idx_input," \n ",round(var_input,3)*100,"%")

  bar_plot <- ggplot(data_input, aes(x=.data[["value"]], y=plotting_name)) +
  geom_bar(stat="identity")+
  theme_classic() + 
    scale_x_continuous(limits = c(round(range_value[1],2)-0.05, round(range_value[2],2)+0.05),
                       breaks = c(round(range_value[1],2)-0.05,0, round(range_value[2],2)+0.05))+
    labs(title = var_title_medium)+
theme(
  axis.title.x = element_blank(),
  axis.text.x = element_text(size = 20,angle = 60,vjust = 0.5),
  axis.title.y = element_blank(),
  axis.text.y = element_text(size = 20),
  legend.text = element_blank(),
  plot.title = element_text(size=20))
  return(bar_plot)
}

comp_one_plot <- pls_vi_plot_with_label(data_input=tidy_all_data_final_fit_baseline_list[[1]],
                                   var_input = var_explained[1],
                                   idx_input = comp_idx_vec[1])



pls_vi_plot_no_label <- function(data_input=tidy_all_data_final_fit_baseline_list[[2]],
                                   var_input = var_explained[2],
                                   idx_input = comp_idx_vec[2],
                                 reorder_name = tidy_all_data_final_fit_baseline_reordered,
                                   range_input = baseline_loading_table){
  ### arrange the data from small to large
  data_input <- data_input %>%
                mutate(plotting_name = as.factor(plotting_name))%>%
                  mutate(plotting_name = factor(plotting_name,
                                                levels =reorder_name))
  
  range_value <- range(range_input$value)
  
  var_title_long <- paste0("component ", idx_input," var explained ",round(var_input,3)*100,"%")
  var_title_short <- paste0(round(var_input,3)*100,"%")
    var_title_medium <- paste0("comp ", idx_input," \n ",round(var_input,3)*100,"%")

  bar_plot <- ggplot(data_input, aes(x=.data[["value"]], y=plotting_name)) +
  geom_bar(stat="identity")+
    scale_x_continuous(limits = c(round(range_value[1],2)-0.05, round(range_value[2],2)+0.05),
                       breaks = c(round(range_value[1],2)-0.05,0, round(range_value[2],2)+0.05))+
  theme_classic() + 
    labs(title = var_title_medium)+
theme(
  axis.title.x = element_blank(),
  axis.text.x = element_text(size = 20,angle = 60,vjust = 0.5),
  axis.title.y = element_blank(),
  axis.text.y = element_blank(),
  legend.text = element_blank(),
  plot.title = element_text(size=20),
  axis.ticks = element_blank())
  return(bar_plot)
}


comp_other_plots <- purrr::pmap(list(tidy_all_data_final_fit_baseline_list[2:all_data_param_baseline],
                                     var_explained[2:all_data_param_baseline],
                                     comp_idx_vec[2:all_data_param_baseline
                                                  ]),~pls_vi_plot_no_label(data_input=..1,
                                   var_input = ..2,
                                   idx_input = ..3)) 
comp_other_plots_combined <- ggpubr::ggarrange(plotlist=comp_other_plots, nrow =1,ncol = length(var_explained)-1)

comp_plots_all <- gridExtra::grid.arrange(comp_one_plot,comp_other_plots_combined,nrow = 1, ncol = 2, widths = c(4.5, 4))

comp_plots_all
```




### Univariate correlations for baseline data

```{r,fig.height=15,fig.width=11}

corr_baseline_train <- processed_ses_baseline_train_select[[1]]
corr_baseline_test <- processed_ses_baseline_test_select[[1]]


corr_data_all <- rbind(corr_baseline_train,corr_baseline_test)
corr_features <- corr_data_all %>% dplyr::select(-"gfactor") %>%colnames()

 corr_all_features <- purrr::map(.x = corr_features,~cor(corr_data_all[[.x]],corr_data_all[["gfactor"]]
                                                         ,use = "pairwise.complete.obs"))%>% 
                                          do.call(rbind,.)%>% as.numeric()
 
 corr_all_features_cor_test <- purrr::map(.x = corr_features,
                            ~cor.test(corr_data_all[[.x]],corr_data_all[["gfactor"]],method="pearson"))
 
 corr_all_features_ci <- purrr::map(corr_all_features_cor_test,"conf.int")%>% 
                                          do.call(rbind,.)%>% tibble::as_tibble()%>%
                                          rename(low=V1,upp=V2)
    
 

 
  corr_output_tibble <- tibble(feature_names = corr_features,value = corr_all_features)
corr_output_tibble <- cbind(corr_output_tibble,corr_all_features_ci)
  
 corr_baseline_all_sites_names <- full_join(corr_output_tibble,plotting_names, by = "feature_names")%>% drop_na()

   corr_baseline_all_sites_names%>%
 mutate(plotting_name = fct_reorder(plotting_name, value,.fun = "max"))%>%
  ggplot(aes(x = plotting_name, y = value))+
    geom_bar(stat = "identity",fill="gray30",alpha = 0.7)+
    geom_errorbar( aes(x=plotting_name, 
                   ymin=low, 
                   ymax=upp),
               width=0.4, colour="black", alpha=0.9, linewidth=1.3)+
      coord_flip()+
    theme_classic() + 
  labs(y =paste0( "Correlation ") , x = "") +
    theme(axis.title.x= element_text(size = 20),
          axis.title.y= element_text(size = 20),
          axis.text.y = element_text(size = 20),
          axis.text.x = element_text(size = 20))
```

```{r}

corr_baseline_all_sites_names_for_all <-corr_baseline_all_sites_names%>%
     mutate(plotting_name = as.factor(plotting_name))%>%
                  mutate(plotting_name = factor(plotting_name,
                                                levels =tidy_all_data_final_fit_baseline_reordered))
  
corr_baseline_range <- range(baseline_loading_table$value)

corr_bar_plot_baseline <-   corr_baseline_all_sites_names_for_all%>%
 #mutate(plotting_name = fct_reorder(plotting_name, value,.fun = "max"))%>%
  ggplot(aes(x = plotting_name, y = value))+
    geom_bar(stat = "identity",fill="gray40",alpha = 0.7)+
    geom_errorbar( aes(x=plotting_name, 
                   ymin=low, 
                   ymax=upp),
               width=0.4, colour="black", alpha=0.9, linewidth=1.3)+
  scale_y_continuous(limits = c(round(corr_baseline_range[1],2)-0.05, round(corr_baseline_range[2],2)+0.05),
                       breaks = c(round(corr_baseline_range[1],2)-0.05,0, round(corr_baseline_range[2],2)+0.05))+
      coord_flip()+
    theme_classic() + 
    labs(title = "Univariate \ncorrelations")+
theme(
  axis.title.x = element_blank(),
  axis.text.x = element_text(size = 20,angle = 60,vjust = 0.5),
  axis.title.y = element_blank(),
  axis.text.y = element_blank(),
  legend.text = element_blank(),
  plot.title = element_text(size=20),
  axis.ticks = element_blank())


```


### Join correlation plot with univariate together

```{r,fig.width=16,fig.height=12}
vi_pls_plot_baseline_all <-gridExtra::grid.arrange(comp_plots_all,corr_bar_plot_baseline,nrow = 1, ncol = 2, widths = c(7, 1)) 

vi_pls_plot_baseline_all
```


## Followup

### Variable importance plot for pls models at baseline

Model across all sites.

```{r,fig.width=16,fig.height=12}

data_all_site_followup <- rbind(processed_ses_followup_train_select[[1]],
                                processed_ses_followup_test_select[[1]])

all_data_recipe_followup <- recipe_prep_scale(train_input=data_all_site_followup, 
                                        features_input = dummy_features)

## follow the function use a more parsimonious model 
## cut at the number of component that does not reduce 0.1% of the RMSE
all_data_fit_followup <- pls_tune(recipe_input = all_data_recipe_followup, 
                                        feature_input = dummy_features)

all_data_wf_followup <- all_data_fit_followup[["pls_final_wf"]]

all_data_final_fit_followup <- all_data_wf_followup%>%
    parsnip::extract_spec_parsnip()%>%
    parsnip::fit(data = data_all_site_followup, formula= as.formula("gfactor~."))

tidy_all_data_final_fit_followup <- all_data_final_fit_followup%>% 
  tidy()

all_data_param_followup <-all_data_fit_followup[["best_pls_model"]][["num_comp"]]
### extract the variance explained by each component

var_explained_followup <- all_data_final_fit_followup[["fit"]][["prop_expl_var"]][["X"]]

### plotting feature importance based on the model with all the data

comp_idx_vec_followup <- c(1:all_data_param_followup)

tidy_all_data_final_fit_followup <- tidy_all_data_final_fit_followup %>%
                                    rename(feature_names = term)
tidy_all_data_final_fit_followup_with_name<- full_join(tidy_all_data_final_fit_followup,
                                                       plotting_names, by = "feature_names")%>%
                                                filter(feature_names != "Y", # outcome variable col name
                                                       )
tidy_all_data_final_fit_followup_list <- purrr::map(comp_idx_vec_followup,
                                                    ~filter(tidy_all_data_final_fit_followup_with_name,
                                                                         component == .)%>%
                                                          dplyr::select(all_of(c("plotting_name","value"))))

### get the variable order from the first component:

tidy_all_data_final_fit_followup_reordered <- tidy_all_data_final_fit_followup_list[[1]] %>% 
                                                                  arrange(value)

tidy_all_data_final_fit_followup_reordered<- tidy_all_data_final_fit_followup_reordered$plotting_name

### get the range of the loadings for the plotting

followup_loading_table <- tidy_all_data_final_fit_followup_list %>% do.call(rbind,.)


comp_one_plot_followup <- pls_vi_plot_with_label(data_input=tidy_all_data_final_fit_followup_list[[1]],
                                   var_input = var_explained_followup[1],
                                   idx_input = comp_idx_vec_followup[1],
                                   reorder_name=tidy_all_data_final_fit_followup_reordered,
                                   range_input = followup_loading_table)


comp_other_plots_followup <- purrr::pmap(list(tidy_all_data_final_fit_followup_list[2:all_data_param_followup],
                                     var_explained_followup[2:all_data_param_followup],
                                     comp_idx_vec_followup[2:all_data_param_followup]
                                     ),~pls_vi_plot_no_label(data_input=..1,
                                   var_input = ..2,
                                   idx_input = ..3,
                                   reorder_name=tidy_all_data_final_fit_followup_reordered,
                                   range_input = followup_loading_table)) 
comp_other_plots_combined_followup <- ggpubr::ggarrange(plotlist=comp_other_plots_followup,
                                                        nrow =1,ncol = length(var_explained_followup)-1)




comp_plots_all_followup <- gridExtra::grid.arrange(comp_one_plot_followup,
                                                   comp_other_plots_combined_followup,
                                                   nrow = 1, ncol = 2, widths = c(4.5, 4))

comp_plots_all_followup
```



### plotting univariate correlation plots across sites at followup


The bar plot for correlations across all sites. Train and test fold are joined together.

```{r,fig.height=15,fig.width=11}
corr_data_all_followup <- rbind(processed_ses_followup_train[[1]],processed_ses_followup_test[[1]])

 corr_all_features_followup <- purrr::map(.x = dummy_features,~cor(corr_data_all_followup[[.x]],
                                                             corr_data_all_followup[["gfactor"]],use = "pairwise.complete.obs"))%>% 
                                          do.call(rbind,.)%>% as.numeric()
 
 corr_all_features_cor_test_followup <- purrr::map(.x = dummy_features,
                            ~cor.test(corr_data_all_followup[[.x]],
                                      corr_data_all_followup[["gfactor"]],method="pearson"))
 
 corr_all_features_ci_followup <- purrr::map(corr_all_features_cor_test_followup,"conf.int")%>% 
                                          do.call(rbind,.)%>% tibble::as_tibble()%>%
                                          rename(low=V1,upp=V2)
                                          
   
 
corr_output_tibble_followup <- tibble(feature_names = dummy_features,value = corr_all_features_followup)
corr_output_tibble_followup <- cbind(corr_output_tibble_followup,corr_all_features_ci_followup)
  
  corr_followup_all_sites_names <- full_join(corr_output_tibble_followup,
                                                      plotting_names, by = "feature_names")%>% drop_na()
  
  
   corr_followup_all_sites_names%>%
 mutate(plotting_name = fct_reorder(plotting_name, value,.fun = "max"))%>%
  ggplot(aes(x = plotting_name, y = value))+
    geom_bar(stat = "identity",fill="gray30",alpha = 0.7)+
    geom_errorbar( aes(x=plotting_name, 
                   ymin=low, 
                   ymax=upp),
               width=0.4, colour="black", alpha=0.9, linewidth=1.3)+
      coord_flip()+
    theme_classic() + 
  labs(y =paste0( "Correlation ") , x = "") +
    theme(axis.title.x= element_text(size = 20),
          axis.title.y= element_text(size = 20),
          axis.text.y = element_text(size = 15),
          axis.text.x = element_text(size = 20))
```


```{r}

corr_followup_all_sites_names_for_all <-corr_followup_all_sites_names%>%
     mutate(plotting_name = as.factor(plotting_name))%>%
                  mutate(plotting_name = factor(plotting_name,
                                                levels =tidy_all_data_final_fit_followup_reordered))
  
corr_followup_range <- range(followup_loading_table$value)
  
corr_bar_plot_followup <-   corr_followup_all_sites_names_for_all%>%
 #mutate(plotting_name = fct_reorder(plotting_name, value,.fun = "max"))%>%
  ggplot(aes(x = plotting_name, y = value))+
    geom_bar(stat = "identity",fill="gray40",alpha = 0.7)+
    geom_errorbar( aes(x=plotting_name, 
                   ymin=low, 
                   ymax=upp),
               width=0.4, colour="black", alpha=0.9, linewidth=1.3)+
  scale_y_continuous(limits = c(round(corr_followup_range[1],2)-0.05, round(corr_followup_range[2],2)+0.05),
                       breaks = c(round(corr_followup_range[1],2)-0.05,0, round(corr_followup_range[2],2)+0.05))+##use this because all the plots should have the same height
      coord_flip()+
    theme_classic() + 
    labs(title = "Univariate \ncorrelations")+
theme(
  axis.title.x = element_blank(),
  axis.text.x = element_text(size = 20,angle = 60,vjust = 0.5),
  axis.title.y = element_blank(),
  axis.text.y = element_blank(),
  legend.text = element_blank(),
  plot.title = element_text(size=20),
  axis.ticks = element_blank())


```



## join correlation plot with univariate together

```{r,fig.width=16,fig.height=12}

vi_pls_plot_followup_all <-gridExtra::grid.arrange(comp_plots_all_followup,
                                                   corr_bar_plot_followup,
                                                   nrow = 1, ncol = 2, widths = c(7, 1)) 
vi_pls_plot_followup_all
```
Combine baseline and followup together


```{r,fig.width=18,fig.height=25}


vi_pls_plot_baseline_label <- vi_pls_plot_baseline_all %>%
                      ggpubr::annotate_figure(top = ggpubr::text_grob("Baseline",size=20,face = "bold",hjust=3.2))


vi_pls_plot_followup_label <- vi_pls_plot_followup_all %>%
                    ggpubr::annotate_figure(top = ggpubr::text_grob("Followup",size=20,face = "bold",hjust=3))



vi_pls_plot_label <- ggpubr::ggarrange(vi_pls_plot_baseline_label,vi_pls_plot_followup_label,nrow = 2)

title_vi_pls_plot <- ggpubr::annotate_figure(vi_pls_plot_label,
                        top = ggpubr::text_grob("Feature importance of Partial Least Squares Regressions Predicting Cognitive \nAbilities from Social-Demographics, Lifestyles and Developments Variables",size=25, face = "bold")) 

title_vi_pls_plot



```
Change the order of the followup plots

```{r}


### get the variable order from the first component:
comp_plots_baseline_followup <- purrr::pmap(list(tidy_all_data_final_fit_followup_list[1:all_data_param_followup],
                                     var_explained_followup[1:all_data_param_followup],
                                     comp_idx_vec_followup[1:all_data_param_followup]
                                     ),~pls_vi_plot_no_label(data_input=..1,
                                   var_input = ..2,
                                   idx_input = ..3,
                                   reorder_name=tidy_all_data_final_fit_baseline_reordered)) 
comp_plots_combined_baseline_followup <- ggpubr::ggarrange(plotlist=comp_plots_baseline_followup,
                                                        nrow =1,ncol = length(var_explained_followup))

comp_plots_combined_baseline_followup

```



```{r}

corr_followup_baseline_all_sites_names_for_all <-corr_followup_all_sites_names%>%
     mutate(plotting_name = as.factor(plotting_name))%>%
                  mutate(plotting_name = factor(plotting_name,
                                                levels =tidy_all_data_final_fit_baseline_reordered))
  
  
corr_bar_plot_followup_baseline <-   corr_followup_baseline_all_sites_names_for_all%>%
 #mutate(plotting_name = fct_reorder(plotting_name, value,.fun = "max"))%>%
  ggplot(aes(x = plotting_name, y = value))+
    geom_bar(stat = "identity",fill="gray40",alpha = 0.7)+
    geom_errorbar( aes(x=plotting_name, 
                   ymin=low, 
                   ymax=upp),
               width=0.4, colour="black", alpha=0.9, linewidth=1.3)+
  scale_y_continuous(limits = c(-0.35, 0.45),
         breaks = c(-0.35,0, 0.45))+##use this because all the plots should have the same height
      coord_flip()+
    theme_classic() + 
    labs(title = "Univariate \ncorrelations")+
theme(
  axis.title.x = element_blank(),
  axis.text.x = element_text(size = 12,angle = 60,vjust = 0.5),
  axis.title.y = element_blank(),
  axis.text.y = element_blank(),
  legend.text = element_blank(),
  plot.title = element_text(size=15),
  axis.ticks = element_blank())


```


## join correlation plot with univariate together

```{r,fig.width=10,fig.height=9}

vi_pls_plot_followup_baseline_all <-gridExtra::grid.arrange(comp_plots_combined_baseline_followup,
                                                   corr_bar_plot_followup_baseline,
                                                   nrow = 1, ncol = 2, widths = c(8, 1.4)) 
vi_pls_plot_followup_baseline_all
```




```{r,fig.width=30,fig.height=20}


vi_pls_plot_baseline_no_label <- vi_pls_plot_baseline_all %>%
                            ggpubr::annotate_figure(top = ggpubr::text_grob("Baseline",size=20,hjust=2.5))


vi_pls_plot_followup_no_label <- vi_pls_plot_followup_baseline_all %>%
                            ggpubr::annotate_figure(top = ggpubr::text_grob("Followup",size=20,hjust=2.5))



vi_pls_plot_label <- ggpubr::ggarrange(vi_pls_plot_baseline_no_label,vi_pls_plot_followup_no_label,ncol = 2,widths = c(1.5,1))

title_vi_pls_plot <- ggpubr::annotate_figure(vi_pls_plot_label,
                        top = ggpubr::text_grob("Feature importance of Partial Least Squares Regressions \nPredicting Cognitive Abilities from Social-Demographics, \nLifestyles and Developments Variables",size=25, face = "bold")) 

title_vi_pls_plot



```









### save the output

```{r}

output_list <- list(baseline_train_pred = ses_pls_pred_baseline_train,
                    baseline_test_pred = ses_pls_pred_baseline,
                    baseline_train_data = processed_ses_baseline_train,
                    baseline_test_data = processed_ses_baseline_test,
                    followup_train_pred = ses_pls_pred_followup_train,
                    followup_test_pred = ses_pls_pred_followup,
                    followup_train_data =processed_ses_followup_train ,
                    followup_test_data = processed_ses_followup_test)

```



```{r,eval=FALSE}
saveRDS(output_list,paste0(scriptfold,'genetics_psychopathology_common_scan_all_scripts/ses_pls_pred_5.1', '.RData'))

```


save the metrics

```{r}
ses_baseline_metric_outout_table <- ses_baseline_metric_avg_table %>% mutate(event = "baseline")


ses_followup_metric_output_table<- ses_followup_metric_avg_table %>% mutate(event = "followup")

output_table <- bind_rows(ses_baseline_metric_outout_table,ses_followup_metric_output_table)%>%
                mutate(modality = "Social Demo Lifestyle Dev")
```


```{r}

saveRDS(output_table,paste0(scriptfold,'Common_psy_gene_brain_all/saved_outputs/performance_metrics/ses_performance_metric_5.1', '.RData'))

```