---
title: "Prepare data about medication for the commonality analysis"
author: "Yue Wang and Narun P"
date:  "`r format(Sys.time(), '%d %b, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: united
    number_sections: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load_data, echo=FALSE}
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.
```

## Note
Here we the ABCD release 5.1 data-set

## Loading libraries
The following libraries and default settings were used during the analysis:


```{r load_libraries}
options(scipen = 999)
#library("sva")
library(tidyverse)
library("tidymodels")
##parallel map

theme_set(theme_bw() + theme(panel.grid = element_blank()))
## parallel processing number of cores register
all_cores <- parallel::detectCores(logical = FALSE) - 10

doParallel::registerDoParallel(cores = all_cores)

```

# Data Preparation


We first loaded all of the relevant data files (not shown here as they refer to local directories):

```{r loading_data, echo=FALSE}
# from Qnap data windows
#datafolder = "//np-qnapa/Data/ABCD/ABCD4/ABCD4SQL/"
#scriptfold = "//np-qnapa/Data/Yue script/"
#NDAfold = "//np-qnapa/Data/ABCD/ABCD4/ABCDStudyNDA/"
#utilFold = "//np-qnapa/Data/ABCD/ABCD3/Analysis/utilFunc/"
#studyNDAFold = "//np-qnapa/Data/ABCD/ABCD4/ABCDStudyNDA/"
#outputfolder = "//np-qnapa/Data/ABCD/ABCD4/ABCD4_precessed_data/"


### linux directory
#datafolder = "/media/Data/ABCD/ABCD4/ABCD4SQL/"
#scriptfold = "/media/Data/Yue script/"
#NDAfold = "/media/Data/ABCD/ABCD4/ABCDStudyNDA/"
#utilFold = "/media/Data/ABCD/ABCD3/Analysis/utilFunc/"
#studyNDAFold = "/media/Data/ABCD/ABCD4/ABCDStudyNDA/"
#outputfolder = "/media/Data/ABCD/ABCD4/ABCD4_precessed_data/"
#featurefolder = "/media/Data/ABCD/ABCD4/Analysis/ManipulatedData/"

### apple directory

datafolder = "/Volumes/Data/ABCD/ABCD4/ABCD4SQL/"
scriptfold = "/Volumes/Data/Yue script/"
NDAfold = "/Volumes/Data/ABCD/ABCD4/ABCDStudyNDA/"
utilFold = "/Volumes/Data/ABCD/ABCD3/Analysis/utilFunc/"
studyNDAFold = "/Volumes/Data/ABCD/ABCD4/ABCDStudyNDA/"
outputfolder = "/Volumes/Data/ABCD/ABCD4/ABCD4_precessed_data/"
featurefolder = "/Volumes/Data/ABCD/ABCD4/Analysis/ManipulatedData/"
scriptfold_5.1  <- "/Volumes/sci-psy-narun/Nesi/Yue/"
### save the output
scriptfold = "/Volumes/Data/Yue script/"


source(paste0(scriptfold,"stacking_gfactor_modelling/r_functions_5.1.R"))


```

set up parallel

```{r}
# parallel for ubuntu
#doParallel::registerDoParallel(cores=30)  

### parallel library for mac
theme_set(theme_bw() + theme(panel.grid = element_blank()))
## parallel processing number of cores register
all_cores <- parallel::detectCores(logical = FALSE) - 5

doParallel::registerDoParallel(cores = all_cores)

## this one works for ubuntu but slow
#library(doFuture)
#registerDoFuture()
#plan(multicore(workers = 30))

### parallel for windows

#library(doFuture)
#registerDoFuture()
#plan(multisession(workers = 30))
```


## Loading tables for the medication information

```{r}
su_y_plus <- read.csv("/Volumes/sci-psy-narun/abcd-data-release-5.1/core/substance-use/su_y_plus.csv",na = c("", "NA", "999", "777"))

su_y_plus_med <- su_y_plus %>% select( "src_subject_id","eventname",contains("med")) %>% arrange(eventname) %>%            
                              purrr::discard(~all(is.na(.)))### remove columns that are all NAs
names(su_y_plus_med) <-toupper(colnames(su_y_plus_med))

med_features <- su_y_plus_med %>% select(- all_of(c("SRC_SUBJECT_ID","EVENTNAME"))) %>% colnames()

su_y_plus_med_baseline <- su_y_plus_med %>% filter(EVENTNAME == "baseline_year_1_arm_1")

su_y_plus_med_followup <- su_y_plus_med %>% filter(EVENTNAME == "2_year_follow_up_y_arm_1")

```



## Processing medication information

ATC/DDD Index 2024

ATC code

A ALIMENTARY TRACT AND METABOLISM
B BLOOD AND BLOOD FORMING ORGANS
C CARDIOVASCULAR SYSTEM
D DERMATOLOGICALS
G GENITO URINARY SYSTEM AND SEX HORMONES
H SYSTEMIC HORMONAL PREPARATIONS, EXCL. SEX HORMONES AND INSULINS
J ANTIINFECTIVES FOR SYSTEMIC USE
L ANTINEOPLASTIC AND IMMUNOMODULATING AGENTS
M MUSCULO-SKELETAL SYSTEM
N NERVOUS SYSTEM
P ANTIPARASITIC PRODUCTS, INSECTICIDES AND REPELLENTS
R RESPIRATORY SYSTEM
S SENSORY ORGANS
V VARIOUS



```{r}

med_processing_one_subj <- function(subj_input = subj_vec[12],
                                    filtered_data = data_input_filter){
  row_input <- filtered_data %>% filter(SRC_SUBJECT_ID == subj_input)
# get the numbers of the med information
    med_info_vec <- row_input %>% select(starts_with("PLS"))  %>% do.call(rbind,.)%>% 
                                as.vector()   %>% na.omit() %>% 
                                stringr::word(.,1) %>% as.numeric()
  ## get the information in the package
    med_class_vec <- med_info_vec %>% map(.,~rxnorm::get_atc(.,"first"))
med_class_vec_trial <- med_class_vec %>% do.call(rbind,.) %>% as.vector() %>% unique()
### create a output tibble
 output_tibble <- tibble(SRC_SUBJECT_ID =row_input$SRC_SUBJECT_ID,EVENTNAME= row_input$EVENTNAME,
                         is_ATC_A = ifelse("alimentary tract and metabolism" %in% med_class_vec_trial, 1,0), 
                         is_ATC_B = ifelse("blood and blood forming organs" %in% med_class_vec_trial, 1,0),
                         is_ATC_C = ifelse("cardiovascular system" %in% med_class_vec_trial, 1,0),
                         is_ATC_D = ifelse("dermatologicals" %in% med_class_vec_trial, 1,0),
                         is_ATC_G = ifelse("genito urinary system and sex hormones" %in% med_class_vec_trial, 1,0),
                  is_ATC_H = ifelse("systemic hormonal preparations, excl. sex hormones and insulins" %in% med_class_vec_trial, 1,0),
                         is_ATC_J = ifelse("antiinfectives for systemic use" %in% med_class_vec_trial, 1,0),
                         is_ATC_L = ifelse("antineoplastic and immunomodulating agents" %in% med_class_vec_trial, 1,0),
                         is_ATC_M = ifelse("musculo-skeletal system" %in% med_class_vec_trial, 1,0),
                         is_ATC_N = ifelse("nervous system" %in% med_class_vec_trial, 1,0),
                         is_ATC_P = ifelse("antiparasitic products, insecticides and repellents" %in% med_class_vec_trial, 1,0),
                         is_ATC_R = ifelse("respiratory system" %in% med_class_vec_trial, 1,0),
                         is_ATC_S = ifelse("sensory organs" %in% med_class_vec_trial, 1,0),
                         is_ATC_V = ifelse("various" %in% med_class_vec_trial, 1,0)) 
 return(output_tibble)
}




med_processing <- function(data_input = su_y_plus_med_baseline){
  ### drop the rows when this row has all NAs
  data_input_na_list <- med_features %>% map(.,~is.na(data_input[[.]])) %>% do.call(cbind,.) 
  data_input_na_sum_vec <- rowSums(data_input_na_list)
  data_input_na_sum <- tibble (na_sum = data_input_na_sum_vec,
                               SRC_SUBJECT_ID=  data_input$SRC_SUBJECT_ID) %>% 
                       filter(na_sum < 18)
  ### filter out the participants that have some sort of medication entry
 data_input_filter <- data_input %>% filter(SRC_SUBJECT_ID %in% data_input_na_sum$SRC_SUBJECT_ID)
  
 subj_vec <- data_input_filter$SRC_SUBJECT_ID
 #trial_subj_vec <- subj_vec[1:5]
 
# med_info_table_trial <- trial_subj_vec %>% map(.,~med_processing_one_subj(subj_input = ., filtered_data = data_input_filter )) %>% 
#                        do.call(rbind,.)
 
 med_info_table <- subj_vec %>% map(.,~med_processing_one_subj(subj_input = ., filtered_data = data_input_filter )) %>% 
                        do.call(rbind,.)
 
 
return(med_info_table)
}

```

 get the med information on baseline and followup
 
```{r,eval=FALSE}

baseline_med_info <- med_processing(data_input = su_y_plus_med_baseline)
## change the other observations in the data table to be 0 in dummy variables created for med information  
baseline_no_med_info<- su_y_plus_med_baseline %>% filter(! SRC_SUBJECT_ID %in% baseline_med_info$SRC_SUBJECT_ID) %>% 
                                                  select("SRC_SUBJECT_ID" , "EVENTNAME" ) %>% 
                 mutate(is_ATC_A = 0, 
                  is_ATC_B = 0,
                  is_ATC_C = 0,
                  is_ATC_D = 0,
                  is_ATC_G = 0,
                  is_ATC_H = 0,
                  is_ATC_J = 0,
                  is_ATC_L =0,
                  is_ATC_M = 0,
                  is_ATC_N = 0,
                  is_ATC_P = 0,
                  is_ATC_R = 0,
                  is_ATC_S = 0,
                  is_ATC_V = 0)

baseline_meds <- bind_rows(baseline_med_info,baseline_no_med_info)
  
followup_med_info <-  med_processing(data_input = su_y_plus_med_followup)



## change the other observations in the data table to be 0 in dummy variables created for med information  
followup_no_med_info<- su_y_plus_med_followup %>% filter(! SRC_SUBJECT_ID %in% followup_med_info$SRC_SUBJECT_ID) %>% 
                                                  select("SRC_SUBJECT_ID" , "EVENTNAME" ) %>% 
                 mutate(is_ATC_A = 0, 
                  is_ATC_B = 0,
                  is_ATC_C = 0,
                  is_ATC_D = 0,
                  is_ATC_G = 0,
                  is_ATC_H = 0,
                  is_ATC_J = 0,
                  is_ATC_L =0,
                  is_ATC_M = 0,
                  is_ATC_N = 0,
                  is_ATC_P = 0,
                  is_ATC_R = 0,
                  is_ATC_S = 0,
                  is_ATC_V = 0)
followup_meds <- bind_rows(followup_med_info,followup_no_med_info)

med_info_all <- bind_rows(baseline_meds,followup_meds)
```


```{r,eval=FALSE}


saveRDS(med_info_all,paste0(scriptfold,'Common_psy_gene_brain_all/saved_outputs/performance_metrics/med_info_all_5.1', '.RData'))


```

## Loading medication information for tables


```{r}
med_info_all <- readRDS(paste0(scriptfold,'Common_psy_gene_brain_all/saved_outputs/performance_metrics/med_info_all_5.1', '.RData'))

```


create medication information table

```{r,results='asis'}
med_info_baseline <- med_info_all %>% filter(EVENTNAME == "baseline_year_1_arm_1")

med_info_baseline_num <- med_info_baseline %>% select_if(is.numeric) %>% colSums()

med_sum_baseline <- tibble(Functionality = c("alimentary tract and metabolism",
"blood and blood forming organs",
"cardiovascular system",
"dermatologicals",
"genito urinary system and sex hormones",
"systemic hormonal preparations, excl. sex hormones and insulins",
"antiinfectives for systemic use", 
"antineoplastic and immunomodulating agents",
"musculo-skeletal system",
"nervous system",
"antiparasitic products, insecticides and repellents", 
"respiratory system",
"sensory organs","various"
),
Number = med_info_baseline_num)


med_sum_baseline%>%
  kableExtra::kbl(caption = paste0("Count of all the observations that took medication in baseline")) %>%
    kableExtra::kable_classic(full_width = F, 
                             html_font = "Cambria")



```


```{r,results='asis'}
med_info_followup <- med_info_all %>% filter(EVENTNAME == "2_year_follow_up_y_arm_1")

med_info_followup_num <- med_info_followup %>% select_if(is.numeric) %>% colSums()

med_sum_followup <- tibble(Functionality = c("alimentary tract and metabolism",
"blood and blood forming organs",
"cardiovascular system",
"dermatologicals",
"genito urinary system and sex hormones",
"systemic hormonal preparations, excl. sex hormones and insulins",
"antiinfectives for systemic use", 
"antineoplastic and immunomodulating agents",
"musculo-skeletal system",
"nervous system",
"antiparasitic products, insecticides and repellents", 
"respiratory system",
"sensory organs","various"
),
Number = med_info_followup_num)


med_sum_followup%>%
  kableExtra::kbl(caption = paste0("Count of all the observations that took medication in followup")) %>%
    kableExtra::kable_classic(full_width = F, 
                             html_font = "Cambria")


```


```{r,results='asis'}

med_sum_all <- tibble(Functionality = c("alimentary tract and metabolism",
"blood and blood forming organs",
"cardiovascular system",
"dermatologicals",
"genito urinary system and sex hormones",
"systemic hormonal preparations, excl. sex hormones and insulins",
"antiinfectives for systemic use", 
"antineoplastic and immunomodulating agents",
"musculo-skeletal system",
"nervous system",
"antiparasitic products, insecticides and repellents", 
"respiratory system",
"sensory organs","various"
),Baseline = med_info_baseline_num,
Followup = med_info_followup_num)


med_sum_all%>%
  kableExtra::kbl(caption = paste0("Count of all the observations that took medication")) %>%
    kableExtra::kable_classic(full_width = F, 
                             html_font = "Cambria")


```

