---
title: "Commonality analysis for Polygenic Scores, mental health, social demographic lifestyle developmental and sets of brain imaging features"
author: "Yue Wang and Narun P"
date:  "`r format(Sys.time(), '%d %b, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: united
    number_sections: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load_data, echo=FALSE}
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.
```

## Note
Here we the ABCD release 5.1 data-set


This file has all the linear mixed models with Polygenic Scores predictions as a variable. The reasons in doing this is that the number of observations in the Polygenic Scores data is substantially less than all the other variables. To be more specific: we have around 5,000 observations in Polygenic Scores data and 11,000 observations in mental health, social demographic lifestyle developmental and sets of brain imaging features.

# Setting up the environments

## Loading libraries
The following libraries and default settings were used during the analysis:


```{r load_libraries}
options(scipen = 999)
#library("sva")
library(tidyverse)
library("tidymodels")
##parallel map
library(partR2)
library(lme4)
library(yhat)
library(ggtext)
library(ggpubr)
library(cowplot)
library(partR2)
library(lme4)
library(yhat)
library("VennDiagram")
## library to tidy up the linear mixed models
library(sjPlot)

theme_set(theme_bw() + theme(panel.grid = element_blank()))
## parallel processing number of cores register
all_cores <- parallel::detectCores(logical = FALSE) - 5

doParallel::registerDoParallel(cores = all_cores)

```


## Setting up the path

We first loaded all of the relevant data files (not shown here as they refer to local directories):

```{r loading_data, echo=FALSE}
# from Qnap data windows
#datafolder = "//np-qnapa/Data/ABCD/ABCD4/ABCD4SQL/"
#scriptfold = "//np-qnapa/Data/Yue script/"
#NDAfold = "//np-qnapa/Data/ABCD/ABCD4/ABCDStudyNDA/"
#utilFold = "//np-qnapa/Data/ABCD/ABCD3/Analysis/utilFunc/"
#studyNDAFold = "//np-qnapa/Data/ABCD/ABCD4/ABCDStudyNDA/"
#outputfolder = "//np-qnapa/Data/ABCD/ABCD4/ABCD4_precessed_data/"

### unbuntu directories

#datafolder = "/media/Data/ABCD/ABCD4/ABCD4SQL/"
#scriptfold = "/media/Data/Yue script/"
#NDAfold = "/media/Data/ABCD/ABCD4/ABCDStudyNDA/"
#utilFold = "/media/Data/ABCD/ABCD3/Analysis/utilFunc/"
#studyNDAFold = "/media/Data/ABCD/ABCD4/ABCDStudyNDA/"
#outputfolder = "/media/Data/ABCD/ABCD4/ABCD4_precessed_data/"
#featurefolder = "/media/Data/ABCD/ABCD4/Analysis/ManipulatedData/"

### mac directories
datafolder = "/Volumes/Data/ABCD/ABCD4/ABCD4SQL/"
scriptfold = "/Volumes/Data/Yue script/"
NDAfold = "/Volumes/Data/ABCD/ABCD4/ABCDStudyNDA/"
utilFold = "/Volumes/Data/ABCD/ABCD3/Analysis/utilFunc/"
studyNDAFold = "/Volumes/Data/ABCD/ABCD4/ABCDStudyNDA/"
outputfolder = "/Volumes/Data/ABCD/ABCD4/ABCD4_precessed_data/"
featurefolder = "/Volumes/Data/ABCD/ABCD4/Analysis/ManipulatedData/"

```


```{r, cache=FALSE, include=FALSE}
### ubuntu and windows directories
#ABCD3Fold <- '/Volumes/wd/ABCD3/'
#ABCD3Fold <-"~/OneDrive - University of Otago/ABCD3/"
#ABCD4Fold <-"/media/Data/ABCD/ABCD4/"
#ABCD3Fold <-"/media/Data/ABCD/ABCD3/"
#scriptfold = "/media/Data/Yue script/"

# mac directories
ABCD4Fold <-"/Volumes/Data/ABCD/ABCD4/"
ABCD3Fold <-"/Volumes/Data/ABCD/ABCD3/"
scriptfold = "/Volumes/Data/Yue script/"

#ABCD4Fold <- "//np-qnapa/Data/ABCD/ABCD4/"
#setwd(paste0(ABCD3Fold, "Analysis/CognitionP"))
dataFold <- paste0(ABCD4Fold, "ABCD4SQL/")
utilFold <- paste0(ABCD3Fold, "Analysis/utilFunc/")

nesi_folder <- "/Volumes/sci-psy-narun/Nesi/Yue/"
datafolder_5.1 = '/Volumes/sci-psy-narun/abcd-data-release-5.1/core/'
outputfolder_5.1 = "/Volumes/sci-psy-narun/Yue/ABCD_5.1_data_precessing/processed_data/"
dicfolder_5.1 = '/Volumes/sci-psy-narun/abcd-data-release-5.1/dictionary/'
featurefolder = "/Volumes/sci-psy-narun/Yue/ABCD_5.1_data_precessing/processed_data/"
utilFold = "/Volumes/Data/ABCD/ABCD3/Analysis/utilFunc/"
imagingfolder_5.1  = paste0(datafolder_5.1, "imaging/")


gene_fold <- paste0(ABCD4Fold, "RicPGS/RicFIles20_Feb_2022/abcd-release-3.0_chrall_0.8-mac5-hg19-eur-qc-v9/")

```

```{r}
source(paste0(scriptfold,"stacking_gfactor_modelling/r_functions_5.1.R"))

```



# Data Preparation

## Loading demographics

```{r, cache = FALSE, warning=FALSE}


acspsw03 <- read.csv("/Volumes/sci-psy-narun/abcd-data-release-5.1/core/abcd-general/abcd_y_lt.csv", na = c("", "NA", "999", "777"))
names(acspsw03) <-toupper(colnames(acspsw03))
acspsw03_select <- acspsw03 %>% filter(EVENTNAME %in% c("baseline_year_1_arm_1","2_year_follow_up_y_arm_1" ))

### write NAs of the followup family ids to be the family IDs at baseline
acspsw03_baseline <- acspsw03_select %>% filter(EVENTNAME == "baseline_year_1_arm_1" )
acspsw03_followup <- acspsw03_select %>% filter(EVENTNAME == "2_year_follow_up_y_arm_1" )

fam_basline <- acspsw03_baseline %>% dplyr::select(all_of(c("REL_FAMILY_ID","SRC_SUBJECT_ID")))

acspsw03_followup <- acspsw03_followup %>%dplyr::select(-"REL_FAMILY_ID") %>% 
                                          left_join(fam_basline, by = "SRC_SUBJECT_ID")

acspsw03_select <- bind_rows(acspsw03_baseline,acspsw03_followup)

demo <- read.csv("/Volumes/sci-psy-narun/abcd-data-release-5.1/core/abcd-general/abcd_p_demo.csv", na = c("", "NA", "999", "777"))
names(demo) <-toupper(colnames(demo))
demo_select <- demo %>% filter(EVENTNAME %in% c("baseline_year_1_arm_1","2_year_follow_up_y_arm_1" ))



ACS <- left_join(demo_select,acspsw03_select,by =c("SRC_SUBJECT_ID","EVENTNAME"))
#knitr::kable(glimpse(ACS))

#race_ethnicity
#1 = White; 2 = Black; 3 = Hispanic; 4 = Asian; 5 = Other

# guardian-report relationship
# Relationship of the participant in his or her family
# 0 = single; 1 = sibling; 2 = twin; 3 = triplet
# ACS %>% count(REL_RELATIONSHIP)

ACSselected <- ACS %>% 
  dplyr::select(all_of(c("SRC_SUBJECT_ID", "EVENTNAME", "DEMO_SEX_V2", "INTERVIEW_AGE", "RACE_ETHNICITY", 
                              "REL_FAMILY_ID", "ACS_RAKED_PROPENSITY_SCORE","SITE_ID_L"))) %>%
  mutate(RACE_ETHNICITY = recode_factor(as.factor(RACE_ETHNICITY),
                `1` = "White", `2` = "Black", `3` = "Hispanic", `4` = "Asian", `5` = "Other",
                .default = "White")) %>%
  mutate(DEMO_SEX_V2 = as.factor(DEMO_SEX_V2)) %>%
  mutate(REL_FAMILY_ID = as.factor(REL_FAMILY_ID))

ACSselected %>%
 filter(EVENTNAME =="baseline_year_1_arm_1") %>%
 skimr::skim()

```





## load fitted gfactors from brain imaging and psychopathology

### load brain scan fitted results from stacking models

```{r}
rf_baseline <- readRDS(paste0(nesi_folder,"stacking_gfactor_modelling/collect_random_forest_results/random_forest_baseline_results.RDS"))

rf_followup <- readRDS(paste0(nesi_folder,"stacking_gfactor_modelling/collect_random_forest_results/random_forest_followup_results.RDS"))
```




### load the mental health predicted results

```{r}
psy_pred <- readRDS(paste0(scriptfold,"Common_psy_gene_brain_all/saved_outputs/psychopathology_pls_pred_no_asr_5.1.RData"))
psy_data_baseline <- psy_pred[["baseline_test_data"]] %>% do.call(rbind,.)
psy_pred_baseline <- psy_pred[["baseline_test_pred"]] %>% do.call(rbind,.) %>% 
                           mutate(SRC_SUBJECT_ID = psy_data_baseline$SRC_SUBJECT_ID) %>% 
                           select( "SRC_SUBJECT_ID","model_predict")
names(psy_pred_baseline) <- c("SRC_SUBJECT_ID", "Proxy Measure of Mental Health")

psy_data_followup <- psy_pred[["followup_test_data"]] %>% do.call(rbind,.)
psy_pred_followup <- psy_pred[["followup_test_pred"]] %>% do.call(rbind,.) %>% 
                           mutate(SRC_SUBJECT_ID = psy_data_followup$SRC_SUBJECT_ID) %>% 
                           select( "SRC_SUBJECT_ID","model_predict")
names(psy_pred_followup) <- c("SRC_SUBJECT_ID", "Proxy Measure of Mental Health")
```


### load the social demographic lifestyle developmental predicted results


```{r}
ses_pred <- readRDS(paste0(scriptfold,'genetics_psychopathology_common_scan_all_scripts/ses_pls_pred_5.1', '.RData'))


ses_data_baseline <- ses_pred[["baseline_test_data"]] %>% do.call(rbind,.)
ses_pred_baseline <- ses_pred[["baseline_test_pred"]] %>% do.call(rbind,.) %>% 
                           mutate(SRC_SUBJECT_ID = ses_data_baseline$SRC_SUBJECT_ID) %>% 
                           select( "SRC_SUBJECT_ID","model_predict")
names(ses_pred_baseline) <- c("SRC_SUBJECT_ID", "Proxy Measure of S-D LS Dev Adv")

ses_data_followup <- ses_pred[["followup_test_data"]] %>% do.call(rbind,.)
ses_pred_followup <- ses_pred[["followup_test_pred"]] %>% do.call(rbind,.) %>% 
                           mutate(SRC_SUBJECT_ID = ses_data_followup$SRC_SUBJECT_ID) %>% 
                           select( "SRC_SUBJECT_ID","model_predict")
names(ses_pred_followup) <- c("SRC_SUBJECT_ID", "Proxy Measure of S-D LS Dev Adv")
```

### Load in genetics related to cognition predicted results 


```{r}

genetics_cog <- readRDS(paste0(scriptfold,'genetics_psychopathology_common_scan_all_scripts/psychopathology_cog_gene_pred_residual_5.1', '.RData'))


poly_data_baseline <- genetics_cog[["baseline_test_data"]] %>% map(.,~select(.,SRC_SUBJECT_ID,gfactor)) %>% do.call(rbind,.)
poly_pred_baseline <- genetics_cog[["baseline_test_pred"]] %>% do.call(rbind,.) %>% 
                           mutate(SRC_SUBJECT_ID = poly_data_baseline$SRC_SUBJECT_ID) %>% 
                           select( "SRC_SUBJECT_ID","model_predict")
names(poly_pred_baseline) <- c("SRC_SUBJECT_ID", "Proxy Measure of Polygenic Scores")

poly_data_followup <- genetics_cog[["followup_test_data"]] %>% map(.,~select(.,SRC_SUBJECT_ID,gfactor)) %>% do.call(rbind,.)
poly_pred_followup <- genetics_cog[["followup_test_pred"]] %>% do.call(rbind,.) %>% 
                           mutate(SRC_SUBJECT_ID = poly_data_followup$SRC_SUBJECT_ID) %>% 
                           select( "SRC_SUBJECT_ID","model_predict")
names(poly_pred_followup) <- c("SRC_SUBJECT_ID", "Proxy Measure of Polygenic Scores")
```

### load the computed gfactor



```{r}

gfactor_list <- readRDS(paste0(scriptfold,'genetics_psychopathology_common_scan_all_scripts/gfactor_scale_seperate_5.1', '.RData'))


gfactor_baselie_test <- map(gfactor_list,"output_test_baseline") %>% do.call(rbind,.)

names(gfactor_baselie_test) <- c("SRC_SUBJECT_ID", "Cognitive Abilities")

gfactor_followup_test <- map(gfactor_list,"output_test_followup") %>% do.call(rbind,.)
names(gfactor_followup_test) <- c("SRC_SUBJECT_ID", "Cognitive Abilities")

```


## process loaded brain imaging, Polygenic Scores, mental health and social demographic lifestyle developmental model predictions

Be careful with what site you choose.

```{r}

rf_baseline_pred <- map(rf_baseline,"test_pred")
rf_baseline_data <- map(rf_baseline,"test_data") %>% do.call(rbind,.)
rf_baseline_pred_tibble <- map(rf_baseline_pred,"model_predict") %>% do.call(rbind,.) %>% 
                           mutate(SRC_SUBJECT_ID = rf_baseline_data$SRC_SUBJECT_ID) %>% 
                           select( "SRC_SUBJECT_ID","model_predict")

names(rf_baseline_pred_tibble) <- c("SRC_SUBJECT_ID","Proxy Measure of Neuroimaging")


rf_followup_pred <- map(rf_followup,"test_pred")
rf_followup_data <- map(rf_followup,"test_data")%>% do.call(rbind,.)
rf_followup_pred_tibble <- map(rf_followup_pred,"model_predict") %>% do.call(rbind,.) %>% 
                           mutate(SRC_SUBJECT_ID = rf_followup_data$SRC_SUBJECT_ID) %>% 
                           select( "SRC_SUBJECT_ID","model_predict")
names(rf_followup_pred_tibble) <- c("SRC_SUBJECT_ID","Proxy Measure of Neuroimaging")

```




```{r}
subj_info <- c("SRC_SUBJECT_ID","SITE_ID_L","EVENTNAME")

```


### Loading the output


```{r}

common_all_baseline <- readRDS(paste0(scriptfold,"Common_psy_gene_brain_all/saved_outputs/common_all_baseline_5.1.RData"))

common_baseline_select <- common_all_baseline %>%  select("SRC_SUBJECT_ID","mental_savg"   )
#names(common_baseline_select) <- c("SRC_SUBJECT_ID","Commonality of Mental Health, Neuroimaging, \n Polygenic scores, and Socio-Demo Lifestyle Dev")
names(common_baseline_select) <- c("SRC_SUBJECT_ID","Commonality of all Four Proxy Measures")
common_all_followup <- readRDS(paste0(scriptfold,"Common_psy_gene_brain_all/saved_outputs/common_all_followup_5.1.RData"))

common_followup_select <- common_all_followup %>%  select("SRC_SUBJECT_ID","mental_savg"   )
#names(common_followup_select) <- c("SRC_SUBJECT_ID","Commonality of Mental Health, Neuroimaging, \n Polygenic scores, and Socio-Demo Lifestyle Dev")
names(common_followup_select) <- c("SRC_SUBJECT_ID","Commonality of all Four Proxy Measures")

common_gene_baseline <- readRDS(paste0(scriptfold,"Common_psy_gene_brain_all/saved_outputs/common_gene_baseline_5.1.RData"))
common_gene_followup <- readRDS(paste0(scriptfold,"Common_psy_gene_brain_all/saved_outputs/common_gene_followup_5.1.RData"))

common_gene_baseline_select <- common_gene_baseline %>%  select("SRC_SUBJECT_ID","mental_savg"   )
names(common_gene_baseline_select) <- c("SRC_SUBJECT_ID","Commonality: Mental Health, Polygenic scores")
common_gene_followup_select <- common_gene_followup %>%  select("SRC_SUBJECT_ID","mental_savg"   )
names(common_gene_followup_select) <- c("SRC_SUBJECT_ID","Commonality: Mental Health, Polygenic scores")

common_brain_baseline <- readRDS(paste0(scriptfold,"Common_psy_gene_brain_all/saved_outputs/common_brain_baseline_5.1.RData"))

common_brain_followup <- readRDS(paste0(scriptfold,"Common_psy_gene_brain_all/saved_outputs/common_brain_followup_5.1.RData"))


common_brain_baseline_select <- common_brain_baseline %>%  select("SRC_SUBJECT_ID","mental_savg"   )
names(common_brain_baseline_select) <- c("SRC_SUBJECT_ID","Commonality: Mental Health, Neuroimaging")
common_brain_followup_select <- common_brain_followup %>%  select("SRC_SUBJECT_ID","mental_savg"   )
names(common_brain_followup_select) <- c("SRC_SUBJECT_ID","Commonality: Mental Health, Neuroimaging")

common_ses_baseline <- readRDS(paste0(scriptfold,"Common_psy_gene_brain_all/saved_outputs/common_ses_baseline_5.1.RData"))

common_ses_followup <- readRDS(paste0(scriptfold,"Common_psy_gene_brain_all/saved_outputs/common_ses_followup_5.1.RData"))

common_ses_baseline_select <- common_ses_baseline %>%  select("SRC_SUBJECT_ID","mental_savg"   )
names(common_ses_baseline_select) <- c("SRC_SUBJECT_ID","Commonality: Mental Health, S-D LS Dev Adv")

common_ses_followup_select <- common_ses_followup %>%  select("SRC_SUBJECT_ID","mental_savg"   )
names(common_ses_followup_select) <- c("SRC_SUBJECT_ID","Commonality: Mental Health, S-D LS Dev Adv")
```

```{r}

ACSselected_site <- ACSselected %>%  select(all_of(c("SRC_SUBJECT_ID","EVENTNAME" )))

ACSselected_site_baseline <- ACSselected_site %>% filter(EVENTNAME == "baseline_year_1_arm_1" ) %>% select(-"EVENTNAME")
ACSselected_site_followup <- ACSselected_site %>% filter(EVENTNAME == "2_year_follow_up_y_arm_1" ) %>% select(-"EVENTNAME")


plot_data_baseline <- plyr::join_all(list(ACSselected_site_baseline,gfactor_baselie_test,psy_pred_baseline,rf_baseline_pred_tibble,poly_pred_baseline,ses_pred_baseline,common_brain_baseline_select,common_gene_baseline_select,common_ses_baseline_select,common_baseline_select), by = "SRC_SUBJECT_ID",type = "full") %>% rename(ID = SRC_SUBJECT_ID)

plot_data_followup <- plyr::join_all(list(ACSselected_site_followup,gfactor_followup_test,psy_pred_followup,rf_followup_pred_tibble,poly_pred_followup,ses_pred_followup,common_brain_followup_select,common_gene_followup_select,common_ses_followup_select,common_followup_select), by = "SRC_SUBJECT_ID",type = "full")%>% rename(ID = SRC_SUBJECT_ID)

```


## Plotting the missingness

```{r,fig.width=10,fig.height=10}




baseline_na_plot <- naniar::vis_miss(plot_data_baseline)+ 
  ylab("Baseline Observations")+
  theme(axis.text.x = element_text(angle = 90))+
  theme(axis.text.x = element_text(size = 15),                      
                           axis.text.y = element_text(size = 15),                     
                           plot.title = element_text(size=15),
        axis.title.y = element_text(size=15),
    legend.text=element_text(size=15))+ 
   theme(legend.position="none")



followup_na_plot <- naniar::vis_miss(plot_data_followup)+
    ylab("Followup Observations")+
  theme(axis.text.x = element_text(size = 15),                      
                           axis.text.y = element_text(size = 15),                     
                           plot.title = element_text(size=15),
        axis.title.y = element_text(size=15),
    legend.text=element_text(size=15)) + 
   theme(legend.position="none")+
    theme(axis.text.x = element_text(angle = 90))



na_plot_all <-ggpubr::ggarrange(baseline_na_plot,followup_na_plot,
                  nrow = 1, ncol = 2,widths = c(1,1), heights = c(1,1) ) 

title_na_plot <- ggpubr::annotate_figure(na_plot_all,
                        top = ggpubr::text_grob("Number of Missing Observations in \n all Four Proxy Measurem and Commonality Analysis",size=25, face = "bold")) 

title_na_plot
```
