---
title: "Illustration of included data through data processing"
author: "Yue Wang and Narun P"
date:  "`r format(Sys.time(), '%d %b, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: united
    number_sections: true
    toc_depth: 3
---
```{r}
suppressPackageStartupMessages(library(DiagrammeR))
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.width = 3
  )

```

```{r load_data, echo=FALSE}
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.
```

# setting up environments

## Note
Here we the ABCD release 5.1 data-set

## Loading libraries
The following libraries and default settings were used during the analysis:


Changes: psychopathology to mental health



```{r load_libraries}
options(scipen = 999)
#library("sva")
library(tidyverse)
library(PRISMA2020)
library(PRISMA)
library(PRISMAstatement)

theme_set(theme_bw() + theme(panel.grid = element_blank()))
## parallel processing number of cores register
all_cores <- parallel::detectCores(logical = FALSE) - 5

doParallel::registerDoParallel(cores = all_cores)

```




## Setting up path

We first loaded all of the relevant data files (not shown here as they refer to local directories):

```{r loading_data, echo=FALSE}
# from Qnap data windows
#datafolder = "//np-qnapa/Data/ABCD/ABCD4/ABCD4SQL/"
#scriptfold = "//np-qnapa/Data/Yue script/"
#NDAfold = "//np-qnapa/Data/ABCD/ABCD4/ABCDStudyNDA/"
#utilFold = "//np-qnapa/Data/ABCD/ABCD3/Analysis/utilFunc/"
#studyNDAFold = "//np-qnapa/Data/ABCD/ABCD4/ABCDStudyNDA/"
#outputfolder = "//np-qnapa/Data/ABCD/ABCD4/ABCD4_precessed_data/"

### unbuntu directories

#datafolder = "/media/Data/ABCD/ABCD4/ABCD4SQL/"
#scriptfold = "/media/Data/Yue script/"
#NDAfold = "/media/Data/ABCD/ABCD4/ABCDStudyNDA/"
#utilFold = "/media/Data/ABCD/ABCD3/Analysis/utilFunc/"
#studyNDAFold = "/media/Data/ABCD/ABCD4/ABCDStudyNDA/"
#outputfolder = "/media/Data/ABCD/ABCD4/ABCD4_precessed_data/"
#featurefolder = "/media/Data/ABCD/ABCD4/Analysis/ManipulatedData/"

### mac directories
datafolder = "/Volumes/Data/ABCD/ABCD4/ABCD4SQL/"
scriptfold = "/Volumes/Data/Yue script/"
NDAfold = "/Volumes/Data/ABCD/ABCD4/ABCDStudyNDA/"
utilFold = "/Volumes/Data/ABCD/ABCD3/Analysis/utilFunc/"
studyNDAFold = "/Volumes/Data/ABCD/ABCD4/ABCDStudyNDA/"
outputfolder = "/Volumes/Data/ABCD/ABCD4/ABCD4_precessed_data/"
featurefolder = "/Volumes/Data/ABCD/ABCD4/Analysis/ManipulatedData/"
nesi_folder <- "/Volumes/sci-psy-narun/Nesi/Yue/"

source(paste0(scriptfold,"stacking_gfactor_modelling/r_functions_5.1.R"))


```

# Plots for Neuroimaging


```{r}
plotting_names <- readxl::read_excel(paste0(scriptfold,"Common_psy_gene_brain_all/CommonalityPlotingNames.xlsx"))


name_with_space <-  c("DTI","rsfMRI cortical FC","T2 summations","T1 summations","T2 normalised intensity","T2 gray matter \navg intensity","T2 white matter \navg intensity","T1 normalised \nintensity","T1 gray matter \navg intensity","T1 white matter \navg intensity","sulcal depth","cortical volumne","cortical area","cortical thickness","subcortical \nvolumne","T2 subcortical \navg intensity","T1 subcortical \navg intensity","rsfMRI temporal \nvariance","SST Incorrect Go \nvs Incorrect Stop","SST Incorrect Go \nvs Correct Go","SST Correct Stop \nvs Incorrect Stop","SST Any Stop \nvs Correct Go","SST Incorrect Stop \nvs Correct Go","SST Correct Stop \nvs Correct Go","SST Correct Go \nvs Fixation","MID Large Loss vs \nSmall Loss anticipation","MID Smal Loss vs \nNeutral anticipation","MID Large Loss vs \nNeutral anticipation","MID Large Reward vs \nSmall Reward anticipation","MID Small Reward vs \nNeutral anticipation","MID Large Reward vs \nNeutral anticipation","MID Postive vs Negative \nPunishment Feedback","MID Postive vs Negative \nReward Feedback","MID Loss vs \nNeutral anticipation","MID Reward vs \nNeutral anticipation","ENback Positive \nvs Neutral Face","ENback Negative \nvs Neutral Face","ENback Face \nvs Place","ENback Emotion \nvs Neutral Face","ENback 2back \nvs 0back","ENback emotion","ENback place","ENback 2back","ENback 0back","rsfMRI \nsubcortical-network FC") 

plotting_names <-plotting_names %>% mutate(plotting_name_space = name_with_space)
```


## Loading all data sets of the neuroimaging

```{r}

neu_data_all <- list.files(path = "/Volumes/sci-psy-narun/Yue/ABCD_5.1_data_precessing/processed_data/RDS", 
                       pattern = ".RDS$", full.names = TRUE)

neu_data_list <- map(neu_data_all, readRDS)

### get the names for neuro data

neu_names_all <- str_remove_all(neu_data_all,"^/Volumes/sci-psy-narun/Yue/ABCD_5.1_data_precessing/processed_data/RDS/") %>% 
                 str_remove_all(".RDS$")

names(neu_data_list) <- neu_names_all
acspsw03_select <- neu_data_list[["acspsw03_select"]] %>% filter(SITE_ID_L != "site22")

site_char <- unique(acspsw03_select[["SITE_ID_L"]]) %>% set_names()


```

## Task-fmri

```{r}

get_num_drop_na <- function(data_input = nback_data_list[[1]], 
                            event_input = "baseline_year_1_arm_1" ){
  output_table <- data_input %>% filter(EVENTNAME == event_input) %>%  drop_na() 
  output_num <- nrow(output_table)
  return(list(output_table = output_table, output_num=output_num))
}


get_num_iqr <- function(data_input = nback_baseline_nona_vis_table[[1]]){
  data_filtered <- data_input 
  features <- data_filtered %>% select(-all_of(c("SRC_SUBJECT_ID","SITE_ID_L","EVENTNAME" ))) %>% colnames()
  iqr_by_site <- site_char %>% map(.,~filter(data_filtered,SITE_ID_L == . ) %>%
                                     IQR_remove_vec(., x= features)) %>% do.call(rbind,.)
  return(list(output_tibble = iqr_by_site, output_number = nrow(iqr_by_site)))
}

```

```{r}
nback_contrasts <- c("X0back_ROI_","X2back_ROI_","X2backvs0back_ROI_","emotion_ROI_",
                                              "emotionvsneutface_ROI_","facevsplace_ROI_","negfacevsneutface_ROI_",
                                              "posfacevsneutface_ROI_","place_ROI_")



baseline_nback_table <- tibble(Original_name = nback_contrasts,
                              total = rep(11771,9),
                              QC = rep(7775,9))


followup_nback_table <- tibble(Original_name = nback_contrasts,
                              total = rep(8123,9),
                              QC = rep(6319,9))


nback_data_list <- neu_data_list[nback_contrasts]


nback_baseline_nona_vis <- map(nback_data_list, ~get_num_drop_na(data_input = ., 
                            event_input = "baseline_year_1_arm_1" ))

nback_baseline_nona_vis_num <- map(nback_baseline_nona_vis,"output_num")%>% do.call(rbind,.) %>% as.double()
nback_baseline_nona_vis_table <- map(nback_baseline_nona_vis,"output_table")


nback_baseline_iqr <- map(nback_baseline_nona_vis_table,~get_num_iqr(data_input = .))
nback_baseline_iqr_num <- map(nback_baseline_iqr,"output_number") %>% do.call(rbind,.) %>% as.double()


baseline_nback_table<- baseline_nback_table %>%  
                       mutate(na_vis = nback_baseline_nona_vis_num) %>% 
                       mutate(iqr = nback_baseline_iqr_num) %>% 
                       left_join(plotting_names, by =  "Original_name")

```



```{r}

flow_char_plotting <- function(data_input = baseline_nback_table, 
                               names_input = nback_contrasts[1]){
  row_select <- data_input %>%  filter(Original_name == names_input)
  flow_exclusions(
  incl_counts = c(row_select$total, row_select$QC, row_select$na_vis, row_select$iqr),
  total_label = row_select$plotting_name_space,
  incl_labels = c("Consented", "Completed Study", "BMI <= 30"),
  excl_labels = c("Declined Consent", "Failed to Complete", "BMI > 30")
)
}


```


```{r}

flow_exclusions_dot(
    incl_counts = c(972, 132, 77, 14),
    total_label = "Total Screened",
    incl_labels = c("Consented", "Completed Study", "BMI <= 30"),
    excl_labels = c("Declined Consent", "Failed to Complete", "BMI > 30")
    )


```