---
title: "Commonality analysis for mental health and stacked set of Brain imaging features models"
author: "Yue Wang and Narun P"
date:  "`r format(Sys.time(), '%d %b, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: united
    number_sections: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load_data, echo=FALSE}
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.
```

## Note
Here we the ABCD release 5.1 data-set

# Setting up the environment

## Loading libraries
The following libraries and default settings were used during the analysis:



```{r load_libraries}
options(scipen = 999)
#library("sva")
library(tidyverse)
library("tidymodels")
##parallel map
library(partR2)
library(lme4)
library(yhat)
library(ggtext)
library(ggpubr)
library(cowplot)
library(partR2)
library(lme4)
library(yhat)
library("VennDiagram")
## library to tidy up the linear mixed models
library(sjPlot)

theme_set(theme_bw() + theme(panel.grid = element_blank()))
## parallel processing number of cores register
all_cores <- parallel::detectCores(logical = FALSE) - 5

doParallel::registerDoParallel(cores = all_cores)

```



```{r, cache=FALSE, include=FALSE}
### ubuntu and windows directories
#ABCD3Fold <- '/Volumes/wd/ABCD3/'
#ABCD3Fold <-"~/OneDrive - University of Otago/ABCD3/"
#ABCD4Fold <-"/media/Data/ABCD/ABCD4/"
#ABCD3Fold <-"/media/Data/ABCD/ABCD3/"
#scriptfold = "/media/Data/Yue script/"

# mac directories
ABCD4Fold <-"/Volumes/Data/ABCD/ABCD4/"
ABCD3Fold <-"/Volumes/Data/ABCD/ABCD3/"
scriptfold = "/Volumes/Data/Yue script/"

#ABCD4Fold <- "//np-qnapa/Data/ABCD/ABCD4/"
#setwd(paste0(ABCD3Fold, "Analysis/CognitionP"))
dataFold <- paste0(ABCD4Fold, "ABCD4SQL/")
utilFold <- paste0(ABCD3Fold, "Analysis/utilFunc/")


datafolder_5.1 = '/Volumes/sci-psy-narun/abcd-data-release-5.1/core/'
outputfolder_5.1 = "/Volumes/sci-psy-narun/Yue/ABCD_5.1_data_precessing/processed_data/"
dicfolder_5.1 = '/Volumes/sci-psy-narun/abcd-data-release-5.1/dictionary/'
featurefolder = "/Volumes/sci-psy-narun/Yue/ABCD_5.1_data_precessing/processed_data/"
utilFold = "/Volumes/Data/ABCD/ABCD3/Analysis/utilFunc/"
imagingfolder_5.1  = paste0(datafolder_5.1, "imaging/")
nesi_folder <- "/Volumes/sci-psy-narun/Nesi/Yue/"


gene_fold <- paste0(ABCD4Fold, "RicPGS/RicFIles20_Feb_2022/abcd-release-3.0_chrall_0.8-mac5-hg19-eur-qc-v9/")

```

```{r}
source(paste0(scriptfold,"stacking_gfactor_modelling/r_functions_5.1.R"))

```


## Setting up the library path

We first loaded all of the relevant data files (not shown here as they refer to local directories):

```{r loading_data, echo=FALSE}
# from Qnap data windows
#datafolder = "//np-qnapa/Data/ABCD/ABCD4/ABCD4SQL/"
#scriptfold = "//np-qnapa/Data/Yue script/"
#NDAfold = "//np-qnapa/Data/ABCD/ABCD4/ABCDStudyNDA/"
#utilFold = "//np-qnapa/Data/ABCD/ABCD3/Analysis/utilFunc/"
#studyNDAFold = "//np-qnapa/Data/ABCD/ABCD4/ABCDStudyNDA/"
#outputfolder = "//np-qnapa/Data/ABCD/ABCD4/ABCD4_precessed_data/"

### unbuntu directories

#datafolder = "/media/Data/ABCD/ABCD4/ABCD4SQL/"
#scriptfold = "/media/Data/Yue script/"
#NDAfold = "/media/Data/ABCD/ABCD4/ABCDStudyNDA/"
#utilFold = "/media/Data/ABCD/ABCD3/Analysis/utilFunc/"
#studyNDAFold = "/media/Data/ABCD/ABCD4/ABCDStudyNDA/"
#outputfolder = "/media/Data/ABCD/ABCD4/ABCD4_precessed_data/"
#featurefolder = "/media/Data/ABCD/ABCD4/Analysis/ManipulatedData/"

### mac directories
datafolder = "/Volumes/Data/ABCD/ABCD4/ABCD4SQL/"
scriptfold = "/Volumes/Data/Yue script/"
NDAfold = "/Volumes/Data/ABCD/ABCD4/ABCDStudyNDA/"
utilFold = "/Volumes/Data/ABCD/ABCD3/Analysis/utilFunc/"
studyNDAFold = "/Volumes/Data/ABCD/ABCD4/ABCDStudyNDA/"
outputfolder = "/Volumes/Data/ABCD/ABCD4/ABCD4_precessed_data/"
featurefolder = "/Volumes/Data/ABCD/ABCD4/Analysis/ManipulatedData/"

```

## load fitted gfactors from brain scan and psychopathology

### load brain scan fitted results from stacking models

```{r}
rf_baseline <- readRDS(paste0(nesi_folder,"stacking_gfactor_modelling/collect_random_forest_results/random_forest_baseline_results.RDS"))

rf_followup <- readRDS(paste0(nesi_folder,"stacking_gfactor_modelling/collect_random_forest_results/random_forest_followup_results.RDS"))
```




### load the mental health predicted results

```{r}
psy_pred <- readRDS(paste0(scriptfold,"Common_psy_gene_brain_all/saved_outputs/psychopathology_pls_pred_no_asr_5.1.RData"))

```

### load the computed gfactor

```{r}

gfactor_list <- readRDS(paste0(scriptfold,'genetics_psychopathology_common_scan_all_scripts/gfactor_scale_seperate_5.1', '.RData'))

```

Be careful with what site you choose.

```{r}

rf_baseline_pred <- map(rf_baseline,"test_pred")
rf_baseline_pred_tibble <- map(rf_baseline_pred,"model_predict")
rf_baseline_table <- map(rf_baseline,"test_data")

rf_followup_pred <- map(rf_followup,"test_pred")
rf_followup_pred_tibble <- map(rf_followup_pred,"model_predict")
rf_followup_table <- map(rf_followup,"test_data")

```


```{r}

gfactor_baselie_test <- map(gfactor_list,"output_test_baseline")
gfactor_followup_test <- map(gfactor_list,"output_test_followup")


```

```{r}
subj_info <- c("SRC_SUBJECT_ID","SITE_ID_L","EVENTNAME")

```



load in family index data


```{r, cache = FALSE, warning=FALSE}
acspsw03 <- read.csv("/Volumes/sci-psy-narun/abcd-data-release-5.1/core/abcd-general/abcd_y_lt.csv", na = c("", "NA", "999", "777"))
names(acspsw03) <-toupper(colnames(acspsw03))
acspsw03_select <- acspsw03 %>% filter(EVENTNAME %in% c("baseline_year_1_arm_1","2_year_follow_up_y_arm_1" ))

### write NAs of the followup family ids to be the family IDs at baseline
acspsw03_baseline <- acspsw03_select %>% filter(EVENTNAME == "baseline_year_1_arm_1" )
acspsw03_followup <- acspsw03_select %>% filter(EVENTNAME == "2_year_follow_up_y_arm_1" )

fam_basline <- acspsw03_baseline %>% dplyr::select(all_of(c("REL_FAMILY_ID","SRC_SUBJECT_ID")))

acspsw03_followup <- acspsw03_followup %>%dplyr::select(-"REL_FAMILY_ID") %>% 
                                          left_join(fam_basline, by = "SRC_SUBJECT_ID")

acspsw03_select <- bind_rows(acspsw03_baseline,acspsw03_followup)

demo <- read.csv("/Volumes/sci-psy-narun/abcd-data-release-5.1/core/abcd-general/abcd_p_demo.csv", na = c("", "NA", "999", "777"))
names(demo) <-toupper(colnames(demo))
demo_select <- demo %>% filter(EVENTNAME %in% c("baseline_year_1_arm_1","2_year_follow_up_y_arm_1" ))




ACS <- left_join(demo_select,acspsw03_select,by =c("SRC_SUBJECT_ID","EVENTNAME"))

# guardian-report relationship
# Relationship of the participant in his or her family
# 0 = single; 1 = sibling; 2 = twin; 3 = triplet
# ACS %>% count(REL_RELATIONSHIP)

ACSselected <- ACS %>% 
  dplyr::select("SRC_SUBJECT_ID", "EVENTNAME", "DEMO_SEX_V2", "INTERVIEW_AGE", "RACE_ETHNICITY", 
                              "REL_FAMILY_ID", "ACS_RAKED_PROPENSITY_SCORE","SITE_ID_L") %>%
  mutate(REL_FAMILY_ID = as.factor(REL_FAMILY_ID))

ACSselected %>%
 filter(EVENTNAME =="baseline_year_1_arm_1") %>%
 skimr::skim()
ACSselected_baseline <- ACSselected %>%
                        filter(EVENTNAME =="baseline_year_1_arm_1")%>%
                        select(SRC_SUBJECT_ID,REL_FAMILY_ID)

ACSselected_followup <- ACSselected %>%
                        filter(EVENTNAME =="1_year_follow_up_y_arm_1")%>%
                        select(SRC_SUBJECT_ID,REL_FAMILY_ID)
```


```{r}
pred_processing <- function(baseline_pred, followup_pred, baseline_table, followup_table,pred_name){
  names_vec <- c(subj_info,pred_name)
  
  baseline_subj_info <- baseline_table %>% select(all_of(subj_info))
  baseline_pred_vec <- baseline_pred %>% select(model_predict)
  baseline_output <- bind_cols(baseline_subj_info,baseline_pred_vec)
  names(baseline_output) <- names_vec
  
  followup_subj_info <- followup_table %>% select(all_of(subj_info))
  followup_pred_vec <- followup_pred %>% select(model_predict)
  followup_output <- bind_cols(followup_subj_info,followup_pred_vec)
  names(followup_output) <- names_vec

  output_all <- bind_rows(baseline_output,followup_output)
  return(list(baseline_output = baseline_output,
              followup_output = followup_output))
}




```



```{r}
processed_rf_results <- pmap(list(rf_baseline_pred_tibble,rf_baseline_table,
                                  rf_followup_pred_tibble,rf_followup_table),
                             ~pred_processing(baseline_pred=..1,
                                              followup_pred=..3, 
                                              baseline_table=..2, 
                                              followup_table=..4,
                                              pred_name="random_forest_stacking"))


processed_psy_results <- pmap(list(psy_pred[["baseline_test_pred"]],
                                   psy_pred[["baseline_test_data"]],
                                  psy_pred[["followup_test_pred"]],
                                  psy_pred[["followup_test_data"]]),
                             ~pred_processing(baseline_pred=..1,
                                              followup_pred=..3, 
                                              baseline_table=..2, 
                                              followup_table=..4,
                                              pred_name="psychopathology_pls"))
```


```{r}

site_char <- names(processed_psy_results)

```


## Join all the data 


```{r}

join_data_all <- function(site_input){
  ### join the data and drop NA
  rf_baseline_tibble <- processed_rf_results[[site_input]][["baseline_output"]]
  rf_followup_tibble <- processed_rf_results[[site_input]][["followup_output"]]
  psy_baseline_tibble <- processed_psy_results[[site_input]][["baseline_output"]]
  psy_followup_tibble <- processed_psy_results[[site_input]][["followup_output"]]
  

  baseline_rf_psy <- full_join(rf_baseline_tibble,
                                      psy_baseline_tibble, 
                                 by =subj_info)
  followup_rf_psy <- full_join(rf_followup_tibble,
                                      psy_followup_tibble, 
                                 by =subj_info)

  gfactor_baseline <- gfactor_baselie_test[[site_input]]
  gfactor_followup <- gfactor_followup_test[[site_input]]
  

baseline_all <- plyr::join_all(list(baseline_rf_psy,
                                      ACSselected_baseline,gfactor_baseline), 
                                 by ="SRC_SUBJECT_ID", type = 'full')%>%
                                 drop_na()
  followup_all <- plyr::join_all(list(followup_rf_psy,
                                      ACSselected_baseline,gfactor_followup), 
                                 by ="SRC_SUBJECT_ID", type = 'full')%>%
                                 drop_na()
 output_all <- bind_rows(baseline_all,followup_all)
  
  return(list(baseline = baseline_all,
              followup=followup_all,
              all = output_all))
  
}


```


```{r}

gfactor_all <- map(.x = site_char,~join_data_all(site_input = .x))

names(gfactor_all) <- site_char

gfactor_all_baseline <- map(gfactor_all,"baseline")
gfactor_all_followup <- map(gfactor_all,"followup")
gfactor_all_baseline_followup <- map(gfactor_all,"all")

```

### get the residual of of the predicted values with age, sex and med information


ATC/DDD Index 2024

ATC code

A ALIMENTARY TRACT AND METABOLISM
B BLOOD AND BLOOD FORMING ORGANS
C CARDIOVASCULAR SYSTEM
D DERMATOLOGICALS
G GENITO URINARY SYSTEM AND SEX HORMONES
H SYSTEMIC HORMONAL PREPARATIONS, EXCL. SEX HORMONES AND INSULINS
J ANTIINFECTIVES FOR SYSTEMIC USE
L ANTINEOPLASTIC AND IMMUNOMODULATING AGENTS
M MUSCULO-SKELETAL SYSTEM
N NERVOUS SYSTEM
P ANTIPARASITIC PRODUCTS, INSECTICIDES AND REPELLENTS
R RESPIRATORY SYSTEM
S SENSORY ORGANS
V VARIOUS

```{r}
abcd_med_5.1 <-  readRDS(paste0(scriptfold,'Common_psy_gene_brain_all/saved_outputs/performance_metrics/med_info_all_5.1', '.RData'))                  

 reg_resp <- c("random_forest_stacking","psychopathology_pls") %>% set_names()
 subj_info_vec <- c(subj_info,"INTERVIEW_AGE")
 med_regress_features <- c("is_ATC_A","is_ATC_B","is_ATC_C","is_ATC_D","is_ATC_G","is_ATC_H","is_ATC_J","is_ATC_L",
                           "is_ATC_M","is_ATC_N","is_ATC_P","is_ATC_R","is_ATC_S","is_ATC_V","DEMO_SEX_V2","INTERVIEW_AGE")
 ### follow up sex information are all NAs (biological sense of sex)
 sex_info_table <- ACSselected %>% filter(EVENTNAME =="baseline_year_1_arm_1") %>% select(all_of(subj_info),"DEMO_SEX_V2") %>% 
                   select(-EVENTNAME)
site_char <- site_char %>% set_names()


 residual_one_resp <- function(resp_input= "random_forest_stacking", 
                               data_input=data_med){
   formula_input <- paste0(resp_input," ~ ",paste0(med_regress_features, collapse = " + "))
   residual_output <- residuals(lm(as.formula(formula_input),data = data_input))
   return(residual_output)
 }
 
get_residuals_med_sex_age <- function(data_list = gfactor_all_followup,
                                      event_input =  "2_year_follow_up_y_arm_1"){
  data_input <- data_list %>% do.call(bind_rows,.)
 
  
  age_info <- ACSselected %>% 
              filter(EVENTNAME == event_input) %>%
              select(all_of(subj_info_vec))
  
  data_fam <- plyr::join_all(list(data_input,age_info),type = "left", by = subj_info) %>% drop_na()
  data_all <- left_join(data_fam, sex_info_table, by = c( "SRC_SUBJECT_ID","SITE_ID_L"))
  ### remove columns that are all 0s
  data_med <- left_join(data_all, abcd_med_5.1, by = c( "SRC_SUBJECT_ID","EVENTNAME")) %>% drop_na()
  
  data_med_info <- data_med %>% select(starts_with("is_ATC_"))%>% select_if(colSums(.) != 0)
  
  data_med_processed <- data_med %>% select(-starts_with("is_ATC_")) %>% bind_cols(data_med_info) %>%
  mutate(across(starts_with("is_ATC_"),factor))
  ### get all the residuals
  
  residual_list <- reg_resp %>% map(.,~residual_one_resp(resp_input = ., data_input=data_med))
  data_output <- tibble(random_forest_stacking = residual_list[["random_forest_stacking"]]%>% as.numeric(),
                        psychopathology_pls= residual_list[["psychopathology_pls"]] %>% as.numeric())
data_input_select <- data_med %>% select(all_of(c("SRC_SUBJECT_ID","SITE_ID_L","EVENTNAME","REL_FAMILY_ID","gfactor"))) 
 output_table  <-  bind_cols(data_input_select,data_output) 

output_list <- map(site_char,~filter(output_table,SITE_ID_L == .))
return(output_list)
}

```

Compute the residuals


```{r}

gfactor_all_baseline_residual <-  get_residuals_med_sex_age(data_list = gfactor_all_baseline,
                                      event_input =  "baseline_year_1_arm_1")

gfactor_all_followup_residual <-  get_residuals_med_sex_age(data_list = gfactor_all_followup,
                                      event_input =  "2_year_follow_up_y_arm_1")
```


## Mean centering within family and within site


This script only perform the commonality analyses for the models with genetics. In genetics there are only around 5000 participants, which is much smaller than all the other models. 

Some explaination of the variables:

brain_savg: the average of brain prediction results within each site.

brain_cws: brain predictions centered within each site.

mental_savg: the average of mental health predictions results within each site.

mental_cws: mental health predictions centered within each site.
 
 
```{r}

center_by_site <- function(data_input){
  output_data <- data_input %>% 
    mutate(brain_savg = mean(random_forest_stacking))%>% 
    mutate(brain_cws = random_forest_stacking-brain_savg)%>% 
   mutate(mental_savg = mean(psychopathology_pls))%>%
    mutate(mental_cws = psychopathology_pls - mental_savg)

return(output_data)
  }


centered_all_baseline <- map(gfactor_all_baseline_residual,~center_by_site(data_input = .))
centered_all_followup <- map(gfactor_all_followup_residual,~center_by_site(data_input = .))

```

## Scale the overall data by each variable

```{r}
gfactor_all_pred_centered_site_baseline <- centered_all_baseline%>%
                                           do.call(rbind,.)
gfactor_all_pred_centered_site_followup <- centered_all_followup%>%
                                           do.call(rbind,.)


features_not_scale <- c(subj_info, "REL_FAMILY_ID","gfactor")

features_scale <- gfactor_all_pred_centered_site_baseline %>% select(-all_of(features_not_scale))%>% colnames()
## recipe to scale the features
recipe_scale <- function(train_input=gfactor_all_pred_centered_site_baseline){
  norm_recipe <- recipe( as.formula("gfactor~."), data = train_input) %>%
    update_role(all_of(features_scale), new_role = "predictor")%>%
    update_role("gfactor", new_role = "outcome" )%>%
    # normalize numeric predictors and outcome
    step_normalize(all_numeric_predictors())
  return(norm_recipe)
}


all_baseline_recipe <- 

data_all_baseline <-recipe_scale(train_input=gfactor_all_pred_centered_site_baseline) %>%
                    prep() %>%
                    juice()


data_all_followup <-recipe_scale(train_input=gfactor_all_pred_centered_site_followup) %>%
                    prep() %>%
                    juice()



```


```{r,eval=FALSE}

saveRDS(data_all_baseline,paste0(scriptfold,"Common_psy_gene_brain_all/saved_outputs/common_brain_baseline_5.1.RData"))

saveRDS(data_all_followup,paste0(scriptfold,"Common_psy_gene_brain_all/saved_outputs/common_brain_followup_5.1.RData"))



```

# Commonality analysis for the models with stacked brain and mental health

We use linear mixed models in the following analyses. There is a following nested structure: participants are nested within family and family are nested within sites. The random intercepts of site seems do not have any effects on the model and it may cause singularity problems. So it is removed from the analysis.


```{r}
common_analysis_psy_brain <- function(data_input=data_all_baseline){

    print("brain_psy_model") 
  brain_psy_model <- lmer(gfactor~mental_savg+mental_cws+brain_savg+brain_cws+(1|SITE_ID_L:REL_FAMILY_ID),data = data_input)
  rsq_brain_psy <- performance::r2(brain_psy_model)

  print("brain_model")
  brain_model <- lmer(gfactor ~ brain_savg+ brain_cws+(1|SITE_ID_L:REL_FAMILY_ID),data = data_input)
  rsq_brain <- performance::r2(brain_model)
  

  print("psy_model")
  psy_model <- lmer(gfactor ~  mental_savg+mental_cws+(1|SITE_ID_L:REL_FAMILY_ID),data = data_input)
  rsq_psy <- performance::r2(psy_model)
  
  unique_brain_margin <- rsq_brain_psy$R2_marginal-rsq_psy$R2_marginal
  
  unique_psy_margin <- rsq_brain_psy$R2_marginal-rsq_brain$R2_marginal
    
  common_brain_psy_margin <- rsq_brain$R2_marginal+rsq_psy$R2_marginal-rsq_brain_psy$R2_marginal


  unique_brain_conditional <- rsq_brain_psy$R2_conditional-rsq_psy$R2_conditional
  
  unique_psy_conditional <- rsq_brain_psy$R2_conditional-rsq_brain$R2_conditional
    
  common_brain_psy_conditional <- rsq_psy$R2_conditional+rsq_brain$R2_conditional-rsq_brain_psy$R2_conditional
  
  output_common_tibble <- tibble(variable_effects = c("unique_brain",
                                              "unique_psy",
                                              "common_brain_psy"),
                          marginal_rsq = c(unique_brain_margin,
                                              unique_psy_margin,
                                              common_brain_psy_margin),
                          conditional_rsq = c(unique_brain_conditional,
                                              unique_psy_conditional,
                                              common_brain_psy_conditional))
  output_rsq_tibble <- tibble(model_names<- c("brain",
                                              "psy",
                                              "brain_psy"),
                          marginal_rsq = c(rsq_brain$R2_marginal,
                                              rsq_psy$R2_marginal,
                                              rsq_brain_psy$R2_marginal),
                          conditional_rsq = c(rsq_brain$R2_conditional,
                                              rsq_psy$R2_conditional,
                                              rsq_brain_psy$R2_conditional))
  
  return(list(output_common_tibble=output_common_tibble,
              output_rsq_tibble=output_rsq_tibble,
              brain_psy_model=brain_psy_model,
             brain_model=brain_model,
             psy_model=psy_model))
  }


```


```{r}
common_analysis_psy_brain_all <-common_analysis_psy_brain(data_input=data_all_baseline)

common_analysis_psy_brain_all_followup <-common_analysis_psy_brain(data_input=data_all_followup)

```

```{r}

tab_model(common_analysis_psy_brain_all$brain_psy_model,
          common_analysis_psy_brain_all$psy_model,
          common_analysis_psy_brain_all$brain_model)


tab_model(common_analysis_psy_brain_all_followup$brain_psy_model,
          common_analysis_psy_brain_all_followup$psy_model,
          common_analysis_psy_brain_all_followup$brain_model)

```

```{r}
baseline_no_gene_vec <- common_analysis_psy_brain_all[[1]]$marginal_rsq

baseline_no_gene_vec_corrected_percent <- baseline_no_gene_vec/sum(baseline_no_gene_vec)*100 
baseline_no_gene_vec_corrected_percent <- round(baseline_no_gene_vec_corrected_percent,2)
print(baseline_no_gene_vec_corrected_percent)

baseline_no_gene_vec_corrected_raw <- baseline_no_gene_vec*100 
baseline_no_gene_vec_corrected_raw <- round(baseline_no_gene_vec_corrected_raw,2)
print(baseline_no_gene_vec_corrected_raw)


baseline_table <- common_analysis_psy_brain_all[[1]] %>%
                  mutate(corrected_percent = baseline_no_gene_vec_corrected_percent)%>%
                  mutate(corrected_raw = baseline_no_gene_vec_corrected_raw)

baseline_table%>% 
    kableExtra::kbl(caption = "Commonality analysis in baseline") %>%
    kableExtra::kable_classic(full_width = F, 
                             html_font = "Cambria")
common_analysis_psy_brain_all[[2]]%>% 
    kableExtra::kbl(caption = "R^2 metrics for all models in baseline") %>%
    kableExtra::kable_classic(full_width = F, 
                             html_font = "Cambria")



no_gene_vec_followup <- common_analysis_psy_brain_all_followup[[1]]$marginal_rsq


no_brain_vec_corrected_followup_percent <- no_gene_vec_followup/sum(no_gene_vec_followup)*100 
no_brain_vec_corrected_followup_percent <- round(no_brain_vec_corrected_followup_percent,2)
print(no_brain_vec_corrected_followup_percent)

no_brain_vec_corrected_followup_raw <- no_gene_vec_followup*100 
no_brain_vec_corrected_followup_raw <- round(no_brain_vec_corrected_followup_raw,2)
print(no_brain_vec_corrected_followup_raw)


followup_table <- common_analysis_psy_brain_all_followup[[1]] %>%
                  mutate(corrected_percent = no_brain_vec_corrected_followup_percent)%>%
                  mutate(corrected_raw = no_brain_vec_corrected_followup_raw)

followup_table%>% 
    kableExtra::kbl(caption = "Commonality analysis in followup") %>%
    kableExtra::kable_classic(full_width = F, 
                             html_font = "Cambria")
common_analysis_psy_brain_all_followup[[2]]%>% 
    kableExtra::kbl(caption = "R^2 metrics for all models in followup") %>%
    kableExtra::kable_classic(full_width = F, 
                             html_font = "Cambria")

```


### venn diagram for baseline


Raw r-square score with label

The "draw.pairwise.venn_invert" function is changed from the source code of the package;

The original code is in this page:

https://github.com/cran/VennDiagram/blob/master/R/draw.quad.venn.R


```{r,fig.width=5,fig.height=2}
venn_plot_baseline_no_gene_raw <- draw.pairwise.venn_invert(area1 =baseline_no_gene_vec_corrected_raw[1]+baseline_no_gene_vec_corrected_raw[3],
  area2 = baseline_no_gene_vec_corrected_raw[2]+baseline_no_gene_vec_corrected_raw[3],
  cross.area  = baseline_no_gene_vec_corrected_raw[3],
  category = c("Mental Health", "Neuroimaging"),
  fill = c("#D55E00", "#009E73"),
  lty = "dashed",
  cat.col = c("#D55E00", "#009E73"),
  filename = NULL,
  cex = 2, ## label font size
  cat.cex = 2,### caption font size
  lwd = 2,
  cat.fontface = "bold",
   cat.dist = c(0.05, -0.45), # Modified
  cat.pos = c(-5, 1),# Modified
  scaled = FALSE,inverted=TRUE
  #print.mode="percent"
  )

grid.newpage()

#grid::grid.draw(venn_plot_baseline_no_gene_raw)
#invisible(dev.off())
```

### venn diagram for followup





```{r,fig.width=5,fig.height=2}
venn_plot_no_gene_followup_raw <- draw.pairwise.venn_invert(area1 =no_brain_vec_corrected_followup_raw[1]+no_brain_vec_corrected_followup_raw[3],
  area2 = no_brain_vec_corrected_followup_raw[2]+no_brain_vec_corrected_followup_raw[3],
  cross.area  = no_brain_vec_corrected_followup_raw[3],
  category = c("Mental Health","Neuroimaging"),
  fill = c("#D55E00","#009E73"),
  lty = "dashed",
  cat.col = c("#D55E00","#009E73"),
  filename = NULL,
  cex = 2, ## label font size
  cat.cex = 2,### caption font size
  lwd = 2,
  cat.fontface = "bold",
  cat.dist = c(0.05, -0.45), # Modified
  cat.pos = c(-5, 1),# Modified
  scaled = FALSE,inverted=TRUE
  #print.mode="percent"
  )

grid.newpage()

#grid::grid.draw(venn_plot_no_gene_followup_raw)
#invisible(dev.off())

```