---
title: "ABCD 5.1 data Nback cleaning"
author: "Yue Wang and Narun P"
date:  "`r format(Sys.time(), '%d %b, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: united
    number_sections: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load_data, echo=FALSE}
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.
```

Due to the changes in the data names in the new ABCD 5.1 release, this file selects variables and changes the variable names with ABCD 5.1 data release. The previous work is based on the ABCD 4.0 data. So, the ABCD 4.0 data tables are loaded and processed first to get the variable names then mapped to the ABCD 5.1 data tables.




# Processing ABCD 5.1 data tables

## Loading libraries

starting with setting up library and script/data folders

```{r}
rm(list=ls())

library(tidyverse)

```

```{r loading_data, echo=FALSE}
### the directories for loading up data and files

datafolder_5.1 = '/Volumes/sci-psy-narun/abcd-data-release-5.1/core/imaging/'
outputfolder_5.1 = "/Volumes/sci-psy-narun/Yue/ABCD_5.1_data_precessing/processed_data/"
dicfolder_5.1 = '/Volumes/sci-psy-narun/abcd-data-release-5.1/dictionary/'
featurefolder = "/Volumes/sci-psy-narun/Yue/ABCD_5.1_data_precessing/processed_data/"
utilFold = "/Volumes/Data/ABCD/ABCD3/Analysis/utilFunc/"
```


## load all of the files

The purpose of this code is:

1. change the variable names and select the needed variables.

2. perform the quality control to all the imaging variables.

```{r load_data2}
###loading brain scan data (Nback only)
mri_y_dti_fa_fs_at <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_dti_fa_fs_at.csv"))) 
mri_y_dti_fa_fs_aseg <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_dti_fa_fs_aseg.csv"))) 
mri_y_dti_fa_fs_gm_dsk <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_dti_fa_fs_gm_dsk.csv"))) 
mri_y_dti_fa_fs_gwc_dsk <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_dti_fa_fs_gwc_dsk.csv"))) 
mri_y_dti_fa_fs_wm_dsk <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_dti_fa_fs_wm_dsk.csv"))) 


mri_y_dti_ld_fs_at <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_dti_ld_fs_at.csv"))) 
mri_y_dti_ld_fs_aseg <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_dti_ld_fs_aseg.csv"))) 
mri_y_dti_ld_fs_gm_dsk <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_dti_ld_fs_gm_dsk.csv"))) 



mri_y_dti_md_fs_at <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_dti_md_fs_at.csv"))) 
mri_y_dti_md_fs_aseg <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_dti_md_fs_aseg.csv"))) 
mri_y_dti_md_fs_gm_dsk <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_dti_md_fs_gm_dsk.csv"))) 
mri_y_dti_md_fs_wm_dsk <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_dti_md_fs_wm_dsk.csv"))) 



mri_y_dti_td_fs_at <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_dti_td_fs_at.csv"))) 
mri_y_dti_td_fs_aseg <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_dti_td_fs_aseg.csv"))) 
mri_y_dti_td_fs_gm_dsk <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_dti_td_fs_gm_dsk.csv"))) 
mri_y_dti_td_fs_wm_dsk <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_dti_td_fs_wm_dsk.csv"))) 


mri_y_dti_vol_fs_at <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_dti_vol_fs_at.csv"))) 

### Note that we have not removed NA before Enet tuning to keep the most number of participants

dic_tibble <-tibble::as_tibble(read.csv(paste0(dicfolder_5.1, "2024-01-23_03_20_38.681784-ABCD_Data_Dictionary.csv"))) 
qc_tibble <-tibble::as_tibble(read.csv(paste0(datafolder_5.1, "mri_y_qc_incl.csv"))) 
```


## processing Nback data

 Deal with the new names in ABCD 5.1


```{r}
### join all the smri data tables and select the needed features 
### also join this tibble with quality control variables
dti_all <- plyr::join_all(list(mri_y_dti_fa_fs_at,mri_y_dti_fa_fs_aseg,mri_y_dti_fa_fs_gm_dsk,
                                 mri_y_dti_fa_fs_gwc_dsk,mri_y_dti_fa_fs_wm_dsk,mri_y_dti_ld_fs_at, 
                                 mri_y_dti_ld_fs_aseg,mri_y_dti_ld_fs_gm_dsk,mri_y_dti_md_fs_at,
                                 mri_y_dti_md_fs_aseg,mri_y_dti_md_fs_gm_dsk,mri_y_dti_md_fs_wm_dsk,
                                 mri_y_dti_td_fs_at, mri_y_dti_td_fs_aseg,mri_y_dti_td_fs_gm_dsk,
                                 mri_y_dti_td_fs_wm_dsk, mri_y_dti_vol_fs_at), by=c("src_subject_id","eventname" ), type='full')

dti_select <- dti_all %>%
                 select(all_of(c("src_subject_id","eventname")),starts_with("dmdtifp1_"))

 
## quality control for smri data
new_subj_info <- c("src_subject_id","eventname")  

qc_features <- qc_tibble %>% select(-all_of(new_subj_info))%>% colnames()

### qc for dst data
dti_qced <- full_join(dti_select, qc_tibble, by = new_subj_info)%>%
             filter(imgincl_dmri_include==1)%>%
             select(-all_of(qc_features))
             
qc_tibble %>% count(eventname,imgincl_dmri_include)

upper_dti_names <- colnames(dti_qced) %>% toupper() 


names(dti_qced) <- upper_dti_names

```



### Load dict and change names and select only the FA of the 23 tracks 

```{r}

#load the readable names based on dictionary
DTIVarNames<-tbl_df(readxl::read_excel(paste0(utilFold,"DTIVariableToImport.xlsx"))) %>% 
  select(UpperOriginal, Readable23HaglerTracks) %>% drop_na(Readable23HaglerTracks)

#change the names
DTI.DictNames <- dti_qced
for (DTIVar in 1:nrow(DTIVarNames)) {
  DTI.DictNames <- DTI.DictNames %>%
  rename(!!DTIVarNames$Readable23HaglerTracks[DTIVar] := !!DTIVarNames$UpperOriginal[DTIVar])
}

# only focus on the 23 tracks in Haggler 2009 Atlas
DTI.23Tracks <- DTI.DictNames %>% select(-starts_with("DMDTIFP"))

```

### write on file
```{r}

write.csv(DTI.23Tracks, paste0(featurefolder,"DTI_FA23Tracks.csv"))
```

