---
title: "Cleaning and quality control structureal-mri T2 data table"
author: "Yue Wang and Narun P"
date:  "`r format(Sys.time(), '%d %b, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: united
    number_sections: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Due to the changes in the data names in the new ABCD 5.1 release, this file selects variables and changes the variable names with ABCD 5.1 data release. The previous work is based on the ABCD 4.0 data. So, the ABCD 4.0 data tables are loaded and processed first to get the variable names then mapped to the ABCD 5.1 data tables.




# Processing ABCD 5.1 data tables

## Loading libraries

starting with setting up library and script/data folders

```{r}
rm(list=ls())

library(tidyverse)

```

```{r loading_data, echo=FALSE}
### the directories for loading up data and files

datafolder_5.1 = '/Volumes/sci-psy-narun/abcd-data-release-5.1/core/imaging/'
outputfolder_5.1 = "/Volumes/sci-psy-narun/Yue/ABCD_5.1_data_precessing/processed_data/"
dicfolder_5.1 = '/Volumes/sci-psy-narun/abcd-data-release-5.1/dictionary/'
featurefolder = "/Volumes/sci-psy-narun/Yue/ABCD_5.1_data_precessing/processed_data/"
utilFold = "/Volumes/Data/ABCD/ABCD3/Analysis/utilFunc/"
```


## load all of the files

The purpose of this code is:

1. change the variable names and select the needed variables.

2. perform the quality control to all the imaging variables.

```{r}

mri_y_smr_t2_aseg <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_smr_t2_aseg.csv"))) 


mri_y_smr_t2_contr_dsk <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_smr_t2_contr_dsk.csv"))) 
mri_y_smr_t2_contr_dst <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_smr_t2_contr_dst.csv"))) 
mri_y_smr_t2_contr_fzy <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_smr_t2_contr_fzy.csv"))) 


mri_y_smr_t2_gray_dsk <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_smr_t2_gray_dsk.csv"))) 
mri_y_smr_t2_gray_dst <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_smr_t2_gray_dst.csv"))) 
mri_y_smr_t2_gray_fzy <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_smr_t2_gray_fzy.csv"))) 


mri_y_smr_t2_white_dsk <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_smr_t2_white_dsk.csv"))) 
mri_y_smr_t2_white_dst <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_smr_t2_white_dst.csv"))) 
mri_y_smr_t2_white_fzy <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_smr_t2_white_fzy.csv"))) 

dic_tibble <-tibble::as_tibble(read.csv(paste0(dicfolder_5.1, "2024-01-23_03_20_38.681784-ABCD_Data_Dictionary.csv"))) 
qc_tibble <-tibble::as_tibble(read.csv(paste0(datafolder_5.1, "mri_y_qc_incl.csv"))) 
```

## Deal with the new names in ABCD 5.1


```{r}
### join all the smri data tables and select the needed features 
### also join this tibble with quality control variables
smri_all <- plyr::join_all(list(mri_y_smr_t2_aseg,mri_y_smr_t2_contr_dsk,
                                mri_y_smr_t2_contr_dst,mri_y_smr_t2_contr_fzy,mri_y_smr_t2_gray_dsk,
                                mri_y_smr_t2_gray_dst,mri_y_smr_t2_gray_fzy,mri_y_smr_t2_white_dsk,
                                mri_y_smr_t2_white_dst,mri_y_smr_t2_white_fzy), by=c("src_subject_id","eventname" ), type='full')
 
## quality control for smri data
new_subj_info <- c("src_subject_id","eventname")  

qc_features <- qc_tibble %>% select(-all_of(new_subj_info))%>% colnames()


smri_qced <- full_join(smri_all, qc_tibble, by = new_subj_info)%>%
             filter(imgincl_t2w_include==1)%>%
             select(-all_of(qc_features))
             
qc_tibble %>% count(eventname,imgincl_t2w_include)

upper_feature_names <- colnames(smri_qced) %>% toupper() 


names(smri_qced) <- upper_feature_names
```

Load dict and change names

```{r}

#load the readable names based on dictionary
sMRIVarNames<-tibble::as_tibble(readxl::read_excel(paste0(utilFold,"sMRIVariableToImport.xlsx"))) %>% 
  select(original, CondReadableFilteredGgseg) %>% drop_na(CondReadableFilteredGgseg)
###Destrieux ROI 


### change names of sulcal depth


roi_names <- sMRIVarNames$CondReadableFilteredGgseg[174:321]%>%
            str_remove_all("Dest_Area_")

## average T2 intensity white matter 

avg_T2_white_roi_names <- paste0("Avg_T2_White_", roi_names)

avg_T2_white_tibble <- smri_qced %>%
                       select(all_of(paste0("MRISDP_", seq(from =1058, to = 1205, by = 1))))


names(avg_T2_white_tibble) <- avg_T2_white_roi_names


## average T2 intensity gray matter 

avg_T2_gray_roi_names <- paste0("Avg_T2_Gray_", roi_names)

avg_T2_Gray_tibble <- smri_qced %>%
                       select(all_of(paste0("MRISDP_", seq(from =1209, to = 1356, by = 1))))


names(avg_T2_Gray_tibble) <- avg_T2_gray_roi_names


### normalised T2 intensity 


nom_T2_roi_names <- paste0("Normalised_T2_", roi_names)

nom_T2_tibble <- smri_qced %>%
                       select(all_of(paste0("MRISDP_", seq(from =1360, to = 1507, by = 1))))


names(nom_T2_tibble) <- nom_T2_roi_names

### change names of ASEG rois

aseg_roi_names <- sMRIVarNames$CondReadableFilteredGgseg[1:19]%>%
            str_remove_all("ASEG_")

aseg_original_names <- sMRIVarNames$original[1:19]%>% 
                       str_remove_all("SMRI_VOL_SCS_")
                      
avg_T2_aseg_roi_names <- paste0("Avg_T2_ASEG_", aseg_roi_names)

aseg_original_roi_names <- paste0("SMRI_T2W_SCS_", aseg_original_names)

T2sMRIVarNames <- tibble(original = aseg_original_roi_names,CondReadableFilteredGgseg= avg_T2_aseg_roi_names)


### Average intensity of the normalized T2-weighted image 



avg_T2_aseg_tibble <- smri_qced %>%
                       select(starts_with("SMRI_T2W_SCS_"))


#change the names
avg_T2_aseg_tibble_newnames <- avg_T2_aseg_tibble
for (sMRIVar in 1:nrow(T2sMRIVarNames)) {
  avg_T2_aseg_tibble_newnames <- avg_T2_aseg_tibble_newnames %>%
  rename(!!T2sMRIVarNames$CondReadableFilteredGgseg[sMRIVar] := !!T2sMRIVarNames$original[sMRIVar])  
}


avg_T2_aseg_tibble_newnames <- avg_T2_aseg_tibble_newnames%>%
                               select(starts_with("Avg_T2_ASEG_"))
  
  
  

whole_Cerebellum_Cortex <- smri_qced%>% select(all_of(c("SMRI_T2W_SCS_CRBCORTEXLH","SMRI_T2W_SCS_CRBCORTEXRH")))%>%
                  rowSums()


### get the mean of individual rois
mean_vars <- c("MRISDP_1208","MRISDP_1359","MRISDP_1510")

mean_T2 <- smri_qced %>% select(all_of(mean_vars))%>%
              rename(mean_T2_Avg_white=MRISDP_1208)%>%
              rename(mean_T2_Avg_gray=MRISDP_1359)%>%
              rename(mean_T2_normalised=MRISDP_1510)%>%
            mutate(Avg_T2_whole_Cerebellum_Cortex_ASEG =whole_Cerebellum_Cortex)




id_tibble <- smri_qced %>% select(all_of(c("SRC_SUBJECT_ID","EVENTNAME")))

sMRI.T2Weighted <-do.call("cbind", list(avg_T2_white_tibble, 
                                        avg_T2_Gray_tibble, 
                                        nom_T2_tibble,
                                        avg_T2_aseg_tibble_newnames,
                                        mean_T2,
                                        id_tibble))


sMRI.T2Weighted <-sMRI.T2Weighted %>%
  mutate_at(vars(starts_with("Avg_T2_White_")),  ~ . / mean_T2_Avg_white)%>%
  mutate_at(vars(starts_with("Avg_T2_Gray_")),  ~ . / mean_T2_Avg_gray) %>%
  mutate_at(vars(starts_with("Normalised_T2_")),  ~ . / mean_T2_normalised)%>%
  mutate_at(vars(starts_with("Avg_T2_ASEG_")),  ~ . /Avg_T2_whole_Cerebellum_Cortex_ASEG)   


```



for real analysis, perhaps start with "ASEG_" and "Dest_Thick_" 


write on file
```{r}
write.csv(sMRI.T2Weighted, paste0(featurefolder,"sMRI.T2Weighted.csv"))

```







