---
title: "ABCD 5.1 data MID cleaning"
author: "Yue Wang and Narun P"
date:  "`r format(Sys.time(), '%d %b, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: united
    number_sections: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load_data, echo=FALSE}
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.
```

Due to the changes in the data names in the new ABCD 5.1 release, this file selects variables and changes the variable names with ABCD 5.1 data release. The previous work is based on the ABCD 4.0 data. So, the ABCD 4.0 data tables are loaded and processed first to get the variable names then mapped to the ABCD 5.1 data tables.




# Processing ABCD 5.1 data tables

## Loading libraries

starting with setting up library and script/data folders

```{r}
rm(list=ls())

library(tidyverse)

```

```{r loading_data, echo=FALSE}
### the directories for loading up data and files

datafolder_5.1 = '/Volumes/sci-psy-narun/abcd-data-release-5.1/core/imaging/'
outputfolder_5.1 = "/Volumes/sci-psy-narun/Yue/ABCD_5.1_data_precessing/processed_data/"
dicfolder_5.1 = '/Volumes/sci-psy-narun/abcd-data-release-5.1/dictionary/'
featurefolder = "/Volumes/sci-psy-narun/Yue/ABCD_5.1_data_precessing/processed_data/"
utilFold = "/Volumes/Data/ABCD/ABCD3/Analysis/utilFunc/"
```


## load all of the files

The purpose of this code is:

1. change the variable names and select the needed variables.

2. perform the quality control to all the imaging variables.

```{r load_data2}
###loading brain scan data (Nback only)
mri_y_tfmr_mid_allvn_aseg <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_tfmr_mid_allvn_aseg.csv"))) 
mri_y_tfmr_mid_allvn_dsk <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_tfmr_mid_allvn_dsk.csv"))) 
mri_y_tfmr_mid_allvn_dst <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_tfmr_mid_allvn_dst.csv"))) 


mri_y_tfmr_mid_alrvn_aseg <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_tfmr_mid_alrvn_aseg.csv"))) 
mri_y_tfmr_mid_alrvn_dsk <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_tfmr_mid_alrvn_dsk.csv"))) 
mri_y_tfmr_mid_alrvn_dst <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_tfmr_mid_alrvn_dst.csv"))) 


mri_y_tfmr_mid_alvn_aseg <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_tfmr_mid_alvn_aseg.csv"))) 
mri_y_tfmr_mid_alvn_dsk <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_tfmr_mid_alvn_dsk.csv"))) 
mri_y_tfmr_mid_alvn_dst <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_tfmr_mid_alvn_dst.csv"))) 


mri_y_tfmr_mid_alvsl_aseg <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_tfmr_mid_alvsl_aseg.csv"))) 
mri_y_tfmr_mid_alvsl_dsk <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_tfmr_mid_alvsl_dsk.csv"))) 
mri_y_tfmr_mid_alvsl_dst <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_tfmr_mid_alvsl_dst.csv"))) 


mri_y_tfmr_mid_alvsr_aseg <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_tfmr_mid_alvsr_aseg.csv"))) 
mri_y_tfmr_mid_alvsr_dsk <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_tfmr_mid_alvsr_dsk.csv"))) 
mri_y_tfmr_mid_alvsr_dst <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_tfmr_mid_alvsr_dst.csv"))) 


mri_y_tfmr_mid_arvn_aseg <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_tfmr_mid_arvn_aseg.csv"))) 
mri_y_tfmr_mid_arvn_dsk <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_tfmr_mid_arvn_dsk.csv"))) 
mri_y_tfmr_mid_arvn_dst <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_tfmr_mid_arvn_dst.csv"))) 


mri_y_tfmr_mid_aslvn_aseg <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_tfmr_mid_aslvn_aseg.csv"))) 
mri_y_tfmr_mid_aslvn_dsk <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_tfmr_mid_aslvn_dsk.csv"))) 
mri_y_tfmr_mid_aslvn_dst <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_tfmr_mid_aslvn_dst.csv"))) 


mri_y_tfmr_mid_asrvn_aseg <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_tfmr_mid_asrvn_aseg.csv"))) 
mri_y_tfmr_mid_asrvn_dsk <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_tfmr_mid_asrvn_dsk.csv"))) 
mri_y_tfmr_mid_asrvn_dst <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_tfmr_mid_asrvn_dst.csv"))) 


mri_y_tfmr_mid_lpvnf_aseg <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_tfmr_mid_lpvnf_aseg.csv"))) 
mri_y_tfmr_mid_lpvnf_dsk <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_tfmr_mid_lpvnf_dsk.csv"))) 
mri_y_tfmr_mid_lpvnf_dst <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_tfmr_mid_lpvnf_dst.csv"))) 


mri_y_tfmr_mid_rpvnf_aseg <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_tfmr_mid_rpvnf_aseg.csv"))) 
mri_y_tfmr_mid_rpvnf_dsk <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_tfmr_mid_rpvnf_dsk.csv"))) 
mri_y_tfmr_mid_rpvnf_dst <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"mri_y_tfmr_mid_rpvnf_dst.csv"))) 
### Note that we have not removed NA before Enet tuning to keep the most number of participants

dic_tibble <-tibble::as_tibble(read.csv(paste0(dicfolder_5.1, "2024-01-23_03_20_38.681784-ABCD_Data_Dictionary.csv"))) 
qc_tibble <-tibble::as_tibble(read.csv(paste0(datafolder_5.1, "mri_y_qc_incl.csv"))) 
```


```{r}

### join all the smri data tables and select the needed features 
### also join this tibble with quality control variables
MID_all <- plyr::join_all(list(mri_y_tfmr_mid_allvn_aseg,mri_y_tfmr_mid_allvn_dsk,mri_y_tfmr_mid_allvn_dst,
                               mri_y_tfmr_mid_alrvn_aseg,mri_y_tfmr_mid_alrvn_dsk,mri_y_tfmr_mid_alrvn_dst, 
                               mri_y_tfmr_mid_alvn_aseg,mri_y_tfmr_mid_alvn_dsk,mri_y_tfmr_mid_alvn_dst,
                               mri_y_tfmr_mid_alvsl_aseg,mri_y_tfmr_mid_alvsl_dsk,mri_y_tfmr_mid_alvsl_dst,
                               mri_y_tfmr_mid_alvsr_aseg, mri_y_tfmr_mid_alvsr_dsk, mri_y_tfmr_mid_alvsr_dst,
                               mri_y_tfmr_mid_arvn_aseg,mri_y_tfmr_mid_arvn_dsk, mri_y_tfmr_mid_arvn_dst,
                               mri_y_tfmr_mid_aslvn_aseg, mri_y_tfmr_mid_aslvn_dsk, mri_y_tfmr_mid_aslvn_dst,
                               mri_y_tfmr_mid_asrvn_aseg, mri_y_tfmr_mid_asrvn_dsk,mri_y_tfmr_mid_asrvn_dst, 
                               mri_y_tfmr_mid_lpvnf_aseg,mri_y_tfmr_mid_lpvnf_dsk,mri_y_tfmr_mid_lpvnf_dst,
                               mri_y_tfmr_mid_rpvnf_aseg, mri_y_tfmr_mid_rpvnf_dsk, mri_y_tfmr_mid_rpvnf_dst),             
                          by=c("src_subject_id","eventname" ), type='full')

## column "TFMRI_MA_ACGML_B_SCS_AARH_VNDCRH" is missing!! 
##My educated guess tells me it's  TFMRI_MA_ALVSL_B_SCS_VTDCRH 

MID_all <- rename(MID_all,  tfmri_ma_acgml_b_scs_vndcrh =  tfmri_ma_alvsl_b_scs_vtdcrh) #For renaming tibble column


MID_dst_all <- MID_all %>%
                 select(all_of(c("src_subject_id","eventname")),starts_with("midabwdp"))



MID_aseg_all <- MID_all%>%
                 select(all_of(c("src_subject_id","eventname")),contains(c("_b_scs_")))


## quality control for smri data
new_subj_info <- c("src_subject_id","eventname")  

qc_features <- qc_tibble %>% select(-all_of(new_subj_info))%>% colnames()

### qc for dst data
MID_dst_qced <- full_join(MID_dst_all, qc_tibble, by = new_subj_info)%>%
             filter(imgincl_mid_include==1)%>%
             select(-all_of(qc_features))
             
qc_tibble %>% count(eventname,imgincl_mid_include)

upper_dst_names <- colnames(MID_dst_qced) %>% toupper() 


names(MID_dst_qced) <- upper_dst_names

### qc for aseg data
MID_aseg_qced <- full_join(MID_aseg_all, qc_tibble, by = new_subj_info)%>%
             filter(imgincl_mid_include==1)%>%
             select(-all_of(qc_features))
             
upper_aseg_names <- colnames(MID_aseg_qced) %>% toupper() 


names(MID_aseg_qced) <- upper_aseg_names




```




## Prep Aseg data
make the contrast Aseg readable, remove ROIs with white matter and ventricle 

```{r}
asegMIDtoGGSeg3d<-tibble::as_tibble(read.csv(paste0(utilFold,"asegMIDtoGGSeg3d_19.csv")))


MIDAseg.ConNames <- MID_aseg_qced  %>%
  select(ends_with("CBWMLH")) %>%
  rename_all(~sub('CBWMLH', '', .)) %>%
  colnames()

conNames <- c("antiRewVsNeu", 
              "antiLosVsNeu", 
              "feedRewPosVsNeg", 
              "feedPunPosVsNeg", 
              "antiLargeRewVsNeu", 
              "antiSmallRewVsNeu", 
              "antiLargeRewVsSmallRew", 
              "antiLargeLossVsNeu", 
              "antiSmallLossVsNeu", 
              "antiLargeLossVsSmallLoss") 

MIDAseg.Sub <- MID_aseg_qced %>% select("SRC_SUBJECT_ID","EVENTNAME")

ROI.FS <- MIDAseg.BetaRenamed <- list()
#take out ventricle and white matter, leaving 19 areas
for (conFSNum in 1:length(MIDAseg.ConNames)) {
  ROI.FS[conFSNum][[1]] <- MID_aseg_qced  %>%  select(contains(MIDAseg.ConNames[conFSNum])) %>% 
    select(contains(asegMIDtoGGSeg3d$MID)) %>% colnames()
  MIDAseg.BetaRenamed[conFSNum][[1]]  <- MID_aseg_qced  %>% 
    select("SRC_SUBJECT_ID","EVENTNAME", ROI.FS[conFSNum][[1]]) %>% 
    rename_at(vars(contains(MIDAseg.ConNames[conFSNum])), 
              funs(sub(MIDAseg.ConNames[conFSNum], conNames[conFSNum], .))) 
    # rename_at(vars(contains(MIDAseg.ConNames[conFSNum])), 
    #           list(~sub(MIDAseg.ConNames[conFSNum], ~conNames[conFSNum], .))) 
}

MIDAseg.BetaConRenamed <- MIDAseg.BetaRenamed %>% reduce(left_join, by = c("SRC_SUBJECT_ID","EVENTNAME"))


#change the contrast names
#MIDAseg.BetaConRenamed <- readableConMIDAsegABCD3(MIDAseg.Beta)

#load the roi names used in ggseg

#change the roi names 
MIDAseg.BetaConRoiRenamed <- MIDAseg.BetaConRenamed 
for (asegROI in 1:nrow(asegMIDtoGGSeg3d)) {
  MIDAseg.BetaConRoiRenamed <- MIDAseg.BetaConRoiRenamed  %>%
  rename_all(~sub(asegMIDtoGGSeg3d$MID[asegROI], paste0("_ROI_",asegMIDtoGGSeg3d$ggseg3d[asegROI]), .))
}
```

## Prep Dest data
1) change the col names to the names in Dict
2) change the contrast names used in Dict to the same name used for Aseg
3) change the ROI names used in Dict to ggseg3d rois for plotting

```{r}
#load the readable names based on dictionary
DestName<-tibble::as_tibble(readxl::read_excel(paste0(utilFold,"MIDDestName_201.xlsx")))
DestConDictNames <- DestName %>% select("DestConOriginal","DestConReadable")

MIDDest.BetaUniq <- MID_dst_qced[,!duplicated(colnames(MID_dst_qced))]

MIDDest.DictNames <- MIDDest.BetaUniq 
for (DestConROI in 1:nrow(DestConDictNames)) {
  MIDDest.DictNames <- MIDDest.DictNames  %>%
  rename(!!DestConDictNames$DestConReadable[DestConROI] := !!DestConDictNames$DestConOriginal[DestConROI])  
}

#load cont names used in ASEG 
MIDDestConToCommonCont<-tibble::as_tibble(read.csv(paste0(utilFold,"MIDDestConToCommonCont.csv")))

#change the cont names to match those in ASEG
MIDDest.DictNamesCommonCont <- MIDDest.DictNames
for (CommonCont in 1:nrow(MIDDestConToCommonCont)) {
  MIDDest.DictNamesCommonCont <- MIDDest.DictNamesCommonCont  %>%
  rename_all(~sub(MIDDestConToCommonCont$DestConReadable[CommonCont], MIDDestConToCommonCont$MidConNames[CommonCont], .))
}

#load the roi names used in ggseg
dictMIDtoGGSeg3d <-tibble::as_tibble(read.csv(paste0(utilFold,"dictMIDtoGGSeg3d.csv")))
#change the roi names 
MIDDest.GGSec3dNamesCommonCont <- MIDDest.DictNamesCommonCont
for (DestROI in 1:nrow(dictMIDtoGGSeg3d )) {
  MIDDest.GGSec3dNamesCommonCont <- MIDDest.GGSec3dNamesCommonCont  %>%
  rename_all(~sub(dictMIDtoGGSeg3d$MID[DestROI], paste0("_ROI_",dictMIDtoGGSeg3d$ggseg3d[DestROI]), .))
}

```

# Join Aseg and Dest together and export a file
```{r}
MIDDestAseg<- plyr::join_all(list(MIDAseg.BetaConRoiRenamed, MIDDest.GGSec3dNamesCommonCont), by=c("SRC_SUBJECT_ID","EVENTNAME"), type='left')
MIDDestAseg <- MIDDestAseg[,!duplicated(colnames(MIDDestAseg))]
#write.csv(MIDDestAseg , paste0(manipuFold,"MIDDestAsegReadableGgseg3d.csv"))
```


# save the data files

```{r}


write.csv(MIDDestAseg, paste0(featurefolder,"MIDDestAseg.csv"))

```
