---
title: "Scatter plots for predictive performance of each brain modality for baseline and follow-up"
author: "Yue Wang and Narun P"
date:  "`r format(Sys.time(), '%d %b, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: united
    number_sections: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load_data, echo=FALSE}
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.
```

## Note
Here we the ABCD release 5.1 data-set

# Setting up the environments

## Loading libraries
The following libraries and default settings were used during the analysis:


```{r load_libraries}
options(scipen = 999)
#library("sva")
library(tidyverse)
library("tidymodels")
##parallel map
library(partR2)
library(lme4)
library(yhat)

library(partR2)
library(lme4)
library(yhat)
### plotting
library(ggpointdensity)
library(ggtext)
library(ggpubr)
library(cowplot)
library(viridis)

theme_set(theme_bw() + theme(panel.grid = element_blank()))
## parallel processing number of cores register
all_cores <- parallel::detectCores(logical = FALSE) - 5

doParallel::registerDoParallel(cores = all_cores)

```

## Loading local paths


We first loaded all of the relevant data files (not shown here as they refer to local directories):

```{r loading_data, echo=FALSE}
# from Qnap data windows
#datafolder = "//np-qnapa/Data/ABCD/ABCD4/ABCD4SQL/"
#scriptfold = "//np-qnapa/Data/Yue script/"
#NDAfold = "//np-qnapa/Data/ABCD/ABCD4/ABCDStudyNDA/"
#utilFold = "//np-qnapa/Data/ABCD/ABCD3/Analysis/utilFunc/"
#studyNDAFold = "//np-qnapa/Data/ABCD/ABCD4/ABCDStudyNDA/"
#outputfolder = "//np-qnapa/Data/ABCD/ABCD4/ABCD4_precessed_data/"

### unbuntu directories

#datafolder = "/media/Data/ABCD/ABCD4/ABCD4SQL/"
#scriptfold = "/media/Data/Yue script/"
#NDAfold = "/media/Data/ABCD/ABCD4/ABCDStudyNDA/"
#utilFold = "/media/Data/ABCD/ABCD3/Analysis/utilFunc/"
#studyNDAFold = "/media/Data/ABCD/ABCD4/ABCDStudyNDA/"
#outputfolder = "/media/Data/ABCD/ABCD4/ABCD4_precessed_data/"
#featurefolder = "/media/Data/ABCD/ABCD4/Analysis/ManipulatedData/"

### mac directories
datafolder = "/Volumes/Data/ABCD/ABCD4/ABCD4SQL/"
scriptfold = "/Volumes/Data/Yue script/"
NDAfold = "/Volumes/Data/ABCD/ABCD4/ABCDStudyNDA/"
utilFold = "/Volumes/Data/ABCD/ABCD3/Analysis/utilFunc/"
studyNDAFold = "/Volumes/Data/ABCD/ABCD4/ABCDStudyNDA/"
outputfolder = "/Volumes/Data/ABCD/ABCD4/ABCD4_precessed_data/"
featurefolder = "/Volumes/Data/ABCD/ABCD4/Analysis/ManipulatedData/"
nesi_folder <- "/Volumes/sci-psy-narun/Nesi/Yue/"

source(paste0(scriptfold,"stacking_gfactor_modelling/r_functions_5.1.R"))


```


# Loading and processing data

Get the naming vectors.

```{r}
subj_info <- c("SRC_SUBJECT_ID","SITE_ID_L","EVENTNAME")

```


## Load in enet predicted results

Loading the processed elastic net test predictions. Those tables are extracted from Nesi model fit output files.

```{r}
enet_baseline_list  <- readRDS(paste0(scriptfold,"stacking_gfactor_modelling/random_forest_data/random_forest_all_baseline_test_5.1.RDS"))
enet_followup_list <- readRDS(paste0(scriptfold,"stacking_gfactor_modelling/random_forest_data/random_forest_all_followup_test_5.1.RDS"))
```

```{r}
enet_baseline_tibble <- enet_baseline_list %>% do.call(rbind,.)
enet_followup_tibble <- enet_followup_list %>% do.call(rbind,.)

```
## load fitted gfactors from brain scan and psychopathology

### load brain scan fitted results from stacking models

```{r}
rf_baseline <- readRDS(paste0(nesi_folder,"stacking_gfactor_modelling/collect_random_forest_results/random_forest_baseline_results.RDS"))

rf_followup <- readRDS(paste0(nesi_folder,"stacking_gfactor_modelling/collect_random_forest_results/random_forest_followup_results.RDS"))
```


Be careful with what site you choose.

```{r}

rf_baseline_pred <- map(rf_baseline,"test_pred")
rf_baseline_pred_tibble <- map(rf_baseline_pred,"model_predict")
rf_baseline_table <- map(rf_baseline,"test_data")

rf_baseline_data_select <- rf_baseline_table %>% map(.,~select(.,all_of(subj_info)))
rf_baseline_pred_select <- rf_baseline_pred_tibble %>% map(.,~select(.,model_predict)%>%
                                                             rename(rf_pred = model_predict))
rf_baseline_select <- map2(.x = rf_baseline_data_select,.y = rf_baseline_pred_select,~bind_cols(.x,.y))%>%
                      do.call(rbind,.)

rf_followup_pred <- map(rf_followup,"test_pred")
rf_followup_pred_tibble <- map(rf_followup_pred,"model_predict")
rf_followup_table <- map(rf_followup,"test_data")

rf_followup_data_select <- rf_followup_table %>% map(.,~select(.,all_of(subj_info)))
rf_followup_pred_select <- rf_followup_pred_tibble %>% map(.,~select(.,model_predict)%>%
                                                             rename(rf_pred = model_predict))
rf_followup_select <- map2(.x = rf_followup_data_select,.y = rf_followup_pred_select,~bind_cols(.x,.y))%>%
                      do.call(rbind,.)
```


### load the mental health predicted results

```{r}
psy_pred <- readRDS(paste0(scriptfold,"Common_psy_gene_brain_all/saved_outputs/psychopathology_pls_pred_5.1.RData"))


psy_baseline_data_select <- psy_pred[["baseline_test_data"]] %>% map(.,~select(.,all_of(subj_info)))
psy_baseline_pred_select <- psy_pred[["baseline_test_pred"]] %>% map(.,~select(.,model_predict)%>%
                                                             rename(psy_pred = model_predict))
psy_baseline_select <- map2(.x = psy_baseline_data_select,.y = psy_baseline_pred_select,~bind_cols(.x,.y))%>%
                      do.call(rbind,.)


psy_followup_data_select <- psy_pred[["followup_test_data"]] %>% map(.,~select(.,all_of(subj_info)))
psy_followup_pred_select <- psy_pred[["followup_test_pred"]] %>% map(.,~select(.,model_predict)%>%
                                                             rename(psy_pred = model_predict))
psy_followup_select <- map2(.x = psy_followup_data_select,.y = psy_followup_pred_select,~bind_cols(.x,.y))%>%
                      do.call(rbind,.)
```


### load the social demographic lifestyle developmental predicted results


```{r}
ses_pred <- readRDS(paste0(scriptfold,"genetics_psychopathology_common_scan_all_scripts/ses_pls_pred_5.1.RData"))

ses_baseline_data_select <- ses_pred[["baseline_test_data"]] %>% map(.,~select(.,all_of(subj_info)))
ses_baseline_pred_select <- ses_pred[["baseline_test_pred"]] %>% map(.,~select(.,model_predict)%>%
                                                             rename(ses_pred = model_predict))
ses_baseline_select <- map2(.x = ses_baseline_data_select,.y = ses_baseline_pred_select,~bind_cols(.x,.y))%>%
                      do.call(rbind,.)


ses_followup_data_select <- ses_pred[["followup_test_data"]] %>% map(.,~select(.,all_of(subj_info)))
ses_followup_pred_select <- ses_pred[["followup_test_pred"]] %>% map(.,~select(.,model_predict)%>%
                                                             rename(ses_pred = model_predict))
ses_followup_select <- map2(.x = ses_followup_data_select,.y = ses_followup_pred_select,~bind_cols(.x,.y))%>%
                      do.call(rbind,.)
```

### Load in genetics related to cognition predicted results 


```{r}

genetics_cog <- readRDS(paste0(scriptfold,'genetics_psychopathology_common_scan_all_scripts/psychopathology_cog_gene_pred_residual_5.1', '.RData'))

gene_baseline_data_select <- genetics_cog[["baseline_test_data"]]%>%map(.,~select(.,all_of("SRC_SUBJECT_ID")))
gene_baseline_pred_select <- genetics_cog[["baseline_test_pred"]] %>% map(.,~select(.,model_predict)%>%
                                                             rename(gene_pred = model_predict))
gene_baseline_select <- map2(.x = gene_baseline_data_select,.y = gene_baseline_pred_select,~bind_cols(.x,.y))%>%
                      do.call(rbind,.)


gene_followup_data_select <- genetics_cog[["followup_test_data"]] %>% map(.,~select(.,all_of("SRC_SUBJECT_ID")))
gene_followup_pred_select <- genetics_cog[["followup_test_pred"]] %>% map(.,~select(.,model_predict)%>%
                                                             rename(gene_pred = model_predict))
gene_followup_select <- map2(.x = gene_followup_data_select,.y = gene_followup_pred_select,~bind_cols(.x,.y))%>%
                      do.call(rbind,.)
```

### load the computed gfactor

```{r}

gfactor_list <- readRDS(paste0(scriptfold,"genetics_psychopathology_common_scan_all_scripts/gfactor_scale_seperate_5.1.RData"))


```


```{r}

gfactor_baseline_test <- map(gfactor_list,"output_test_baseline")%>%
                      do.call(rbind,.)
gfactor_followup_test <- map(gfactor_list,"output_test_followup")%>%
                      do.call(rbind,.)


```




```{r}
baseline_pred <- plyr::join_all(list(psy_baseline_select,
                                         rf_baseline_select,
                                         ses_baseline_select,
                                         enet_baseline_tibble),by = subj_info,type = "full")

followup_pred <- plyr::join_all(list(psy_followup_select,
                                         enet_followup_tibble,
                                         rf_followup_select,
                                         ses_followup_select),by = subj_info,type = "full")


baseline_pred_all <- plyr::join_all(list(baseline_pred,
                                         gfactor_baseline_test,
                                         gene_baseline_select),by = "SRC_SUBJECT_ID",type = "full")

followup_pred_all <- plyr::join_all(list(followup_pred,
                                         gfactor_followup_test,
                                         gene_followup_select),by = "SRC_SUBJECT_ID",type = "full")

```


```{r}
saveRDS(baseline_pred_all, paste0(scriptfold,'Common_psy_gene_brain_all/saved_outputs/baseline_pred_all_5.1', '.RData'))
saveRDS(followup_pred_all, paste0(scriptfold,'Common_psy_gene_brain_all/saved_outputs/followup_pred_all_5.1', '.RData'))

```

