---
title: "ABCD 5.1 data processing"
author: "Yue Wang and Narun P"
date:  "`r format(Sys.time(), '%d %b, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: united
    number_sections: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)

options(width = 60)
local({
  hook_output <- knitr::knit_hooks$get('output')
  knitr::knit_hooks$set(output = function(x, options) {
    if (!is.null(options$max.height)) options$attr.output <- c(
      options$attr.output,
      sprintf('style="max-height: %s;"', options$max.height)
    )
    hook_output(x, options)
  })
})
```

Show part of the output if it is too long.

```{r load_data, echo=FALSE}
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.
```

## Note
Here we the ABCD release 5.1 data-set

# Setting up the environment

## Loading libraries
The following libraries and default settings were used during the analysis:


```{r load_libraries}
options(scipen = 999)
#library("sva")
library(tidyverse)
#library("tidymodels")
##parallel map

theme_set(theme_bw() + theme(panel.grid = element_blank()))
## parallel processing number of cores register
all_cores <- parallel::detectCores(logical = FALSE) - 10

doParallel::registerDoParallel(cores = all_cores)

```

## Setting up paths.

We first loaded all of the relevant data files (not shown here as they refer to local directories):

```{r loading_data, echo=FALSE}
### the directories for loading up data and files

datafolder_5.1 = '/Volumes/sci-psy-narun/abcd-data-release-5.1/core/'
outputfolder_5.1 = "/Volumes/sci-psy-narun/Yue/ABCD_5.1_data_precessing/processed_data/"
dicfolder_5.1 = '/Volumes/sci-psy-narun/abcd-data-release-5.1/dictionary/'
featurefolder = "/Volumes/sci-psy-narun/Yue/ABCD_5.1_data_precessing/processed_data/"
utilFold = "/Volumes/Data/ABCD/ABCD3/Analysis/utilFunc/"
imagingfolder_5.1  = paste0(datafolder_5.1, "imaging/")
```


# Data Preparation

## Loading site information



```{r load_site}

Siteinfo <-tibble::as_tibble(read.csv(paste0(datafolder_5.1, "abcd-general/abcd_y_lt.csv")))
```

## load all of the files

The aim is to compute almost all of the sets of all brain features into the analysis.

All of the following files are processed with quality control. Please refer to those files if necessary.


```{r load_data2}
###loading site and scanner information
MRIinfo <-tibble::as_tibble(read.csv(paste0(imagingfolder_5.1, "mri_y_adm_info.csv"))) 
MriandSite <- left_join(MRIinfo,Siteinfo, by=c('src_subject_id','eventname'))
### loading demographics
demo_info <-tibble::as_tibble(read.csv(paste0(datafolder_5.1, "abcd-general/abcd_p_demo.csv")))
demo_info%>% count(demo_sex_v2,eventname)

### include variables about sex into the demographics
upper_demo_names <- colnames(demo_info) %>% toupper() 

names(demo_info) <- upper_demo_names
### change the variable name to upper case
names(MriandSite) <-toupper(colnames(MriandSite))


###loading response variables
NIH_TB <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"neurocognition/nc_y_nihtb.csv"))) 
names(NIH_TB) <-toupper(colnames(NIH_TB))

LittleMan <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"neurocognition/nc_y_lmt.csv"))) 
names(LittleMan) <-toupper(colnames(LittleMan))

nc_y_ravlt <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"neurocognition/nc_y_ravlt.csv"))) 
names(nc_y_ravlt) <-toupper(colnames(nc_y_ravlt))

nc_y_wisc <-tibble::as_tibble(read.csv(paste0(datafolder_5.1,"neurocognition/nc_y_wisc.csv"))) 
names(nc_y_wisc) <-toupper(colnames(nc_y_wisc))

NBackBeh <- tibble::as_tibble(read.csv(paste0(imagingfolder_5.1, "mri_y_tfmr_nback_beh.csv")) ) 
names(NBackBeh) <-toupper(colnames(NBackBeh))
## loading information about school, interview, site, family.
acspsw03 <- read.csv(paste0(datafolder_5.1,"abcd-general/abcd_y_lt.csv"), na = c("", "NA", "999", "777"))
names(acspsw03) <-toupper(colnames(acspsw03))

###loading QCed brain scan data (Nback only)
NBackDestAsegQCed <- tibble::as_tibble(read.csv(paste0(featurefolder, "NBackDestAseg.csv")) ) 
MIDDestAsegQCed <- tibble::as_tibble(read.csv(paste0(featurefolder, "MIDDestAseg.csv")) ) 
SSTDestAsegQCed <- tibble::as_tibble(read.csv(paste0(featurefolder, "SSTDestAseg.csv")) ) 



DTI_FA23Tracks <- tibble::as_tibble(read.csv(paste0(featurefolder, "DTI_FA23Tracks.csv")) ) 

RSBetNetExcludedNoCOMBATABCD4 <- tibble::as_tibble(read.csv(paste0(featurefolder, "RSBetNetExcludedNoCOMBATABCD4.csv")) ) 

dim(RSBetNetExcludedNoCOMBATABCD4)

#colnames(RSBetNetExcludedNoCOMBATABCD4)

RSBetNetExcludedNoCOMBATABCD4_selected_names <- RSBetNetExcludedNoCOMBATABCD4%>%
                                                dplyr::select(-all_of(c("SRC_SUBJECT_ID","EVENTNAME" )))%>%
                                                colnames()


RSSubNetExcludedNoCOMBATedABCD4 <- tibble::as_tibble(read.csv(paste0(featurefolder, "RSSubNetExcludedNoCOMBATedABCD4.csv")) ) 

dim(RSSubNetExcludedNoCOMBATedABCD4)

RSSubNetExcludedNoCOMBATedABCD4_selected_names <- RSSubNetExcludedNoCOMBATedABCD4%>%
                                                select(-all_of(c("SRC_SUBJECT_ID","EVENTNAME" )))%>%
                                                colnames()


rsmri_variance_gordon_aseg <- tibble::as_tibble(read.csv(paste0(featurefolder, "rsmri_variance_gordon_aseg.csv")) ) 



dim(rsmri_variance_gordon_aseg)

#colnames(rsmri_variance_gordon_aseg)

sMRI.T2Weighted <- tibble::as_tibble(read.csv(paste0(featurefolder, "sMRI.T2Weighted.csv")) ) 
sMRI.T1Weighted <- tibble::as_tibble(read.csv(paste0(featurefolder, "sMRI.T1Weighted.csv")) ) 



### Note that we have not removed NA before Enet tuning to keep the most number of participants

### load vision scan data, according to the documents some of the participants cannot see the IPad screen
vision_idx <- tibble::as_tibble(read.csv(paste0(datafolder_5.1, "neurocognition/nc_y_svs.csv"),header = TRUE))
names(vision_idx) <-toupper(colnames(vision_idx))





```

demo_sex_v2	What sex was the child assigned at birth, on the original birth certificate? 	1 = Male ; 2 = Female; 3 = Intersex-Male ; 4 = Intersex-Female ; 999 = Don't know ; 777 = Refuse to answer 

demo_gender_id_v2	What is the child's current gender identity? 	1 = Male ; 2 = Female; 3 = Trans male; 4 = Trans female ; 5 = Gender queer; 6 = Different; 777 = Refuse to answer ; 999 = Don't know 


```{r}

### processing demographic information use the sex category assigned at birth drop the observations assigned as Intersex-Male
### there are three such observations

demo_selected <- demo_info %>% filter(EVENTNAME == "baseline_year_1_arm_1" ) %>% select(SRC_SUBJECT_ID,DEMO_SEX_V2) %>% 
                               filter(DEMO_SEX_V2 != 3)

```


Three children are assigned as Intersex-Male at baseline so they are removed



## Join all the data sets

```{r}
### join all the data

data_all <- plyr::join_all(list(NBackDestAsegQCed,
                                MIDDestAsegQCed,
                                SSTDestAsegQCed,
                                DTI_FA23Tracks,
                                RSBetNetExcludedNoCOMBATABCD4,
                                rsmri_variance_gordon_aseg,
                                sMRI.T2Weighted,
                                sMRI.T1Weighted,
                                NBackBeh,
                                nc_y_ravlt,
                                nc_y_wisc,
                                LittleMan,
                                NIH_TB,
                                MriandSite,
                                vision_idx,
                                RSSubNetExcludedNoCOMBATedABCD4), 
                           by=c('SRC_SUBJECT_ID','EVENTNAME'), type='full')
  
### full join all the data sets to keep all the participants after QC. Actually smri have the most number of participants
### there are only two participants that are not in the smri data set but in other modalities.
### change integer response variables into double for later scaling and IQR
data_all$PEA_RAVLT_LD_TRIAL_VII_TC <- as.double(data_all$PEA_RAVLT_LD_TRIAL_VII_TC)
data_all$PEA_WISCV_TRS <- as.double(data_all$PEA_WISCV_TRS)
```

## filter out the participants that have problems with vision

54 subjects

```{r}
data_removed <- data_all %>% filter(SNELLEN_VA_Y == 0 | SNELLEN_VA_Y == 1 | VIS_FLG == 2)

removed_subj <- data_removed$SRC_SUBJECT_ID
data_all <- data_all %>% filter(!SRC_SUBJECT_ID %in% removed_subj)

length(removed_subj)
```

### Get the number of the participants removed by vision problems

```{r}



data_list <- list(nback = NBackDestAsegQCed,
                  MID =   MIDDestAsegQCed,
                  SST =   SSTDestAsegQCed,
                  DTI =   DTI_FA23Tracks,
                  rsmri  =  full_join(RSBetNetExcludedNoCOMBATABCD4,rsmri_variance_gordon_aseg,by=c('SRC_SUBJECT_ID','EVENTNAME')),
                  smri_t1 =sMRI.T1Weighted ,
                  smri_t2 =  sMRI.T2Weighted)

```

```{r}

vision_removed <- vision_idx %>% filter(SNELLEN_VA_Y == 0 | SNELLEN_VA_Y == 1 | VIS_FLG == 2)



vision_baseline <- vision_removed %>% filter(EVENTNAME == "baseline_year_1_arm_1" )
vision_2_followup <- vision_removed %>% filter(EVENTNAME == "2_year_follow_up_y_arm_1"  )
 vision_4_followup <- vision_removed %>% filter(EVENTNAME == "4_year_follow_up_y_arm_1"  )

site_only <- Siteinfo %>% select(all_of(c("src_subject_id","eventname","site_id_l")))
names(site_only) <- toupper(names(site_only))

site_22_baseline <- site_only %>% filter(EVENTNAME == "baseline_year_1_arm_1" & SITE_ID_L =="site22" )
site_22_2_followup <- site_only %>% filter(EVENTNAME == "2_year_follow_up_y_arm_1" & SITE_ID_L =="site22" )
site_22_4_followup <- site_only %>% filter(EVENTNAME == "4_year_follow_up_y_arm_1" & SITE_ID_L =="site22" )


get_vision_site_num <- function(data_input = data_list[["smri_t1"]] ){
  data_input_baseline <- data_input %>% filter(EVENTNAME == "baseline_year_1_arm_1" )
 data_input_2_followup <- data_input %>% filter(EVENTNAME == "2_year_follow_up_y_arm_1"  )
  data_input_4_followup <- data_input %>% filter(EVENTNAME == "4_year_follow_up_y_arm_1"  )

  vision_data_baseline <- data_input_baseline%>% 
                           filter(! SRC_SUBJECT_ID %in% removed_subj)
  vision_data_2_followup<- data_input_2_followup %>% 
                           filter(! SRC_SUBJECT_ID %in% removed_subj)
  vision_data_4_followup <- data_input_4_followup %>% 
                           filter(! SRC_SUBJECT_ID %in% removed_subj)
  
  
  site_data_baseline <-vision_data_baseline%>% 
                           filter(! SRC_SUBJECT_ID %in% site_22_baseline$SRC_SUBJECT_ID)
  site_data_2_followup<- vision_data_2_followup%>% 
                           filter(! SRC_SUBJECT_ID %in% site_22_2_followup$SRC_SUBJECT_ID)
  site_data_4_followup <- vision_data_4_followup %>% 
                           filter(! SRC_SUBJECT_ID %in% site_22_4_followup$SRC_SUBJECT_ID)
  output_tibble = tibble (vision = c(nrow(vision_data_baseline),nrow(vision_data_2_followup),nrow(vision_data_4_followup)),
                          site = c(nrow(site_data_baseline),nrow(site_data_2_followup),nrow(site_data_4_followup)))
  return(output_tibble)
}

data_num_list <- map(data_list,~get_vision_site_num(data_input = .))
names(data_num_list) <- names(data_list)

data_num_list
```

### Remove all those participants



```{r}

data_all_trial <- data_all%>%
    drop_na(SITE_ID_L) %>%
  filter(SITE_ID_L != "site22")


```

## set up variable names

```{r}
TaskDVs1Batch = c("NIHTBX_PICVOCAB_UNCORRECTED", 
                  "NIHTBX_READING_UNCORRECTED",
              "NIHTBX_FLANKER_UNCORRECTED",
              "NIHTBX_PATTERN_UNCORRECTED",
              "NIHTBX_PICTURE_UNCORRECTED",
               "PEA_RAVLT_LD_TRIAL_VII_TC")


subj_info <- c('SRC_SUBJECT_ID', 'SITE_ID_L',"EVENTNAME")
```


# Set up the sets of brain features

## Getting all the contrasts

```{r}
### get the names of the contrasts for all the modalities

nback_contrasts <- NBackDestAsegQCed%>%
                   select(ends_with("Left.Cerebellum.Cortex"))%>%
                   colnames()%>%
                   str_remove_all("Left.Cerebellum.Cortex")%>%
                   print()

MID_contrasts <- MIDDestAsegQCed%>%
                   select(ends_with("Left.Cerebellum.Cortex"))%>%
                   colnames()%>%
                   str_remove_all("Left.Cerebellum.Cortex")%>%
                   print()

SST_contrasts <- SSTDestAsegQCed%>%
                   select(ends_with("Left.Cerebellum.Cortex"))%>%
                   colnames()%>%
                   str_remove_all("Left.Cerebellum.Cortex")%>%
                   print()


## "Within" and  "avg" comprise one modality

rsmri_within <- RSBetNetExcludedNoCOMBATABCD4%>%
                   select(ends_with("Auditory"))%>%
                   colnames()%>%
                   str_remove_all("Auditory")%>%
                   print()





rsmri_avg <- RSBetNetExcludedNoCOMBATABCD4%>%
                   select(ends_with("AuditoryCinguloOpercular"))%>%
                   colnames()%>%
                   str_remove_all("AuditoryCinguloOpercular")%>%
                   print()


###  "rsmri_var_gordon_ROI_" and "rsmri_var_aseg_ROI_" are one modality


rsmri_gordon <- rsmri_variance_gordon_aseg%>%
                   select(ends_with("SMhand_1"))%>%
                   colnames()%>%
                   str_remove_all("SMhand_1")%>%
                   print()


rsmri_aseg <- rsmri_variance_gordon_aseg%>%
                   select(ends_with("Left.Cerebellum.Cortex"))%>%
                   colnames()%>%
                   str_remove_all("Left.Cerebellum.Cortex")%>%
                   print()




smri_T1_aseg <- sMRI.T1Weighted%>%
                   select(ends_with("Left.Cerebellum.Cortex"))%>%
                   colnames()%>%
                   str_remove_all("Left.Cerebellum.Cortex")%>%
                   print()


smri_T2_aseg <- sMRI.T2Weighted%>%
                   select(ends_with("Left.Cerebellum.Cortex"))%>%
                   colnames()%>%
                   str_remove_all("Left.Cerebellum.Cortex")%>%
                   print()


smri_T1_dest <- sMRI.T1Weighted%>%
                   select(ends_with("lh_G_and_S_paracentral"))%>%
                   colnames()%>%
                   str_remove_all("lh_G_and_S_paracentral")%>%
                   print()


smri_T2_dest <- sMRI.T2Weighted%>%
                   select(ends_with("lh_G_and_S_paracentral"))%>%
                   colnames()%>%
                   str_remove_all("lh_G_and_S_paracentral")%>%
                   print()


smri_T1_mean_total <- c('Dest_total_area','Dest_total_volumn','Dest_mean_thickness','Dest_mean_sulcal_depth','mean_T1_Avg_white','mean_T1_Avg_gray','mean_T1_normalised','subcorticalgrayvolume','Avg_T1_whole_Cerebellum_Cortex_ASEG' )
  
  
smri_T2_mean_total <- c('mean_T2_Avg_white','mean_T2_Avg_gray','mean_T2_normalised','Avg_T2_whole_Cerebellum_Cortex_ASEG' )

```


## split all the data tables based on the contrasts


```{r}
one_contrast_extract <- function(name_input ){
 data_output = select(data_all_trial, starts_with(name_input),all_of(subj_info))
 return(data_output)
}
nback_list <- nback_contrasts %>% map(., ~one_contrast_extract(name_input = .))

MID_list <-    MID_contrasts%>% map(., ~one_contrast_extract(name_input = .))

SST_list <- SST_contrasts %>% map(., ~one_contrast_extract(name_input = .))

cog_data <- select(data_all_trial,all_of(TaskDVs1Batch),all_of(subj_info))

rsmri_within_avg_data <- select(data_all_trial,all_of(RSBetNetExcludedNoCOMBATABCD4_selected_names), all_of(subj_info))

rsmri_gordon_aseg_data <- select(data_all_trial,starts_with(rsmri_gordon),starts_with(rsmri_aseg), all_of(subj_info))

rsmri_subnet <- select(data_all_trial,all_of(RSSubNetExcludedNoCOMBATedABCD4_selected_names), all_of(subj_info))


smri_T1_aseg_list <- smri_T1_aseg %>% map(., ~one_contrast_extract(name_input = .))

smri_T2_aseg_list <- smri_T2_aseg %>% map(., ~one_contrast_extract(name_input = .))

smri_T1_dest_list <- smri_T1_dest %>% map(., ~one_contrast_extract(name_input = .))

smri_T2_dest_list <- smri_T2_dest %>% map(., ~one_contrast_extract(name_input = .))

smri_T1_mean_total_data <- select(data_all_trial,starts_with(smri_T1_mean_total), all_of(subj_info))

smri_T2_mean_total_data <- select(data_all_trial,starts_with(smri_T2_mean_total), all_of(subj_info))


##### processing DTI data

DTI_select <- DTI_FA23Tracks %>% select(starts_with("FA_"), all_of(c("EVENTNAME","SRC_SUBJECT_ID")))

suj_info_tibble <- data_all_trial %>% select(all_of(subj_info))

DTI_data <- left_join(DTI_select,suj_info_tibble,by = c("EVENTNAME","SRC_SUBJECT_ID"))



### save the information about site, family id
acspsw03_select <- acspsw03 %>%  select(all_of(c("SRC_SUBJECT_ID","EVENTNAME","SITE_ID_L","REL_FAMILY_ID")))






```


demo_sex_v2	What sex was the child assigned at birth, on the original birth certificate? 	1 = Male ; 2 = Female; 3 = Intersex-Male ; 4 = Intersex-Female ; 999 = Don't know ; 777 = Refuse to answer 

demo_gender_id_v2	What is the child's current gender identity? 	1 = Male ; 2 = Female; 3 = Trans male; 4 = Trans female ; 5 = Gender queer; 6 = Different; 777 = Refuse to answer ; 999 = Don't know 




## Saving up all the outputs

Save to RDS file

```{r,eval=FALSE,echo=FALSE}
### all the recipes are uploaded to Nesi
###tuning hyper-parameters are done on nesi

map2(.x = nback_contrasts, .y = nback_list, ~saveRDS(.y, 
                                    paste0(featurefolder,'RDS/',.x,'.RDS')))

map2(.x = MID_contrasts, .y = MID_list, ~saveRDS(.y, 
                          paste0(featurefolder,'RDS/',.x , '.RDS')))

map2(.x = SST_contrasts, .y = SST_list, ~saveRDS(.y, 
                          paste0(featurefolder,'RDS/',.x , '.RDS')))

saveRDS(cog_data, paste0(featurefolder,'RDS/cog_data.RDS'))

saveRDS(rsmri_within_avg_data, paste0(featurefolder,'RDS/rsmri_within_avg_data.RDS'))

saveRDS(rsmri_gordon_aseg_data, paste0(featurefolder,'RDS/rsmri_gordon_aseg_data.RDS'))

saveRDS(rsmri_subnet, paste0(featurefolder,'RDS/rsmri_subnet.RDS'))



map2(.x = smri_T1_aseg, .y = smri_T1_aseg_list, ~saveRDS(.y, 
                          paste0(featurefolder,'RDS/',.x , '.RDS')))
map2(.x = smri_T2_aseg, .y = smri_T2_aseg_list, ~saveRDS(.y, 
                          paste0(featurefolder,'RDS/',.x , '.RDS')))
map2(.x = smri_T1_dest, .y = smri_T1_dest_list, ~saveRDS(.y, 
                          paste0(featurefolder,'RDS/',.x , '.RDS')))
map2(.x = smri_T2_dest, .y = smri_T2_dest_list, ~saveRDS(.y, 
                          paste0(featurefolder,'RDS/',.x , '.RDS')))



saveRDS(smri_T1_mean_total_data, paste0(featurefolder,'RDS/smri_T1_mean_total_data.RDS'))

saveRDS(smri_T2_mean_total_data, paste0(featurefolder,'RDS/smri_T2_mean_total_data.RDS'))
saveRDS(DTI_data, paste0(featurefolder,'RDS/DTI_data.RDS'))

### save the cognitive scores:

NIH_TB_select <- NIH_TB %>% select(all_of(c("SRC_SUBJECT_ID","EVENTNAME")),ends_with("_UNCORRECTED"))
saveRDS(NIH_TB_select, paste0(featurefolder,'RDS/NIH_TB_select.RDS'))

saveRDS(acspsw03_select, paste0(featurefolder,'RDS/acspsw03_select.RDS'))

saveRDS(demo_selected, paste0(featurefolder,'RDS/demo_selected.RDS'))

```

save to csv files

```{r,eval=FALSE,echo=FALSE}
### all the recipes are uploaded to Nesi
###tuning hyper-parameters are done on nesi

map2(.x = nback_contrasts, .y = nback_list, ~write.csv(.y, 
                                    paste0(featurefolder,'CSV/',.x,'.csv')))

map2(.x = MID_contrasts, .y = MID_list, ~write.csv(.y, 
                          paste0(featurefolder,'CSV/',.x , '.csv')))

map2(.x = SST_contrasts, .y = SST_list, ~write.csv(.y, 
                          paste0(featurefolder,'CSV/',.x , '.csv')))

write.csv(cog_data, paste0(featurefolder,'CSV/cog_data.csv'))

write.csv(rsmri_within_avg_data, paste0(featurefolder,'CSV/rsmri_within_avg_data.csv'))

write.csv(rsmri_gordon_aseg_data, paste0(featurefolder,'CSV/rsmri_gordon_aseg_data.csv'))

write.csv(rsmri_subnet, paste0(featurefolder,'CSV/rsmri_subnet.csv'))



map2(.x = smri_T1_aseg, .y = smri_T1_aseg_list, ~write.csv(.y, 
                          paste0(featurefolder,'CSV/',.x , '.csv')))
map2(.x = smri_T2_aseg, .y = smri_T2_aseg_list, ~write.csv(.y, 
                          paste0(featurefolder,'CSV/',.x , '.csv')))
map2(.x = smri_T1_dest, .y = smri_T1_dest_list, ~write.csv(.y, 
                          paste0(featurefolder,'CSV/',.x , '.csv')))
map2(.x = smri_T2_dest, .y = smri_T2_dest_list, ~write.csv(.y, 
                          paste0(featurefolder,'CSV/',.x , '.csv')))



write.csv(smri_T1_mean_total_data, paste0(featurefolder,'CSV/smri_T1_mean_total_data.csv'))

write.csv(smri_T2_mean_total_data, paste0(featurefolder,'CSV/smri_T2_mean_total_data.csv'))
write.csv(DTI_data, paste0(featurefolder,'CSV/DTI_data.csv'))

## save response cognitive scires
write.csv(NIH_TB_select, paste0(featurefolder,'CSV/NIH_TB_select.csv'))
### save the information about site, family id
saveRDS(acspsw03_select, paste0(featurefolder,'CSV/acspsw03_select.csv'))

saveRDS(demo_selected, paste0(featurefolder,'CSV/demo_selected.csv'))

```


## print out the feature names for each modality


```{r,eval=FALSE}
feature_name_print <- function(data_input){
  col_names <- data_input %>% select(-all_of(subj_info))%>% colnames()
  print(col_names)
}


map(nback_list,~feature_name_print(data_input = .))

map(MID_list,~feature_name_print(data_input = .))


map(SST_list,~feature_name_print(data_input = .))


feature_name_print(data_input =rsmri_within_avg_data)

feature_name_print(data_input =rsmri_gordon_aseg_data)

feature_name_print(data_input =rsmri_subnet)

map(smri_T1_aseg_list,~feature_name_print(data_input = .))


map(smri_T2_aseg_list,~feature_name_print(data_input = .))


map(smri_T1_dest_list,~feature_name_print(data_input = .))


map(smri_T2_dest_list,~feature_name_print(data_input = .))

feature_name_print(data_input =smri_T1_mean_total_data)
feature_name_print(data_input =smri_T2_mean_total_data)
feature_name_print(data_input =DTI_data)



```



