---
title: "PLS Model Fitting of Cognitive Abilities ~ Soc-Dem-Life-Dev for baseline and follow-up"
author: "Yue Wang, Narun Pat"
date:  "`r format(Sys.time(), '%d %b, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: united
    number_sections: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

options(scipen = 999)
```

# Set the working environment

## Reset workspace and load libraries  
This analysis uses ABCD Release 5.1.

This script is modified based on the social economics status and developmental analysis with elastic net version 2.0.

```{r , results='hide', message=FALSE, warning=FALSE}
rm(list=ls())
gc()
```

```{r , results='hide', message=FALSE, warning=FALSE}
library(tidyverse)
library(qgraph)
library(pander)
library(summarytools)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(tidymodels)
library(knitr)
library(extrafont)
## for poisson class of elastic net
library(poissonreg)
library("sva")
### plotting libraries
library(ggtext)
library(ggpubr)
library(cowplot)
library(ggthemes)
### package for pls analysis (all packages are necessary for the model to run)
library("pls")
library("mixOmics")
library(plsmod)

```


## Setting up paths

Using ABCD 4.0 

```{r, cache=FALSE, include=FALSE}

#ABCD3Fold <- '/Volumes/wd/ABCD3/'
#ABCD3Fold <-"~/OneDrive - University of Otago/ABCD3/"

#ABCD4Fold <-"/media/Data/ABCD/ABCD4/"
ABCD4Fold <-"/Volumes/Data/ABCD/ABCD4/"


#ABCD4Fold <- "//np-qnapa/Data/ABCD/ABCD4/"
#setwd(paste0(ABCD3Fold, "Analysis/CognitionP"))
dataFold <- paste0(ABCD4Fold, "ABCD4SQL/")

#ABCD3Fold <-"/media/Data/ABCD/ABCD3/"
ABCD3Fold <-"/Volumes/Data/ABCD/ABCD3/"


#utilFold <- paste0(ABCD3Fold, "Analysis/utilFunc/")

#scriptfold = "/media/Data/Yue script/"
scriptfold = "/Volumes/Data/Yue script/"


datafolder_5.1 = '/Volumes/sci-psy-narun/abcd-data-release-5.1/core/'
outputfolder_5.1 = "/Volumes/sci-psy-narun/Yue/ABCD_5.1_data_precessing/processed_data/"
dicfolder_5.1 = '/Volumes/sci-psy-narun/abcd-data-release-5.1/dictionary/'
featurefolder = "/Volumes/sci-psy-narun/Yue/ABCD_5.1_data_precessing/processed_data/"
commonfolder = "/Volumes/sci-psy-narun/Yue/Common_psy_ses_brain_gene_5.1/"
utilFold = "/Volumes/Data/ABCD/ABCD3/Analysis/utilFunc/"
imagingfolder_5.1  = paste0(datafolder_5.1, "imaging/")
nesi_folder <- "/Volumes/sci-psy-narun/Nesi/Yue/"


source(paste0(scriptfold,"stacking_gfactor_modelling/r_functions_5.1.R"))

```

set up parallel

```{r}
# parallel for ubuntu
#doParallel::registerDoParallel(cores=30)  

### parallel library for mac
theme_set(theme_bw() + theme(panel.grid = element_blank()))
## parallel processing number of cores register
all_cores <- parallel::detectCores(logical = FALSE) - 5

doParallel::registerDoParallel(cores = all_cores)

## this one works for ubuntu but slow
#library(doFuture)
#registerDoFuture()
#plan(multicore(workers = 30))

### parallel for windows

#library(doFuture)
#registerDoFuture()
#plan(multisession(workers = 30))
```

# Load up data files

## Family relationship


1 = Male ;2 = Female  ;3 = Intersex-Male ; 4 = Intersex-Female o; 999 = Don't know ; 777 = Refuse to answer 

```{r, cache = FALSE, warning=FALSE}

acspsw03 <- read.csv("/Volumes/sci-psy-narun/abcd-data-release-5.1/core/abcd-general/abcd_y_lt.csv", na = c("", "NA", "999", "777"))
names(acspsw03) <-toupper(colnames(acspsw03))
acspsw03_select <- acspsw03 %>% filter(EVENTNAME %in% c("baseline_year_1_arm_1","2_year_follow_up_y_arm_1" ))

### write NAs of the followup family ids to be the family IDs at baseline
acspsw03_baseline <- acspsw03_select %>% filter(EVENTNAME == "baseline_year_1_arm_1" )
acspsw03_followup <- acspsw03_select %>% filter(EVENTNAME == "2_year_follow_up_y_arm_1" )

fam_basline <- acspsw03_baseline %>% dplyr::select(all_of(c("REL_FAMILY_ID","SRC_SUBJECT_ID")))

acspsw03_followup <- acspsw03_followup %>%dplyr::select(-"REL_FAMILY_ID") %>% 
                                          left_join(fam_basline, by = "SRC_SUBJECT_ID")

acspsw03_select <- bind_rows(acspsw03_baseline,acspsw03_followup)

demo <- read.csv("/Volumes/sci-psy-narun/abcd-data-release-5.1/core/abcd-general/abcd_p_demo.csv", na = c("", "NA", "999", "777"))
names(demo) <-toupper(colnames(demo))
demo_select <- demo %>% filter(EVENTNAME %in% c("baseline_year_1_arm_1","2_year_follow_up_y_arm_1" ))




ACS <- left_join(demo_select,acspsw03_select,by =c("SRC_SUBJECT_ID","EVENTNAME"))

# guardian-report relationship
# Relationship of the participant in his or her family
# 0 = single; 1 = sibling; 2 = twin; 3 = triplet
# ACS %>% count(REL_RELATIONSHIP)

ACSselected <- ACS %>% 
  dplyr::select(all_of(c("SRC_SUBJECT_ID", "EVENTNAME", "DEMO_SEX_V2", "INTERVIEW_AGE", "RACE_ETHNICITY", 
                              "REL_FAMILY_ID", "ACS_RAKED_PROPENSITY_SCORE","SITE_ID_L"))) %>%
  mutate(RACE_ETHNICITY = recode_factor(as.factor(RACE_ETHNICITY),
                `1` = "White", `2` = "Black", `3` = "Hispanic", `4` = "Asian", `5` = "Other",
                .default = "White")) %>%
  mutate(DEMO_SEX_V2 = as.factor(DEMO_SEX_V2)) %>%
  mutate(DEMO_SEX_V2 = recode_factor(as.factor(DEMO_SEX_V2),
                `1` = "Male", `2` = "Female", `3` = "Intersex-Male", `4` = "Intersex-Female",
                .default = "White")) %>%
  mutate(REL_FAMILY_ID = as.factor(REL_FAMILY_ID))

ACSselected %>%
 filter(EVENTNAME =="baseline_year_1_arm_1") %>%
 skimr::skim()


ACSselected_baseline <- ACSselected %>% filter(EVENTNAME =="baseline_year_1_arm_1") 
ACS_sex_race <- ACSselected_baseline %>% dplyr::select(SRC_SUBJECT_ID,DEMO_SEX_V2,RACE_ETHNICITY)

ACSselected_followup <- ACSselected %>% filter(EVENTNAME =="2_year_follow_up_y_arm_1") %>% 
                                        dplyr::select(- all_of(c( "DEMO_SEX_V2" ,"RACE_ETHNICITY"  )))

ACSselected_followup <- left_join(ACSselected_followup,ACS_sex_race,by = "SRC_SUBJECT_ID") 
```

# Create fold information

```{r}

set.seed(123)

fam_vec <- unique(acspsw03_baseline$REL_FAMILY_ID)

fam_split_list <- split(fam_vec, sort(fam_vec%%10))

part_info_select <- ACSselected %>% dplyr::select("SRC_SUBJECT_ID" ,"EVENTNAME" , "REL_FAMILY_ID") 

fold_vec <- c(paste0("fold0",seq(1:9)),"fold10")

add_fold <- function(data_input=part_info_select, 
                     fold_input=fold_vec[1], 
                     split_input = fam_split_list[[1]]){
  data_select <- data_input %>% filter(REL_FAMILY_ID %in% split_input) %>% mutate(fold = fold_input)
  return(data_select)
}


part_fold <- map2(.x = fam_split_list, .y = fold_vec, ~add_fold(data_input=part_info_select, 
                     fold_input=.y, 
                     split_input = .x)) %>% do.call(rbind,.)


part_fold_baseline <- part_fold %>% filter(EVENTNAME == "baseline_year_1_arm_1" )

part_fold_baseline %>% count(fold)


part_fold_followup <- part_fold %>% filter(EVENTNAME == "2_year_follow_up_y_arm_1" )

part_fold_followup %>% count(fold)
```

```{r,eval=FALSE}
saveRDS(part_fold,paste0(nesi_folder,"stacking_gfactor_10foldcv/data/part_fold",".RDS"))
```
