---
title: "Predictive performance of Mental Health, CBCL, ASR,  Personality, Brain, Each Brain Modality, Genes, Soc-Dem-Life-Dev for baseline and follow-up"
author: "Yue Wang and Narun P"
date:  "`r format(Sys.time(), '%d %b, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: united
    number_sections: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load_data, echo=FALSE}
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.
```

# setting up environments

## Note
Here we the ABCD release 5.1 data-set

## Loading libraries
The following libraries and default settings were used during the analysis:


Changes: psychopathology to mental health



```{r load_libraries}
options(scipen = 999)
#library("sva")
library(tidyverse)
library("tidymodels")
##parallel map
library(partR2)
library(lme4)
library(yhat)
library(ggtext)
library(ggpubr)
library(cowplot)
library(partR2)
library(lme4)
library(yhat)
library("VennDiagram")
library(viridis)
library(ggpointdensity)
library(ggthemes)

theme_set(theme_bw() + theme(panel.grid = element_blank()))
## parallel processing number of cores register
all_cores <- parallel::detectCores(logical = FALSE) - 5

doParallel::registerDoParallel(cores = all_cores)

```

## Setting up path

We first loaded all of the relevant data files (not shown here as they refer to local directories):

```{r loading_data, echo=FALSE}
# from Qnap data windows
#datafolder = "//np-qnapa/Data/ABCD/ABCD4/ABCD4SQL/"
#scriptfold = "//np-qnapa/Data/Yue script/"
#NDAfold = "//np-qnapa/Data/ABCD/ABCD4/ABCDStudyNDA/"
#utilFold = "//np-qnapa/Data/ABCD/ABCD3/Analysis/utilFunc/"
#studyNDAFold = "//np-qnapa/Data/ABCD/ABCD4/ABCDStudyNDA/"
#outputfolder = "//np-qnapa/Data/ABCD/ABCD4/ABCD4_precessed_data/"

### unbuntu directories

#datafolder = "/media/Data/ABCD/ABCD4/ABCD4SQL/"
#scriptfold = "/media/Data/Yue script/"
#NDAfold = "/media/Data/ABCD/ABCD4/ABCDStudyNDA/"
#utilFold = "/media/Data/ABCD/ABCD3/Analysis/utilFunc/"
#studyNDAFold = "/media/Data/ABCD/ABCD4/ABCDStudyNDA/"
#outputfolder = "/media/Data/ABCD/ABCD4/ABCD4_precessed_data/"
#featurefolder = "/media/Data/ABCD/ABCD4/Analysis/ManipulatedData/"

### mac directories
datafolder = "/Volumes/Data/ABCD/ABCD4/ABCD4SQL/"
scriptfold = "/Volumes/Data/Yue script/"
NDAfold = "/Volumes/Data/ABCD/ABCD4/ABCDStudyNDA/"
utilFold = "/Volumes/Data/ABCD/ABCD3/Analysis/utilFunc/"
studyNDAFold = "/Volumes/Data/ABCD/ABCD4/ABCDStudyNDA/"
outputfolder = "/Volumes/Data/ABCD/ABCD4/ABCD4_precessed_data/"
featurefolder = "/Volumes/Data/ABCD/ABCD4/Analysis/ManipulatedData/"
nesi_folder <- "/Volumes/sci-psy-narun/Nesi/Yue/"

source(paste0(scriptfold,"stacking_gfactor_modelling/r_functions_fold.R"))


```



# Data Preparation

## load fitted gfactors from brain scan and psychopathology

### load brain scan fitted results from stacking models

```{r}
rf_baseline <- readRDS(paste0(nesi_folder,"stacking_gfactor_10foldcv/collect_random_forest_results/random_forest_baseline_results.RDS"))

rf_followup <- readRDS(paste0(nesi_folder,"stacking_gfactor_10foldcv/collect_random_forest_results/random_forest_followup_results.RDS"))
```

### load the psychopathology predicted results

```{r}
psy_pred <- readRDS(paste0(scriptfold,"Common_psy_gene_brain_all/saved_outputs/psychopathology_pls_pred_no_asr_fold.RData"))
```

### load the computed gfactor

```{r}

gfactor_list <- readRDS(paste0(nesi_folder,"stacking_gfactor_10foldcv/data/gfactor_scale_seperate_fold",".RData"))


```

### genetics predictions

load in genetics related to cognition predicted results 


```{r}

genetics_cog <- readRDS(paste0(scriptfold,'genetics_psychopathology_common_scan_all_scripts/psychopathology_cog_gene_pred_residual_fold', '.RData'))


```

### Soc-Dem-Life-Dev predictions

```{r}

gfactor_ses <- readRDS(paste0(scriptfold,'genetics_psychopathology_common_scan_all_scripts/ses_pls_pred_fold', '.RData'))


```



## process loaded data

Be careful with what site you choose.

Extract the needed data sets from the list.

```{r}

rf_baseline_pred <- map(rf_baseline,"test_pred")
rf_baseline_pred_tibble <- map(rf_baseline_pred,"model_predict")
rf_baseline_table <- map(rf_baseline,"test_data")

rf_followup_pred <- map(rf_followup,"test_pred")
rf_followup_pred_tibble <- map(rf_followup_pred,"model_predict")
rf_followup_table <- map(rf_followup,"test_data")

```


```{r}

gfactor_baselie_test <- map(gfactor_list,"output_test_baseline")
gfactor_followup_test <- map(gfactor_list,"output_test_followup")


```

```{r}
subj_info <- c("SRC_SUBJECT_ID","SITE_ID_L","EVENTNAME")

```

### process data of brain and mental health

```{r}
## this function extract the subject information and join those information to the predicted results
pred_processing <- function(baseline_pred, followup_pred, baseline_table, followup_table,pred_name){
  names_vec <- c(subj_info,pred_name)
  
  baseline_subj_info <- baseline_table %>% select(all_of(subj_info))
  baseline_pred_vec <- baseline_pred %>% select(model_predict)
  baseline_output <- bind_cols(baseline_subj_info,baseline_pred_vec)
  names(baseline_output) <- names_vec
  
  followup_subj_info <- followup_table %>% select(all_of(subj_info))
  followup_pred_vec <- followup_pred %>% select(model_predict)
  followup_output <- bind_cols(followup_subj_info,followup_pred_vec)
  names(followup_output) <- names_vec

  output_all <- bind_rows(baseline_output,followup_output)
  return(list(baseline_output = baseline_output,
              followup_output = followup_output))
}




```



```{r}
processed_rf_results <- pmap(list(rf_baseline_pred_tibble,rf_baseline_table,
                                  rf_followup_pred_tibble,rf_followup_table),
                             ~pred_processing(baseline_pred=..1,
                                              followup_pred=..3, 
                                              baseline_table=..2, 
                                              followup_table=..4,
                                              pred_name="random_forest_stacking"))


processed_psy_results <- pmap(list(psy_pred[["baseline_test_pred"]],
                                   psy_pred[["baseline_test_data"]],
                                  psy_pred[["followup_test_pred"]],
                                  psy_pred[["followup_test_data"]]),
                             ~pred_processing(baseline_pred=..1,
                                              followup_pred=..3, 
                                              baseline_table=..2, 
                                              followup_table=..4,
                                              pred_name="psychopathology"))
```

```{r}

fold_names <- names(processed_rf_results) %>% set_names()

```



### process data of genes 


```{r}
genetics_cog_baseline_pred <-genetics_cog[["baseline_test_pred"]]
genetics_cog_baseline_table <-genetics_cog[["baseline_test_data"]]

genetics_cog_followup_pred <- genetics_cog[["followup_test_pred"]]
genetics_cog_followup_data <- genetics_cog[["followup_test_data"]]


pred_processing_gene <- function(baseline_pred, followup_pred, baseline_table, followup_table,pred_name){
  names_vec <- c(c("SRC_SUBJECT_ID","SITE_ID_L"),pred_name)
  
  baseline_subj_info <- baseline_table %>% select(all_of(c("SRC_SUBJECT_ID","SITE_ID_L")))
  baseline_pred_vec <- baseline_pred %>% select(model_predict)
  baseline_output <- bind_cols(baseline_subj_info,baseline_pred_vec)
  names(baseline_output) <- names_vec
  
  followup_subj_info <- followup_table %>% select(all_of(c("SRC_SUBJECT_ID","SITE_ID_L")))
  followup_pred_vec <- followup_pred %>% select(model_predict)
  followup_output <- bind_cols(followup_subj_info,followup_pred_vec)
  names(followup_output) <- names_vec

  output_all <- bind_rows(baseline_output,followup_output)
  return(list(baseline_output = baseline_output,
              followup_output = followup_output))
}

processed_gene_results <- pmap(list(genetics_cog_baseline_pred,genetics_cog_baseline_table,
                                  genetics_cog_followup_pred,genetics_cog_followup_data),
                             ~pred_processing_gene(baseline_pred=..1,
                                              followup_pred=..3, 
                                              baseline_table=..2, 
                                              followup_table=..4,
                                              pred_name="gene_cog"))


```




### process the data of Soc-Dem-Life-Dev


```{r}
gfactor_ses_baseline_pred <-gfactor_ses[["baseline_test_pred"]]
gfactor_ses_baseline_table <-gfactor_ses[["baseline_test_data"]]

gfactor_ses_followup_pred <- gfactor_ses[["followup_test_pred"]]
gfactor_ses_followup_data <- gfactor_ses[["followup_test_data"]]


processed_ses_results <- pmap(list(gfactor_ses_baseline_pred,gfactor_ses_baseline_table,
                                  gfactor_ses_followup_pred,gfactor_ses_followup_data),
                             ~pred_processing_gene(baseline_pred=..1,
                                              followup_pred=..3, 
                                              baseline_table=..2, 
                                              followup_table=..4,
                                              pred_name="ses"))


```


## join the individual data sets with gfactor


```{r}

join_pred_gfactor <- function(data_input, site_input){
  data_baseline_tibble <- data_input[[site_input]][["baseline_output"]]
  data_followup_tibble <- data_input[[site_input]][["followup_output"]]
  
  gfactor_baseline <- gfactor_baselie_test[[site_input]]
  gfactor_followup <- gfactor_followup_test[[site_input]]

  output_baseline <- plyr::join_all(list(data_baseline_tibble,gfactor_baseline),by="SRC_SUBJECT_ID",type = "full")%>%
    drop_na()
  output_followup <- plyr::join_all(list(data_followup_tibble,gfactor_followup),by="SRC_SUBJECT_ID",type="full")%>%
    drop_na()
 output_all <- bind_rows(output_baseline,output_followup)
  
  return(list(baseline = output_baseline,
              followup=output_followup,
              all = output_all))
}


```


Features: stacking brain models, mental health, genes and Soc-Dem-Life-Dev are joined with response variable individually,


```{r}

gfactor_rf <- map(.x = fold_names,~join_pred_gfactor(data_input =processed_rf_results, site_input = .x))


gfactor_rf_baseline <- map(gfactor_rf,"baseline")%>% do.call(rbind,.)
gfactor_rf_followup <- map(gfactor_rf,"followup")%>% do.call(rbind,.)
gfactor_rf_baseline_followup <- map(gfactor_rf,"all")%>% do.call(rbind,.)



gfactor_psy <- map(.x = fold_names,~join_pred_gfactor(data_input =processed_psy_results, site_input = .x))


gfactor_psy_baseline <- map(gfactor_psy,"baseline")%>% do.call(rbind,.)
gfactor_psy_followup <- map(gfactor_psy,"followup")%>% do.call(rbind,.)
gfactor_psy_baseline_followup <- map(gfactor_psy,"all")%>% do.call(rbind,.)


gfactor_gene <- map(.x = fold_names,~join_pred_gfactor(data_input =processed_gene_results, site_input = .x))


gfactor_gene_baseline <- map(gfactor_gene,"baseline")%>% do.call(rbind,.)%>%
                        filter(gene_cog < 3)
### try to detect outliers
map(gfactor_gene,"baseline")%>% do.call(rbind,.)%>%
                        filter(gene_cog > 3)%>%
                        print()

gfactor_gene_followup <- map(gfactor_gene,"followup")%>% do.call(rbind,.)%>%
                        filter(gene_cog < 3)
gfactor_gene_baseline_followup <- map(gfactor_gene,"all")%>% do.call(rbind,.)%>%
                        filter(gene_cog < 3)


gfactor_ses <- map(.x = fold_names,~join_pred_gfactor(data_input =processed_ses_results, site_input = .x))


gfactor_ses_baseline <- map(gfactor_ses,"baseline")%>% do.call(rbind,.)
gfactor_ses_followup <- map(gfactor_ses,"followup")%>% do.call(rbind,.)
gfactor_ses_baseline_followup <- map(gfactor_ses,"all")%>% do.call(rbind,.)
```

## Combine data and creating names

```{r,fig.width=10}
pred_gfactor_baseline <- list(rf = gfactor_rf_baseline,
                              psy = gfactor_psy_baseline, 
                              gene = gfactor_gene_baseline,
                              ses =gfactor_ses_baseline)

pred_gfactor_followup <- list(rf = gfactor_rf_followup,
                              psy = gfactor_psy_followup, 
                              gene = gfactor_gene_followup,
                              ses =gfactor_ses_followup)

```



# scatterplots

## Loading the metric lavels

```{r}
brain_performance_metric <- readRDS(paste0(scriptfold,'Common_psy_gene_brain_all/saved_outputs/performance_metrics/brain_performance_metric_fold', '.RData'))

gene_performance_metric <- readRDS(paste0(scriptfold,'Common_psy_gene_brain_all/saved_outputs/performance_metrics/gene_performance_metric_fold', '.RData'))

mental_health_performance_metric <- readRDS(paste0(scriptfold,'Common_psy_gene_brain_all/saved_outputs/performance_metrics/mental_health_performance_metric_no_asr_fold', '.RData'))

ses_performance_metric <- readRDS(paste0(scriptfold,'Common_psy_gene_brain_all/saved_outputs/performance_metrics/ses_performance_metric_fold', '.RData'))
```
## Loading in all the scatterplots from other files




```{r}

scatter_legend <- readRDS(paste0(scriptfold,'Common_psy_gene_brain_all/saved_outputs/scatter_plots/scatter_legend_5.1', '.RData'))


scatter_legend_right <- readRDS(paste0(scriptfold,'Common_psy_gene_brain_all/saved_outputs/scatter_plots/scatter_legend_right_5.1', '.RData'))

```





```{r}
names_vec <- c("Mental Health","Neuroimaging",  "Polygenic Scores", "SD LS Dev Adv")

pred_names <- c("random_forest_stacking","psychopathology","gene_cog","ses" )
## create the labels
cor_label_vec_baseline <- c(mental_health_performance_metric$`correlation (sd)`[1],
                            brain_performance_metric$`correlation (sd)`[1],
                            gene_performance_metric$`correlation (sd)`[1],
                            ses_performance_metric$`correlation (sd)`[1])
cor_label_vec_followup <- c(mental_health_performance_metric$`correlation (sd)`[4],
                            brain_performance_metric$`correlation (sd)`[2],
                            gene_performance_metric$`correlation (sd)`[2],
                            ses_performance_metric$`correlation (sd)`[2])


scatter_plot_gfactor_new <- function(data_input,name_input,pred_names,cor_labels){
  
  scatter_plot <-  ggplot(data_input,aes(x = scale(.data[[pred_names]]) , 
                     y = scale(.data[["gfactor"]]))) +
  geom_pointdensity(size = 1) +
       scale_color_viridis()+
  geom_smooth(method = 'lm', se = FALSE, col = 'black')  +
  labs(x = NULL,
       y = NULL,
       title = paste (name_input,'\nr = ',cor_labels))+
     scale_x_continuous(limits=c(-5,5))+
     scale_y_continuous(limits=c(-5,5))+
        theme_classic() + 
             theme(axis.text.x = element_text(size = 35),                      
                           axis.text.y = element_text(size = 35),                     
                           plot.title = element_text(size=35)) +
     theme(
    strip.background = element_blank(),
    strip.text.x = element_blank(),
    legend.position = "none")
 return(scatter_plot)
  
}


scatter_plot_baseline_new <- pmap(list(pred_gfactor_baseline,names_vec,pred_names,cor_label_vec_baseline),
                              ~scatter_plot_gfactor_new(data_input = ..1,
                                                    name_input = ..2,
                                                    pred_names = ..3,
                                                    cor_labels = ..4))



scatter_plot_followup_new <- pmap(list(pred_gfactor_followup,names_vec,pred_names,cor_label_vec_followup),
                              ~scatter_plot_gfactor_new(data_input = ..1,
                                                    name_input = ..2,
                                                    pred_names = ..3,
                                                    cor_labels = ..4))


```

## Load thr saved outputs

```{r}
scatter_plot_baseline_5.1 <- readRDS(paste0(scriptfold,'Common_psy_gene_brain_all/saved_outputs/scatter_plots/scatter_plot_baseline_5.1', '.RData'))
scatter_plot_followup_5.1 <-readRDS(paste0(scriptfold,'Common_psy_gene_brain_all/saved_outputs/scatter_plots/scatter_plot_followup_5.1', '.RData'))

```
## Arrange the plots with all the mental health features

```{r,fig.width=20,fig.height=15}
## plots with mental health

scatter_plot_baseline_fold <-ggpubr::ggarrange(plotlist = scatter_plot_baseline_new,
                                                        ncol = 4,nrow = 1) %>%
                  #                                      legend.grob = scatter_legend,
                  #                                      legend="top")%>%
                ggpubr::annotate_figure(top = ggpubr::text_grob("Baseline",size=45,face="bold",hjust=3.4)) 



scatter_plot_followup_fold <-ggpubr::ggarrange(plotlist = scatter_plot_followup_new,
                                                        ncol = 4,nrow = 1)%>%
                            ggpubr::annotate_figure(top = ggpubr::text_grob("Followup",face="bold",size=45,hjust=3.2))



scatter_all_grid_fold <- ggpubr::ggarrange(scatter_plot_baseline_fold,scatter_plot_followup_fold,nrow = 2,heights = c(1,1))

labelled_scatter_fold <- ggpubr::annotate_figure(scatter_all_grid_fold,
                          left= ggpubr::text_grob("Observed Cognitive Abilities (Z)",size=45,rot=90),
                        bottom = ggpubr::text_grob("Predicted Cognitive Abilities (Z)",size=45),
                        top = ggpubr::text_grob("10 Fold Cross Validation",size=45, face = "bold"
                                                )) 

labelled_scatter_fold
```



```{r,fig.width=20,fig.height=15}
## plots with mental health

scatter_plot_baseline_site <-ggpubr::ggarrange(plotlist = scatter_plot_baseline_5.1,
                                                        ncol = 4,nrow = 1) %>%
                  #                                      legend.grob = scatter_legend,
                  #                                      legend="top")%>%
                ggpubr::annotate_figure(top = ggpubr::text_grob("Baseline",size=45,face="bold",hjust=3.4)) %>%
  ggpubr::ggarrange(                                    legend.grob = scatter_legend,
                                                        legend="top")



scatter_plot_followup_site <-ggpubr::ggarrange(plotlist = scatter_plot_followup_5.1,
                                                        ncol = 4,nrow = 1)%>%
                            ggpubr::annotate_figure(top = ggpubr::text_grob("Followup",face="bold",size=45,hjust=3.2))



scatter_all_grid_site <- ggpubr::ggarrange(scatter_plot_baseline_site,scatter_plot_followup_site,nrow = 2,heights = c(1.2,1))

labelled_scatter_site <- ggpubr::annotate_figure(scatter_all_grid_site,
                          left= ggpubr::text_grob("Observed Cognitive Abilities (Z)",size=45,rot=90),
                        bottom = ggpubr::text_grob("Predicted Cognitive Abilities (Z)",size=45),
                        top = ggpubr::text_grob("Leave One Site out Cross Validation",size=45#, face = "bold"
                                                )) 

labelled_scatter_site
```





## Combine all site plots together

```{r,fig.width=20,fig.height=30}

scatter_all_site_fold <- ggpubr::ggarrange(labelled_scatter_site,labelled_scatter_fold,nrow = 2,heights = c(1.2,1))


labelled_all_site_fold <- ggpubr::annotate_figure(scatter_all_site_fold,
                        top = ggpubr::text_grob("Camparing the Predictive Performance \nbetween Leave One Site out and 10 Fold Cross Validation",size=45, face = "bold")) 

labelled_all_site_fold
```

